---
title: "Bounce Analysis"
author: "Hannah Curtis"
date: "2024-01-16"
output: html_document
---

This file plots linear regressions of hydrologic, engineering design, and watershed variables against the bounce both using the average value for each pond, and the value per each storm with with collected information for variables including the percent change in all water quality parameters (includes 3 storms when sampling occurred), gradual decline rate in water level, and temperature variance (should later add attenuation by storm). 

Predictor variables:
Hydrologic variables: median water level, percentage of time water level is constant, percentage of time water level is constant (within 6 inches), percentage of time water level is within 6 inches of the outlet, percentage of time water level is below the outlet opening, percentage of time water level is between the 25 and 75 percentiles, percentage of time water level is between the 10 and 90 percentiles, skewness of water level pdfs, and average graudal decline rate in water level. 

Engineering design variables: length-to-width ratio, whether the pond is in a chain, number of outlets, whether the pond is mowed, pond age, pond area, average pond depth, average pond volume, low flow outlet restrictiveness, total outlet restrictiveness, total number of vegetation species, percent native veg species, and percent non-native veg species. 

Watershed variables: percentage of days urban baseflow is occurring.

Response variables:
Biodiversity: total species richness, plant richness, animal richness, invertebrate richness, vertebrate richness, fish richness, herp richness, and amphibian richness.

Aesthetics: odor, trash count, recreation count.

Water Quality: chloride, dissolved oxygen, secchi depth, specific conductance, sulfate, temperature, total nitrogen, total phosphorous, total suspended solids, nitrate (using half of LOD values for values below LOD), and ammonia (using half LOD values for values below LOD).

Could come back and determine R2 value for each linear regression.

Also could look at average change in water quality variables vs average bounce.

Updated: 3/8/24


Read Variables and Bounce Files
```{r}
library(dplyr)

# Predictor Variables

# Design Vars
design_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Design/Design_Vars.csv")
lw_ratio <- design_dat$L.to.W.ratio
pond_chain <- design_dat$Pond.Chain
num_outlets <- design_dat$Number.of.Outlets
mow_status <- design_dat$Mowed
pond_age <- design_dat$Pond.Age

# Pond/Watershed Areas
area_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Areas/Pond_Areas.csv")
pond_area <- area_dat$Pond.Area.ft2

# Constant Depth Variables
const_depth_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Constant_Depth/Uniform_Depth.csv")
median_wl <- const_depth_dat$Median.Water.Level
const_wl <- const_depth_dat$Constant.Water.Level
const_wl_6in <- const_depth_dat$Contant.Water.Level.6in
outlet_wl <- const_depth_dat$Outlet.Water.Level
below_outlet_wl <- const_depth_dat$Below.Outlet.Water.Level
wl_25_75 <- const_depth_dat$Water.Level.25.75.Quantile
wl_10_90 <- const_depth_dat$Water.Level.10.90.Quantile
skewness <- const_depth_dat$Pond.Skewness

# Gradual Decline Rate
dec_rate_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Decline_Rate/Decline_Rate.csv")
avg_dec_rate <- dec_rate_dat$Average.Decline.Rate
dec_rate_5_11 <- na.omit(dec_rate_dat$Decline.Rate.5.11)
dec_rate_7_28 <- na.omit(dec_rate_dat$Decline.Rate.7.28)
dec_rate_8_14 <- na.omit(dec_rate_dat$Decline.Rate.8.14)
dec_rate_9_24 <- na.omit(dec_rate_dat$Decline.Rate.9.24)
dec_rate_10_13 <- na.omit(dec_rate_dat$Decline.Rate.10.13)

# Outlet Restrictiveness
out_rest_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Outlet_Restrictiveness/Outlet_Restrictiveness.csv")
# Using rating curve calculated from outflow calcs
lf_rest <- na.omit(out_rest_dat$LF.Restrictiveness..calc.RC.)
tot_rest <- na.omit(out_rest_dat$Tot.Restrictiveness..calc.RC.)

# Residence Time
res_time_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Residence_Time/Res_Time.csv")
avg_depth <- res_time_dat$Average.Pond.Depth.ft
avg_volume <- res_time_dat$Pond.Volume

# Urban Baseflow
urban_bf_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Urban_Baseflow/Urban_Baseflow.csv")
urban_bf <- urban_bf_dat$Urban.Baseflow

# Vegetation Survey
veg_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Vegetation/Vegetation Survey.csv")
tot_veg <- veg_data$Total...Veg.Species
num_native <- veg_data$X..Native.Species
num_nonnative <- veg_data$X..Non.native.species
percent_native <- veg_data$X..Native.Species.1
percent_nonnative <- veg_data$X..Non.native.species.1

# Response Variables

# Species Richness
species_rich_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Species_Richness/Pond_Richness.csv")
tot_rich <- species_rich_dat$Total.Richness
plant_rich <- species_rich_dat$Plant.Richness
animal_rich <- species_rich_dat$Animal.Richness
invert_rich <- species_rich_dat$Invert.Richness
vert_rich <- species_rich_dat$Vert.Richness
fish_rich <- species_rich_dat$Fish.Richness
herp_rich <- species_rich_dat$Herp.Richness
amphib_rich <- species_rich_dat$Amphib.Richness

# Aesthetics
aesth_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Aesthetic/Average_Aesthetic.csv")
avg_odor <- aesth_dat$Average.Odor
avg_trash <- aesth_dat$Average.Trash.Count
tot_rec <- aesth_dat$Total.People.Recreating

# Water Quality Vars
# Chloride
chloride_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Chloride.csv")
chloride <- chloride_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(Chloride..mg.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(chloride_data$Pond.Name)), desc(Average_Value))

# DO
dissoxy_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/DissolvedOxygen.csv")
dissoxy <- dissoxy_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(YSI.DO..mg.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(dissoxy_data$Pond.Name)), desc(Average_Value))

# Secchi
secchi_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Secchi_Depth.csv")
secchi <- secchi_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(Secchi.Disk.Depth..cm., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(secchi_data$Pond.Name)), desc(Average_Value))

# SPC
spc_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/SPC.csv")
spc <- spc_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(SPC, na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(spc_data$Pond.Name)), desc(Average_Value))

# Sulfate
sulfate_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Sulfate.csv")
sulfate <- sulfate_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(Sulfate..mg.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(sulfate_data$Pond.Name)), desc(Average_Value))

# Temp
temp_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Temperature.csv")
temp <- temp_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(Temperature..Degrees.Celsius., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(temp_data$Pond.Name)), desc(Average_Value))

# TN
tot_n_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/TotalNitrogen.csv")
tot_n <- tot_n_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(TN..ug.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(tot_n_data$Pond.Name)), desc(Average_Value))

# TP
tot_p_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/TotalPhosphorous.csv")
tot_p <- tot_p_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(TP..ug.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(tot_p_data$Pond.Name)), desc(Average_Value))

# TSS
tot_ss_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/TSS.csv")
tot_ss <- tot_ss_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(TSS..mg.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(tot_ss_data$Pond.Name)), desc(Average_Value))

# Nitrate/Ammonia
nitrate_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Nitrate Data.csv")
nitrate <- nitrate_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(Nitrate..ug.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(nitrate_data$Pond.Name)), desc(Average_Value))
nitrate_lod <- nitrate_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(Nitrate.LOD..ug.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(nitrate_data$Pond.Name)), desc(Average_Value))
ammonia <- nitrate_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(Ammonia..ug.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(nitrate_data$Pond.Name)), desc(Average_Value))
ammonia_lod <- nitrate_data %>%
  group_by(Pond.Name) %>%
  summarize(Average_Value = mean(Ammonia.LOD..ug.L., na.rm = TRUE)) %>%
  arrange(factor(Pond.Name, levels=unique(nitrate_data$Pond.Name)), desc(Average_Value))

# Water Quality Percent Change by Storm

# 7/28
water_qual_7_28_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Water_Quality_Change_7_28.csv")
chloride_7_28 <- water_qual_7_28_dat$Chloride.Change....
do_7_28 <- water_qual_7_28_dat$YSI.DO.Change....
secchi_7_28 <- water_qual_7_28_dat$Secchi.Disk.Change....
sulfate_7_28 <- water_qual_7_28_dat$Sulfate.Change....
temp_7_28 <- water_qual_7_28_dat$Temperature.Change....
tn_7_28 <- water_qual_7_28_dat$TN.Change....
tp_7_28 <- water_qual_7_28_dat$TP.Change....
tss_7_28 <- water_qual_7_28_dat$TSS.Change....
nitrate_7_28 <- water_qual_7_28_dat$Nitrate.Change....
ammonia_7_28 <- water_qual_7_28_dat$Ammonia.Change....

# 8/14
water_qual_8_14_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Water_Quality_Change_8_14.csv")
chloride_8_14 <- water_qual_8_14_dat$Chloride.Change....
do_8_14 <- water_qual_8_14_dat$YSI.DO.Change....
secchi_8_14 <- water_qual_8_14_dat$Secchi.Disk.Change....
sulfate_8_14 <- water_qual_8_14_dat$Sulfate.Change....
temp_8_14 <- water_qual_8_14_dat$Temperature.Change....
tn_8_14 <- water_qual_8_14_dat$TN.Change....
tp_8_14 <- water_qual_8_14_dat$TP.Change....
tss_8_14 <- water_qual_8_14_dat$TSS.Change....
nitrate_8_14 <- water_qual_8_14_dat$Nitrate.Change....
ammonia_8_14 <- water_qual_8_14_dat$Ammonia.Change....

# 9/24
water_qual_9_24_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Water_Quality_Change_9_24.csv")
chloride_9_24 <- water_qual_9_24_dat$Chloride.Change....
do_9_24 <- water_qual_9_24_dat$YSI.DO.Change....
secchi_9_24 <- water_qual_9_24_dat$Secchi.Disk.Change....
spc_9_24 <- water_qual_9_24_dat$SPC.Change....
sulfate_9_24 <- water_qual_9_24_dat$Sulfate.Change....
temp_9_24 <- water_qual_9_24_dat$Temperature.Change....
tn_9_24 <- water_qual_9_24_dat$TN.Change....
tp_9_24 <- water_qual_9_24_dat$TP.Change....
tss_9_24 <- water_qual_9_24_dat$TSS.Change....
nitrate_9_24 <- water_qual_9_24_dat$Nitrate.Change....
ammonia_9_24 <- water_qual_9_24_dat$Ammonia.Change....

# Bounce files by storm
# July 4
bounce_jul4_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Bounce/July4_storm.csv")
bounce_jul4 <- bounce_jul4_dat$maxbounce
temp_var_jul4 <- bounce_jul4_dat$tempvariance
rain_jul4 <- bounce_jul4_dat$rainamount
# July 28
bounce_jul28_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Bounce/July28_storm.csv")
bounce_jul28 <- bounce_jul28_dat$maxbounce
temp_var_jul28 <- bounce_jul28_dat$tempvariance
rain_jul28 <- bounce_jul28_dat$rainamount
# August 14
bounce_aug14_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Bounce/Aug14_storm.csv")
bounce_aug14 <- bounce_aug14_dat$maxbounce
temp_var_aug14 <- bounce_aug14_dat$tempvariance
rain_aug14 <- bounce_aug14_dat$rainamount
# Sept 6
bounce_sept6_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Bounce/Sept6_storm.csv")
bounce_sept6 <- bounce_sept6_dat$maxbounce
temp_var_sept6 <- bounce_sept6_dat$tempvariance
rain_sept6 <- bounce_sept6_dat$rainamount
# Sept 24
bounce_sept24_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Bounce/Sept24_storm.csv")
bounce_sept24 <- bounce_sept24_dat$maxbounce
temp_var_sept24 <- bounce_sept24_dat$tempvariance
rain_sept24 <- bounce_sept24_dat$rainamount
# Oct 13
bounce_oct13_dat <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Bounce/Oct13_storm.csv")
bounce_oct13 <- bounce_oct13_dat$maxbounce
temp_var_oct13 <- bounce_oct13_dat$tempvariance
rain_oct13 <- bounce_oct13_dat$rainamount

# Avg bounce files
avg_bounce_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Bounce/AverageBounce.csv")
avg_bounce <- avg_bounce_data$maxbounce
norm_bounce <- avg_bounce_data$normalized.bounce
```

Average Bounce vs Average Value Relationships
```{r}
# Predictor Variables
# Length-to-width Ratio
bounce_lw <- lm(lw_ratio ~ avg_bounce)
plot(avg_bounce, lw_ratio, xlab = "Bounce (ft)", ylab = "Length-to-width Ratio", pch = 16, col = "red", bg="transparent")
abline(bounce_lw)
grid()

# Pond Chain 
bounce_chain <- lm(pond_chain ~ avg_bounce)
plot(avg_bounce, pond_chain, xlab = "Bounce (ft)", ylab = "Pond Chain", pch = 16, col = "red2", bg="transparent")
abline(bounce_chain)
grid()

# Number of Outlets
bounce_numout <- lm(num_outlets ~ avg_bounce)
plot(avg_bounce, num_outlets, xlab = "Bounce (ft)", ylab = "Number of Outlets", pch = 16, col = "red3", bg="transparent")
abline(bounce_numout)
grid()

# Mow Status
bounce_mow <- lm(mow_status ~ avg_bounce)
plot(avg_bounce, mow_status, xlab = "Bounce (ft)", ylab = "Mow Status", pch = 16, col = "red4", bg="transparent")
abline(bounce_mow)
grid()

# Pond Age
bounce_age <- lm(pond_age ~ avg_bounce)
plot(avg_bounce, pond_age, xlab = "Bounce (ft)", ylab = "Pond Age", pch = 16, col = "maroon", bg="transparent")
abline(bounce_age)
grid()

# Median WL
bounce_med_wl <- lm(median_wl ~ avg_bounce)
plot(avg_bounce, median_wl, xlab = "Bounce (ft)", ylab = "Median Water Level (ft)", pch = 16, col = "orange", bg="transparent")
abline(bounce_med_wl)
grid()

# Constant WL
bounce_const_wl <- lm(const_wl ~ avg_bounce)
plot(avg_bounce, const_wl, xlab = "Bounce (ft)", ylab = "Percent of Time Water Level is Constant", pch = 16, col = "orange2", bg="transparent")
abline(bounce_const_wl)
grid()

# Constant WL within 6 in
bounce_const_wl_6in <- lm(const_wl_6in ~ avg_bounce)
plot(avg_bounce, const_wl_6in, xlab = "Bounce (ft)", ylab = "Percent of Time Water Level within 6 in of Mode", pch = 16, col = "orange3", bg="transparent")
abline(bounce_const_wl_6in)
grid()

# Outlet WL
bounce_out_wl <- lm(outlet_wl ~ avg_bounce)
plot(avg_bounce, outlet_wl, xlab = "Bounce (ft)", ylab = "Outlet Water Level", pch = 16, col = "orange4", bg="transparent")
abline(bounce_out_wl)
grid()

# Below Outlet WL
bounce_below_out <- lm(below_outlet_wl ~ avg_bounce)
plot(avg_bounce, below_outlet_wl, xlab = "Bounce (ft)", ylab = "Percent of Time Water Level is Below Outlet", pch = 16, col = "gold", bg="transparent")
abline(bounce_below_out)
grid()

# Water Level 25-75 Percentile
bounce_25_75 <- lm(wl_25_75 ~ avg_bounce)
plot(avg_bounce, wl_25_75, xlab = "Bounce (ft)", ylab = "Percentage of Time Water Level Between 25 and 75 Percentile", pch = 16, col = "gold2", bg="transparent")
abline(bounce_25_75)
grid()

# Water Level 10-90 Percentile
bounce_10_90 <- lm(wl_10_90 ~ avg_bounce)
plot(avg_bounce, wl_10_90, xlab = "Bounce (ft)", ylab = "Percentage of Time Water Level Between 10 and 90 Percentile", pch = 16, col = "gold3", bg="transparent")
abline(bounce_10_90)
grid()

# Skewness
bounce_skew <- lm(skewness ~ avg_bounce)
plot(avg_bounce, skewness, xlab = "Bounce (ft)", ylab = "Skewness of Water Level Histogram", pch = 16, col = "gold4", bg="transparent")
abline(bounce_skew)
grid()

# Average Gradual Decline Rate
bounce_dec <- lm(avg_dec_rate ~ avg_bounce)
plot(avg_bounce, avg_dec_rate, xlab = "Bounce (ft)", ylab = "Average Gradual Decline Rate", pch = 16, col = "yellow", bg="transparent")
abline(bounce_dec)
grid()

# Low Flow Outlet Restrictiveness
bounce_lf_rest <- lm(lf_rest ~ avg_bounce)
plot(avg_bounce, lf_rest, xlab = "Bounce (ft)", ylab = "Low Flow Outlet Restrictiveness", pch = 16, col = "salmon", bg="transparent")
abline(bounce_lf_rest)
grid()

# Total Outlet Restrictiveness
bounce_tot_rest <- lm(tot_rest ~ avg_bounce)
plot(avg_bounce, tot_rest, xlab = "Bounce (ft)", ylab = "Total Outlet Restrictiveness", pch = 16, col = "salmon3", bg="transparent")
abline(bounce_tot_rest)
grid()

# Pond Area
bounce_area <- lm(pond_area ~ avg_bounce)
plot(avg_bounce, pond_area, xlab = "Bounce (ft)", ylab = "Pond Area (ft2)", pch = 16, col = "maroon2", bg="transparent")
abline(bounce_area)
grid()

# Average Depth
bounce_depth <- lm(avg_depth ~ avg_bounce)
plot(avg_bounce, avg_depth, xlab = "Bounce (ft)", ylab = "Average Pond Depth (ft)", pch = 16, col = "pink", bg="transparent")
abline(bounce_depth)
grid()

# Average Volume
bounce_vol <- lm(avg_volume ~ avg_bounce)
plot(avg_bounce, avg_volume, xlab = "Bounce (ft)", ylab = "Pond Volume (ft3)", pch = 16, col = "pink2", bg="transparent")
abline(bounce_vol)
grid()

# Urban Baseflow
bounce_urb_bf <- lm(urban_bf ~ avg_bounce)
plot(avg_bounce, urban_bf, xlab = "Bounce (ft)", ylab = "Percentage of Days with Inflow", pch = 16, col = "pink3", bg="transparent")
abline(bounce_urb_bf)
grid()

# Total Vegetation Species
bounce_tot_veg <- lm(tot_veg ~ avg_bounce)
plot(avg_bounce, tot_veg, xlab = "Bounce (ft)", ylab = "Total # of Vegetation Species", pch = 16, col = "darkseagreen", bg="transparent")
abline(bounce_tot_veg)
grid()

# Percent Native Veg Species
bounce_native_veg <- lm(percent_native ~ avg_bounce)
plot(avg_bounce, percent_native, xlab = "Bounce (ft)", ylab = "% Native Species", pch = 16, col = "darkseagreen2", bg="transparent")
abline(bounce_native_veg)
grid()

# Percent Non-native Veg Species
bounce_nonnative_veg <- lm(percent_nonnative ~ avg_bounce)
plot(avg_bounce, percent_nonnative, xlab = "Bounce (ft)", ylab = "% Non-native Species", pch = 16, col = "darkseagreen3", bg="transparent")
abline(bounce_nonnative_veg)
grid()

# Response Variables
# Species Richness
bounce_rich <- lm(tot_rich ~ avg_bounce)
plot(avg_bounce, tot_rich, xlab = "Bounce (ft)", ylab = "Total Species Richness", pch = 16, col = "purple", bg="transparent")
abline(bounce_rich)
grid()

# Plant Richness
bounce_plant_rich <- lm(plant_rich ~ avg_bounce)
plot(avg_bounce, plant_rich, xlab = "Bounce (ft)", ylab = "Plant Species Richness", pch = 16, col = "purple3", bg="transparent")
abline(bounce_plant_rich)
grid()

# Animal Richness
bounce_animal_rich <- lm(animal_rich ~ avg_bounce)
plot(avg_bounce, animal_rich, xlab = "Bounce (ft)", ylab = "Animal Species Richness", pch = 16, col = "purple4", bg="transparent")
abline(bounce_animal_rich)
grid()

# Invertebrate Richness
bounce_invert_rich <- lm(invert_rich ~ avg_bounce)
plot(avg_bounce, invert_rich, xlab = "Bounce (ft)", ylab = "Invertebrate Species Richness", pch = 16, col = "magenta", bg="transparent")
abline(bounce_invert_rich)
grid()

# Vertebrate Richness
bounce_vert_rich <- lm(vert_rich ~ avg_bounce)
plot(avg_bounce, vert_rich, xlab = "Bounce (ft)", ylab = "Vertebrate Species Richness", pch = 16, col = "magenta2", bg="transparent")
abline(bounce_vert_rich)
grid()

# Fish Richness
bounce_fish_rich <- lm(fish_rich ~ avg_bounce)
plot(avg_bounce, fish_rich, xlab = "Bounce (ft)", ylab = "Fish Species Richness", pch = 16, col = "magenta3", bg="transparent")
abline(bounce_fish_rich)
grid()

# Herp Richness
bounce_herp_rich <- lm(herp_rich ~ avg_bounce)
plot(avg_bounce, herp_rich, xlab = "Bounce (ft)", ylab = "Herp Species Richness", pch = 16, col = "magenta4", bg="transparent")
abline(bounce_herp_rich)
grid()

# Amphibian Richness
bounce_amphib_rich <- lm(amphib_rich ~ avg_bounce)
plot(avg_bounce, amphib_rich, xlab = "Bounce (ft)", ylab = "Amphibian Species Richness", pch = 16, col = "orchid", bg="transparent")
abline(bounce_amphib_rich)
grid()

# Chloride
bounce_chlor <- lm(chloride$Average_Value ~ avg_bounce)
plot(avg_bounce, chloride$Average_Value, xlab = "Bounce (ft)", ylab = "Chloride (mg/L)", pch = 16, col = "lightblue", bg="transparent")
abline(bounce_chlor)
grid()

# DO
bounce_do <- lm(dissoxy$Average_Value ~ avg_bounce)
plot(avg_bounce, dissoxy$Average_Value, xlab = "Bounce (ft)", ylab = "Dissolved Oxygen (mg/L)", pch = 16, col = "blue", bg="transparent")
abline(bounce_do)
grid()

# Secchi
bounce_secchi <- lm(secchi$Average_Value ~ avg_bounce)
plot(avg_bounce, secchi$Average_Value, xlab = "Bounce (ft)", ylab = "Secchi Depth (cm)", pch = 16, col = "blue4", bg="transparent")
abline(bounce_secchi)
grid()

# SPC
bounce_spc <- lm(spc$Average_Value ~ avg_bounce)
plot(avg_bounce, spc$Average_Value, xlab = "Bounce (ft)", ylab = "Specific Conductance", pch = 16, col = "lightgreen", bg="transparent")
abline(bounce_spc)
grid()

# Sulfate
bounce_sulfate <- lm(sulfate$Average_Value ~ avg_bounce)
plot(avg_bounce, sulfate$Average_Value, xlab = "Bounce (ft)", ylab = "Sulfate (mg/L)", pch = 16, col = "green2", bg="transparent")
abline(bounce_sulfate)
grid()

# Temperature
bounce_temp <- lm(temp$Average_Value ~ avg_bounce)
plot(avg_bounce, temp$Average_Value, xlab = "Bounce (ft)", ylab = "Temperature (degrees C)", pch = 16, col = "green3", bg="transparent")
abline(bounce_temp)
grid()

# TN
bounce_tn <- lm(tot_n$Average_Value ~ avg_bounce)
plot(avg_bounce, tot_n$Average_Value, xlab = "Bounce (ft)", ylab = "Total Nitrogen (mg/L)", pch = 16, col = "green4", bg="transparent")
abline(bounce_tn)
grid()

# TP
bounce_tp <- lm(tot_p$Average_Value ~ avg_bounce)
plot(avg_bounce, tot_p$Average_Value, xlab = "Bounce (ft)", ylab = "Total Phosphorous (mg/L)", pch = 16, col = "turquoise", bg="transparent")
abline(bounce_tp)
grid()

# TSS
bounce_tss <- lm(tot_ss$Average_Value ~ avg_bounce)
plot(avg_bounce, tot_ss$Average_Value, xlab = "Bounce (ft)", ylab = "Total Suspended Solids (mg/L)", pch = 16, col = "turquoise2", bg="transparent")
abline(bounce_tss)
grid()

# Nitrate
bounce_nitrate <- lm(nitrate$Average_Value ~ avg_bounce)
plot(avg_bounce, nitrate$Average_Value, xlab = "Bounce (ft)", ylab = "Nitrate (ug/L)", pch = 16, col = "turquoise4", bg="transparent")
abline(bounce_nitrate)
grid()

# Nitrate LOD
bounce_nitrate_lod <- lm(nitrate_lod$Average_Value ~ avg_bounce)
plot(avg_bounce, nitrate_lod$Average_Value, xlab = "Bounce (ft)", ylab = "Nitrate LOD (ug/L)", pch = 16, col = "seagreen", bg="transparent")
abline(bounce_nitrate_lod)
grid()

# Ammonia
bounce_ammonia <- lm(ammonia$Average_Value ~ avg_bounce)
plot(avg_bounce, ammonia$Average_Value, xlab = "Bounce (ft)", ylab = "Ammonia (ug/L)", pch = 16, col = "seagreen2", bg="transparent")
abline(bounce_ammonia)
grid()

# Ammonia LOD
bounce_ammonia_lod <- lm(ammonia_lod$Average_Value ~ avg_bounce)
plot(avg_bounce, ammonia_lod$Average_Value, xlab = "Bounce (ft)", ylab = "Ammonia LOD (ug/L)", pch = 16, col = "seagreen3", bg="transparent")
abline(bounce_ammonia_lod)
grid()

# Odor
bounce_odor <- lm(avg_odor ~ avg_bounce)
plot(avg_bounce, avg_odor, xlab = "Bounce (ft)", ylab = "Average Odor (scale -5 to 5)", pch = 16, col = "lightgray", bg="transparent")
abline(bounce_odor)
grid()

# Trash
bounce_trash <- lm(avg_trash ~ avg_bounce)
plot(avg_bounce, avg_trash, xlab = "Bounce (ft)", ylab = "Average Trash Count", pch = 16, col = "gray", bg="transparent")
abline(bounce_trash)
grid()

# Recreation
bounce_rec <- lm(tot_rec ~ avg_bounce)
plot(avg_bounce, tot_rec, xlab = "Bounce (ft)", ylab = "Total Recreation", pch = 16, col = "darkgray", bg="transparent")
abline(bounce_rec)
grid()
```

Storm-Based Bounce Relationships
```{r}
# Gradual Water Level Decline
# July 28
bounce_dec_jul28 <- lm(dec_rate_7_28 ~ bounce_jul28)
plot(bounce_jul28, dec_rate_7_28, xlab = "Bounce (ft)", ylab = "Average Gradual Decline Rate", pch = 16, col = "royalblue", bg="transparent")
abline(bounce_dec_jul28)
grid()

# August 14
bounce_dec_aug14 <- lm(dec_rate_8_14 ~ bounce_aug14)
plot(bounce_aug14, dec_rate_8_14, xlab = "Bounce (ft)", ylab = "Average Gradual Decline Rate", pch = 16, col = "royalblue4", bg="transparent")
abline(bounce_dec_aug14)
grid()

# September 24
bounce_dec_sept24 <- lm(dec_rate_9_24 ~ bounce_sept24)
plot(bounce_sept24, dec_rate_9_24, xlab = "Bounce (ft)", ylab = "Average Gradual Decline Rate", pch = 16, col = "forestgreen", bg="transparent")
abline(bounce_dec_sept24)
grid()

# October 13
bounce_dec_oct13 <- lm(dec_rate_10_13 ~ bounce_oct13)
plot(bounce_oct13, dec_rate_10_13, xlab = "Bounce (ft)", ylab = "Average Gradual Decline Rate", pch = 16, col = "darkgreen", bg="transparent")
abline(bounce_dec_oct13)
grid()

# Temperature Variance

# July 4
bounce_temp_jul4 <- lm(temp_var_jul4 ~ bounce_jul4)
plot(bounce_jul4, temp_var_jul4, xlab = "Bounce (ft)", ylab = "Temperature Variance", pch = 16, col = "lightpink", bg="transparent")
abline(bounce_temp_jul4)
grid()

# July 28
bounce_temp_jul28 <- lm(temp_var_jul28 ~ bounce_jul28)
plot(bounce_jul28, temp_var_jul28, xlab = "Bounce (ft)", ylab = "Temperature Variance", pch = 16, col = "lightpink3", bg="transparent")
abline(bounce_temp_jul28)
grid()

# August 14
bounce_temp_aug14 <- lm(temp_var_aug14 ~ bounce_aug14)
plot(bounce_aug14, temp_var_aug14, xlab = "Bounce (ft)", ylab = "Temperature Variance", pch = 16, col = "lightpink4", bg="transparent")
abline(bounce_temp_aug14)
grid()

# September 6
bounce_temp_sept6 <- lm(temp_var_sept6 ~ bounce_sept6)
plot(bounce_sept6, temp_var_sept6, xlab = "Bounce (ft)", ylab = "Temperature Variance", pch = 16, col = "hotpink", bg="transparent")
abline(bounce_temp_sept6)
grid()

# September 24
bounce_temp_sept24 <- lm(temp_var_sept24 ~ bounce_sept24)
plot(bounce_sept24, temp_var_sept24, xlab = "Bounce (ft)", ylab = "Temperature Variance", pch = 16, col = "hotpink3", bg="transparent")
abline(bounce_temp_sept24)
grid()

# October 13
bounce_temp_oct13 <- lm(temp_var_oct13 ~ bounce_oct13)
plot(bounce_oct13, temp_var_oct13, xlab = "Bounce (ft)", ylab = "Temperature Variance", pch = 16, col = "hotpink4", bg="transparent")
abline(bounce_temp_oct13)
grid()

# Water Quality

# July 28 Storm
# Chloride
bounce_chlor_jul28 <- lm(chloride_7_28 ~ bounce_jul28)
plot(bounce_jul28, chloride_7_28, xlab = "Bounce (ft)", ylab = "Chloride", pch = 16, col = "lightblue", bg="transparent")
abline(bounce_chlor_jul28)
grid()

# DO
bounce_do_jul28 <- lm(do_7_28 ~ bounce_jul28)
plot(bounce_jul28, do_7_28, xlab = "Bounce (ft)", ylab = "Dissolved Oxygen", pch = 16, col = "lightblue3", bg="transparent")
abline(bounce_do_jul28)
grid()

# Secchi
bounce_secchi_jul28 <- lm(secchi_7_28 ~ bounce_jul28)
plot(bounce_jul28, secchi_7_28, xlab = "Bounce (ft)", ylab = "Water Clarity", pch = 16, col = "lightblue4", bg="transparent")
abline(bounce_secchi_jul28)
grid()

# Sulfate
bounce_sulfate_jul28 <- lm(sulfate_7_28 ~ bounce_jul28)
plot(bounce_jul28, sulfate_7_28, xlab = "Bounce (ft)", ylab = "Sulfate", pch = 16, col = "lightgreen", bg="transparent")
abline(bounce_sulfate_jul28)
grid()

# Temp
bounce_temp_jul28 <- lm(temp_7_28 ~ bounce_jul28)
plot(bounce_jul28, temp_7_28, xlab = "Bounce (ft)", ylab = "Temperature", pch = 16, col = "palegreen", bg="transparent")
abline(bounce_temp_jul28)
grid()

# TN
bounce_tn_jul28 <- lm(tn_7_28 ~ bounce_jul28)
plot(bounce_jul28, tn_7_28, xlab = "Bounce (ft)", ylab = "Total Nitrogen", pch = 16, col = "palegreen3", bg="transparent")
abline(bounce_tn_jul28)
grid()

# TP
bounce_tp_jul28 <- lm(tp_7_28 ~ bounce_jul28)
plot(bounce_jul28, tp_7_28, xlab = "Bounce (ft)", ylab = "Total Phosphorous", pch = 16, col = "palegreen4", bg="transparent")
abline(bounce_tp_jul28)
grid()

# TSS
bounce_tss_jul28 <- lm(tss_7_28 ~ bounce_jul28)
plot(bounce_jul28, tss_7_28, xlab = "Bounce (ft)", ylab = "Total Suspended Solids", pch = 16, col = "lightslateblue", bg="transparent")
abline(bounce_tss_jul28)
grid()

# Nitrate
bounce_nitrate_jul28 <- lm(nitrate_7_28 ~ bounce_jul28)
plot(bounce_jul28, nitrate_7_28, xlab = "Bounce (ft)", ylab = "Nitrate", pch = 16, col = "mediumpurple", bg="transparent")
abline(bounce_nitrate_jul28)
grid()

# Ammonia
bounce_ammonia_jul28 <- lm(ammonia_7_28 ~ bounce_jul28)
plot(bounce_jul28, ammonia_7_28, xlab = "Bounce (ft)", ylab = "Ammonia", pch = 16, col = "mediumpurple3", bg="transparent")
abline(bounce_ammonia_jul28)
grid()

# August 14 Storm
# Chloride
bounce_chlor_aug14 <- lm(chloride_8_14 ~ bounce_aug14)
plot(bounce_aug14, chloride_8_14, xlab = "Bounce (ft)", ylab = "Chloride", pch = 16, col = "lightblue", bg="transparent")
abline(bounce_chlor_aug14)
grid()

# DO
bounce_do_aug14 <- lm(do_8_14 ~ bounce_aug14)
plot(bounce_aug14, do_8_14, xlab = "Bounce (ft)", ylab = "Dissolved Oxygen", pch = 16, col = "lightblue3", bg="transparent")
abline(bounce_do_aug14)
grid()

# Secchi
bounce_secchi_aug14 <- lm(secchi_8_14 ~ bounce_aug14)
plot(bounce_aug14, secchi_8_14, xlab = "Bounce (ft)", ylab = "Water Clarity", pch = 16, col = "lightblue4", bg="transparent")
abline(bounce_secchi_aug14)
grid()

# Sulfate
bounce_sulfate_aug14 <- lm(sulfate_8_14 ~ bounce_aug14)
plot(bounce_aug14, sulfate_8_14, xlab = "Bounce (ft)", ylab = "Sulfate", pch = 16, col = "lightgreen", bg="transparent")
abline(bounce_sulfate_aug14)
grid()

# Temp
#bounce_temp_aug14 <- lm(temp_8_14 ~ bounce_aug14)
#plot(bounce_aug14, temp_8_14, xlab = "Bounce (ft)", ylab = "Temperature", pch = 16, col = "palegreen", bg="transparent")
#abline(bounce_temp_aug14)
#grid()

# TN
bounce_tn_aug14 <- lm(tn_8_14 ~ bounce_aug14)
plot(bounce_aug14, tn_8_14, xlab = "Bounce (ft)", ylab = "Total Nitrogen", pch = 16, col = "palegreen3", bg="transparent")
abline(bounce_tn_aug14)
grid()

# TP
bounce_tp_aug14 <- lm(tp_8_14 ~ bounce_aug14)
plot(bounce_aug14, tp_8_14, xlab = "Bounce (ft)", ylab = "Total Phosphorous", pch = 16, col = "palegreen4", bg="transparent")
abline(bounce_tp_aug14)
grid()

# TSS
bounce_tss_aug14 <- lm(tss_8_14 ~ bounce_aug14)
plot(bounce_aug14, tss_8_14, xlab = "Bounce (ft)", ylab = "Total Suspended Solids", pch = 16, col = "lightslateblue", bg="transparent")
abline(bounce_tss_aug14)
grid()

# Nitrate
bounce_nitrate_aug14 <- lm(nitrate_8_14 ~ bounce_aug14)
plot(bounce_aug14, nitrate_8_14, xlab = "Bounce (ft)", ylab = "Nitrate", pch = 16, col = "mediumpurple", bg="transparent")
abline(bounce_nitrate_aug14)
grid()

# Ammonia
bounce_ammonia_aug14 <- lm(ammonia_8_14 ~ bounce_aug14)
plot(bounce_aug14, ammonia_8_14, xlab = "Bounce (ft)", ylab = "Ammonia", pch = 16, col = "mediumpurple3", bg="transparent")
abline(bounce_ammonia_aug14)
grid()


# September 24 Storm
# Chloride
bounce_chlor_sept24 <- lm(chloride_9_24 ~ bounce_sept24)
plot(bounce_sept24, chloride_9_24, xlab = "Bounce (ft)", ylab = "Chloride", pch = 16, col = "lightblue", bg="transparent")
abline(bounce_chlor_sept24)
grid()

# DO
bounce_do_sept24 <- lm(do_9_24 ~ bounce_sept24)
plot(bounce_sept24, do_9_24, xlab = "Bounce (ft)", ylab = "Dissolved Oxygen", pch = 16, col = "lightblue3", bg="transparent")
abline(bounce_do_sept24)
grid()

# Secchi
bounce_secchi_sept24 <- lm(secchi_9_24 ~ bounce_sept24)
plot(bounce_sept24, secchi_9_24, xlab = "Bounce (ft)", ylab = "Water Clarity", pch = 16, col = "lightblue4", bg="transparent")
abline(bounce_secchi_sept24)
grid()

# Sulfate
bounce_sulfate_sept24 <- lm(sulfate_9_24 ~ bounce_sept24)
plot(bounce_sept24, sulfate_9_24, xlab = "Bounce (ft)", ylab = "Sulfate", pch = 16, col = "lightgreen", bg="transparent")
abline(bounce_sulfate_sept24)
grid()

# Temp
bounce_temp_sept24 <- lm(temp_9_24 ~ bounce_sept24)
plot(bounce_sept24, temp_9_24, xlab = "Bounce (ft)", ylab = "Temperature", pch = 16, col = "palegreen", bg="transparent")
abline(bounce_temp_sept24)
grid()

# TN
bounce_tn_sept24 <- lm(tn_9_24 ~ bounce_sept24)
plot(bounce_sept24, tn_9_24, xlab = "Bounce (ft)", ylab = "Total Nitrogen", pch = 16, col = "palegreen3", bg="transparent")
abline(bounce_tn_sept24)
grid()

# TP
bounce_tp_sept24 <- lm(tp_9_24 ~ bounce_sept24)
plot(bounce_sept24, tp_9_24, xlab = "Bounce (ft)", ylab = "Total Phosphorous", pch = 16, col = "palegreen4", bg="transparent")
abline(bounce_tp_sept24)
grid()

# TSS
bounce_tss_sept24 <- lm(tss_9_24 ~ bounce_sept24)
plot(bounce_sept24, tss_9_24, xlab = "Bounce (ft)", ylab = "Total Suspended Solids", pch = 16, col = "lightslateblue", bg="transparent")
abline(bounce_tss_sept24)
grid()

# Nitrate
bounce_nitrate_sept24 <- lm(nitrate_9_24 ~ bounce_sept24)
plot(bounce_sept24, nitrate_9_24, xlab = "Bounce (ft)", ylab = "Nitrate", pch = 16, col = "mediumpurple", bg="transparent")
abline(bounce_nitrate_sept24)
grid()

# Ammonia
bounce_ammonia_sept24 <- lm(ammonia_9_24 ~ bounce_sept24)
plot(bounce_sept24, ammonia_9_24, xlab = "Bounce (ft)", ylab = "Ammonia", pch = 16, col = "mediumpurple3", bg="transparent")
abline(bounce_ammonia_sept24)
grid()

# SPC
bounce_spc_sept24 <- lm(spc_9_24 ~ bounce_sept24)
plot(bounce_sept24, spc_9_24, xlab = "Bounce (ft)", ylab = "Specific Conductance", pch = 16, col = "darkslateblue", bg="transparent")
abline(bounce_spc_sept24)
grid()

```

