---
title: "Inflow_Rate"
author: "Hannah Curtis"
date: "2024-01-30"
output: html_document
---
This file calculates the slope of the increase in water level for several storms as the rate of inflow in each pond. The storms included are 7/28, 8/14, and 9/25. 

Need to add remaining watershed areas.

Updated: 3/5/24

Read in water level files
```{r}
baxter_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Baxter/Baxter_Water_Level.csv")
commave_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/CommAve/CommAve_Water_Level.csv")
doba4_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA4/DobA4_Water_Level.csv")
doba5_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA5/DobA5_Water_Level.csv")
doba7_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA7/DobA7_Water_Level.csv")
doba8_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA8/DobA8_Water_Level.csv")
doba22_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA22/DobA22_Water_Level.csv")
doorcreek_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DoorCreek/DoorCreek_Water_Level.csv")
elver_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Elver/Elver_Water_Level.csv")
garner_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Garner/Garner_Water_Level.csv")
greentree_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Greentree/Greentree_Water_Level.csv")
hospital_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Hospital/Hospital_Water_Level.csv")
hpchurch_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/HPChurch/HPChurch_Water_Level.csv")
lot60_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Lot60/Lot60_Water_Level.csv")
madcity_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/MadCity/MadCity_Water_Level.csv")
manitou_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Manitou/Manitou_Water_Level.csv")
mariondunn_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/MarionDunn/MarionDunn_Water_Level.csv")
midtown_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Midtown/Midtown_Water_Level.csv")
owen_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Owen/Owen_Water_Level.csv")
twofountains_wl <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/TwoFountains/TwoFountains_Water_Level.csv")
```

Pond and watershed areas
```{r}
#without doba5 and midtown for storm one
pond_areas_1 <- c(41430, 54475, 32388, 186680, 25596, 159671, 50304, 93049, 51799, 79133, 59167, 64464, 29134, 16998, 13893, 48773, 114855, 45805)
#without doba5 and midtown for storm one
watershed_areas_1 <- c(1, 1, 2507478, 24962828, 4990450, 1, 1, 1, 1, 1, 10782337, 20726969, 6311395, 2160762, 3734247, 511053, 40122697, 6437832)

pond_areas <- c(41430, 54475, 32388, 186680, 25596, 159671, 50304, 48765, 93049, 51799, 79133, 59167, 64464, 29134, 16998, 13893, 39806, 48773, 114855, 45805)

watershed_areas <- c(1, 1, 2507478, 24962828, 4990450, 1, 1, 3446096, 1, 1, 1, 10782337, 20726969, 6311395, 2160762, 3734247, 4732612, 511053, 40122697, 6437832)
```

Function for finding inflow rate
```{r}
# Function for finding inflow rate
get_inflow_rate <- function(pond_wl, pond_datetime, start_time, end_time) {
  y <- pond_wl[start_time: end_time]
  x_seq <- seq_along(y)
  x <- x_seq
  model <- lm(y ~ x)
  slope <- coef(model)[2]
  return(slope*(1440/5))
}

```

Plot pond function
```{r}
plot_pond <- function(pond_dates, depth, col, name, outlet_depth) {
  plot(depth, type="l", col=col, lwd=3, pch=17, ylim = c(0,7),
     main=paste(name,"Water Level"), 
     xlab="Date", 
     ylab="Water Level (feet)", xaxt='n')
    # add a date axis
  grid()
  abline(h=outlet_depth, col="black", lwd=3)
  legend("topright",c("Outlet Location"), 
     col=c("black"), lty=1, lwd=3)
  get_dates <- function(datetime) {
    d = strsplit(datetime,' ')[[1]][1]
    d = strsplit(d,'/')[[1]]
    return(paste(d[1], '/', d[2], sep=""))
  }
  
  dates = lapply(pond_dates,get_dates)
  idx_change=c()
  last_d = 0
  for (i in 1:length(dates)) {
    if (dates[[i]] != last_d) {
      idx_change = append(idx_change, i)
      last_d = dates[i]
    }
  }
    
  axis(1,at=idx_change,labels=dates[idx_change])
}
```

Plotting water level to determine start and end times
```{r}

get_date_plot <- function(pond_wl, pond_datetime, start_time, end_time) {
 y <- pond_wl[start_time:end_time]
 x_seq <- seq_along(y)
 x <- x_seq
 model <- lm(y ~ x)
 plot_pond(pond_datetime[start_time:end_time], pond_wl[start_time:end_time], "lightblue", "", 0)
 abline(model, col = "black")
}

test <- get_date_plot(doba5_wl$Depth.ft, doba5_wl$DateTime, 13350, 13360)

```

Finding inflow rate for storm 1: 7/28
```{r}
# Inflow rate
baxter_inf_rate_1 <- get_inflow_rate(baxter_wl$Depth.ft, baxter_wl$DateTime, 22573, 22576)
commave_inf_rate_1 <- get_inflow_rate(commave_wl$Depth.ft, commave_wl$DateTime, 22517, 22522)
doba4_inf_rate_1 <- get_inflow_rate(doba4_wl$Depth.ft, doba4_wl$DateTime, 22531, 22539)
#doba5_inf_rate_1 <- get_inflow_rate(doba5_wl$Depth.ft, doba5_wl$DateTime)
doba7_inf_rate_1 <- get_inflow_rate(doba7_wl$Depth.ft, doba7_wl$DateTime, 22620, 22622)
doba8_inf_rate_1 <- get_inflow_rate(doba8_wl$Depth.ft, doba8_wl$DateTime, 22621, 22624)
doba22_inf_rate_1 <- get_inflow_rate(doba22_wl$Depth.ft, doba22_wl$DateTime,22562, 22566)
doorcreek_inf_rate_1 <- get_inflow_rate(doorcreek_wl$Depth.ft, doorcreek_wl$DateTime, 22540, 22550)
elver_inf_rate_1 <- get_inflow_rate(elver_wl$Depth.ft, elver_wl$DateTime, 22621, 22630)
garner_inf_rate_1 <- get_inflow_rate(garner_wl$Depth.ft, garner_wl$DateTime, 22620, 22624)
greentree_inf_rate_1 <- get_inflow_rate(greentree_wl$Depth.ft, greentree_wl$DateTime, 22622, 22628)
hospital_inf_rate_1 <- get_inflow_rate(hospital_wl$Depth.ft, hospital_wl$DateTime, 22619, 22624)
hpchurch_inf_rate_1 <- get_inflow_rate(hpchurch_wl$Depth.ft, hpchurch_wl$DateTime, 22501, 22508)
lot60_inf_rate_1 <- get_inflow_rate(lot60_wl$Depth.ft, lot60_wl$DateTime, 22618, 22628)
madcity_inf_rate_1 <- get_inflow_rate(madcity_wl$Depth.ft, madcity_wl$DateTime, 22621, 22623)
manitou_inf_rate_1 <- get_inflow_rate(manitou_wl$Depth.ft, manitou_wl$DateTime, 22620, 22624)
mariondunn_inf_rate_1 <- get_inflow_rate(mariondunn_wl$Depth.ft, mariondunn_wl$DateTime, 22620, 22624)
#midtown_inf_rate_1 <- get_inflow_rate(midtown_wl$Depth.ft, midtown_wl$DateTime)
owen_inf_rate_1 <- get_inflow_rate(owen_wl$Depth.ft, owen_wl$DateTime, 22619, 22624)
twofountains_inf_rate_1 <- get_inflow_rate(twofountains_wl$Depth.ft, twofountains_wl$DateTime, 22621, 22626)

inflow_rate_1 <- c(hospital_inf_rate_1,lot60_inf_rate_1,garner_inf_rate_1,doba7_inf_rate_1,owen_inf_rate_1,hpchurch_inf_rate_1,doba8_inf_rate_1,elver_inf_rate_1,twofountains_inf_rate_1,greentree_inf_rate_1,mariondunn_inf_rate_1,manitou_inf_rate_1,madcity_inf_rate_1,baxter_inf_rate_1,doba22_inf_rate_1,doba4_inf_rate_1,doorcreek_inf_rate_1,commave_inf_rate_1)

# Inflow rate/watershed area
inflow_1_wat_norm <- inflow_rate_1/watershed_areas_1

# Inflow rate/pond area
inflow_1_pond_norm <- inflow_rate_1/pond_areas_1
```

Finding inflow rate for storm 2: 8/14
```{r}
# Inflow rate
baxter_inf_rate_2 <- get_inflow_rate(baxter_wl$Depth.ft, baxter_wl$DateTime, 27315,27332)
commave_inf_rate_2 <- get_inflow_rate(commave_wl$Depth.ft, commave_wl$DateTime, 27220,27280)
doba4_inf_rate_2 <- get_inflow_rate(doba4_wl$Depth.ft, doba4_wl$DateTime, 27240,27305)
doba5_inf_rate_2 <- get_inflow_rate(doba5_wl$Depth.ft, doba5_wl$DateTime, 1020,1100)
doba7_inf_rate_2 <- get_inflow_rate(doba7_wl$Depth.ft, doba7_wl$DateTime, 27330,27390)
doba8_inf_rate_2 <- get_inflow_rate(doba8_wl$Depth.ft, doba8_wl$DateTime, 27330,27380)
doba22_inf_rate_2 <- get_inflow_rate(doba22_wl$Depth.ft, doba22_wl$DateTime, 27270,27330)
doorcreek_inf_rate_2 <- get_inflow_rate(doorcreek_wl$Depth.ft, doorcreek_wl$DateTime, 27240,27315)
elver_inf_rate_2 <- get_inflow_rate(elver_wl$Depth.ft, elver_wl$DateTime, 27335,27385)
garner_inf_rate_2 <- get_inflow_rate(garner_wl$Depth.ft, garner_wl$DateTime, 27325,2735)
greentree_inf_rate_2 <- get_inflow_rate(greentree_wl$Depth.ft, greentree_wl$DateTime, 27325,27382)
hospital_inf_rate_2 <- get_inflow_rate(hospital_wl$Depth.ft, hospital_wl$DateTime, 27330,27380)
hpchurch_inf_rate_2 <- get_inflow_rate(hpchurch_wl$Depth.ft, hpchurch_wl$DateTime, 27230,27270)
lot60_inf_rate_2 <- get_inflow_rate(lot60_wl$Depth.ft, lot60_wl$DateTime, 27300,27390)
madcity_inf_rate_2 <- get_inflow_rate(madcity_wl$Depth.ft, madcity_wl$DateTime, 27335,27380)
manitou_inf_rate_2 <- get_inflow_rate(manitou_wl$Depth.ft, manitou_wl$DateTime, 27330,27380)
mariondunn_inf_rate_2 <- get_inflow_rate(mariondunn_wl$Depth.ft, mariondunn_wl$DateTime, 27330,27380)
midtown_inf_rate_2 <- get_inflow_rate(midtown_wl$Depth.ft, midtown_wl$DateTime, 1350,1430)
owen_inf_rate_2 <- get_inflow_rate(owen_wl$Depth.ft, owen_wl$DateTime, 27320,27380)
twofountains_inf_rate_2 <- get_inflow_rate(twofountains_wl$Depth.ft, twofountains_wl$DateTime, 26500,27400)

inflow_rate_2 <- c(hospital_inf_rate_2,lot60_inf_rate_2,garner_inf_rate_2,doba7_inf_rate_2,owen_inf_rate_2,hpchurch_inf_rate_2,doba8_inf_rate_2,midtown_inf_rate_2,elver_inf_rate_2,twofountains_inf_rate_2,greentree_inf_rate_2,mariondunn_inf_rate_2,manitou_inf_rate_2,madcity_inf_rate_2,baxter_inf_rate_2,doba22_inf_rate_2,doba5_inf_rate_2,doba4_inf_rate_2,doorcreek_inf_rate_2,commave_inf_rate_2)

# Inflow rate/watershed area
inflow_2_wat_norm <- inflow_rate_2/watershed_areas

# Inflow rate/pond area
inflow_2_pond_norm <- inflow_rate_2/pond_areas
```

Finding inflow rate for storm 3: 9/25
```{r}
# Inflow rate
baxter_inf_rate_3 <- get_inflow_rate(baxter_wl$Depth.ft, baxter_wl$DateTime, 39310,39660)
commave_inf_rate_3 <- get_inflow_rate(commave_wl$Depth.ft, commave_wl$DateTime, 39540,39550)
doba4_inf_rate_3 <- get_inflow_rate(doba4_wl$Depth.ft, doba4_wl$DateTime, 39550,39570)
doba5_inf_rate_3 <- get_inflow_rate(doba5_wl$Depth.ft, doba5_wl$DateTime, 13350, 13360)
doba7_inf_rate_3 <- get_inflow_rate(doba7_wl$Depth.ft, doba7_wl$DateTime, 39500,39700)
doba8_inf_rate_3 <- get_inflow_rate(doba8_wl$Depth.ft, doba8_wl$DateTime, 39500,39700)
doba22_inf_rate_3 <- get_inflow_rate(doba22_wl$Depth.ft, doba22_wl$DateTime, 39570,39650)
doorcreek_inf_rate_3 <- get_inflow_rate(doorcreek_wl$Depth.ft, doorcreek_wl$DateTime, 39550,39600)
elver_inf_rate_3 <- get_inflow_rate(elver_wl$Depth.ft, elver_wl$DateTime, 39630,39710)
garner_inf_rate_3 <- get_inflow_rate(garner_wl$Depth.ft, garner_wl$DateTime, 39630,39710)
greentree_inf_rate_3 <- get_inflow_rate(greentree_wl$Depth.ft, greentree_wl$DateTime, 39620,39700)
hospital_inf_rate_3 <- get_inflow_rate(hospital_wl$Depth.ft, hospital_wl$DateTime, 39635,39695)
hpchurch_inf_rate_3 <- get_inflow_rate(hpchurch_wl$Depth.ft, hpchurch_wl$DateTime, 39500,39620)
lot60_inf_rate_3 <- get_inflow_rate(lot60_wl$Depth.ft, lot60_wl$DateTime, 39600,39720)
madcity_inf_rate_3 <- get_inflow_rate(madcity_wl$Depth.ft, madcity_wl$DateTime, 39630,39695)
manitou_inf_rate_3 <- get_inflow_rate(manitou_wl$Depth.ft, manitou_wl$DateTime, 39640,39705)
mariondunn_inf_rate_3 <- get_inflow_rate(mariondunn_wl$Depth.ft, mariondunn_wl$DateTime, 39600,39700)
midtown_inf_rate_3 <- get_inflow_rate(midtown_wl$Depth.ft, midtown_wl$DateTime, 13650, 13780)
owen_inf_rate_3 <- get_inflow_rate(owen_wl$Depth.ft, owen_wl$DateTime, 39620,39720)
twofountains_inf_rate_3 <- get_inflow_rate(twofountains_wl$Depth.ft, twofountains_wl$DateTime, 39680,39700)

inflow_rate_3 <- c(hospital_inf_rate_3,lot60_inf_rate_3,garner_inf_rate_3,doba7_inf_rate_3,owen_inf_rate_3,hpchurch_inf_rate_3,doba8_inf_rate_3,midtown_inf_rate_3,elver_inf_rate_3,twofountains_inf_rate_3,greentree_inf_rate_3,mariondunn_inf_rate_3,manitou_inf_rate_3,madcity_inf_rate_3,baxter_inf_rate_3,doba22_inf_rate_3,doba5_inf_rate_3,doba4_inf_rate_3,doorcreek_inf_rate_3,commave_inf_rate_3)

# Inflow rate/watershed area
inflow_3_wat_norm <- inflow_rate_3/watershed_areas

# Inflow rate/pond area
inflow_3_pond_norm <- inflow_rate_3/pond_areas
```
Save variables in csv file
```{r}
# Pond names
pond_names <- c("Hospital", "Lot60", "Garner", "DobA7", "Owen", "HPChurch", "DobA8", "Midtown", "Elver", "TwoFountains", "Greentree", "MarionDunn", "Manitou", "MadCity", "Baxter", "DobA22", "DobA5", "DobA4", "DoorCreek", "CommAve")

pond_names_1 <- c("Hospital", "Lot60", "Garner", "DobA7", "Owen", "HPChurch", "DobA8", "Elver", "TwoFountains", "Greentree", "MarionDunn", "Manitou", "MadCity", "Baxter", "DobA22", "DobA4", "DoorCreek", "CommAve")

# Create a data frame for all ponds
inflow_rate_1_df <- data.frame(Pond.Names = pond_names_1, Inflow.Rate = inflow_rate_1, Inflow.Wat.Norm = inflow_1_wat_norm, Inflow.Pond.Norm = inflow_1_pond_norm)
inflow_rate_2_df <- data.frame(Pond.Names = pond_names, Inflow.Rate = inflow_rate_2, Inflow.Wat.Norm = inflow_2_wat_norm, Inflow.Pond.Norm = inflow_2_pond_norm)
inflow_rate_3_df <- data.frame(Pond.Names = pond_names, Inflow.Rate = inflow_rate_3, Inflow.Wat.Norm = inflow_3_wat_norm, Inflow.Pond.Norm = inflow_3_pond_norm)

# Write csv for data frame
write.csv(inflow_rate_1_df, "/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Inflow_Rate/Inflow_Rate_1.csv")
write.csv(inflow_rate_2_df, "/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Inflow_Rate/Inflow_Rate_2.csv")
write.csv(inflow_rate_3_df, "/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Inflow_Rate/Inflow_Rate_3.csv")
```
