---
title: "Spatial Maps"
author: "Hannah Curtis"
date: "2024-01-18"
output: html_document
---

This file creates spatial heat maps of different variables at each pond on a map. The variables with maps include ammonia, chloride, dissolved oxygen, nitrate, secchi depth, specific conductance, sulfate, temperature (from YSI), total nitrogen, total phosphorous, total suspended solids, richness, and bounce.

Could add temperature from sensors, other aesthetic and rihness variables, and attenuation.

Updated: 3/5/24

Failed attempts (could be useful in the future if any were on the right track?)
```{r}
library(sf)
library(ggplot2)
library(leaflet)

# Provide the path to your shapefile
shapefile_path <- "/Users/hannahcurtis/Downloads/wi_blk10_Census_change_1990_2010_PLA2/wi_blk10_Census_change_1990_2010_PLA2.shp"

# Read the shapefile
shapefile <- st_read(shapefile_path)

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles() %>%
  addPolygons(data = shapefile)

# Print the map
print(my_map)
```

```{r}
library(ggplot2)
library(maps)
library(mapdata)
library(raster)

# Example data with latitude, longitude, and color
data <- data.frame(
  latitude = c(43.08113195, 43.07849119, 43.06354804, 43.0599518, 43.06867106, 43.0774902, 43.0382138, 43.0373738, 43.03801484, 43.044528, 43.04184272, 43.05201405, 43.04762, 43.0388574, 43.02946538, 43.02661718, 43.07498036, 43.09265805, 43.0966168, 43.10708),  # Example latitude values (Madison, WI)
  longitude = c(-89.42700781, -89.42924194, -89.4727964, -89.4994612, -89.48837267, -89.515668, -89.5224096, -89.5272514, -89.50464724, -89.499567, -89.49836001, -89.43511254, -89.43781, -89.42464823, -89.3707364, -89.28484903, -89.27972208, -89.26627707, -89.2513815, -89.29788),  # Example longitude values (Madison, WI)
  color = c("blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue", "blue") , # Different colors for each point
  label = c("Lot 60", "Hospital", "Garner Park", "Dobson A7", "Owen Park", "High Point Church", "Dobson A8", "Midtown Park", "Elver Park", "Two Fountains", "Greentree Park", "Marion-Dunn", "Manitou", "Mad         City", "Baxter Park", "Dobson A22", "Dobson A5", "Dobson A4", "Door Creek", "Commercial Ave")
)

# Create a map with ggplot2 and zoom in on Madison, WI
# world <- map_data("world")
# 
# ggplot() +
#   geom_polygon(data = world, aes(x = long, y = lat, group = group), fill = "lightgray") +
#   geom_point(data = data, aes(x = longitude, y = latitude, color = color), size = 3) +
#   scale_color_identity() +
#   coord_fixed(ratio = 1, xlim = c(-89.6, -89.2), ylim = c(42.95, 43.2)) +  # Adjust xlim and ylim for zooming in
#   theme_minimal()


# Replace "path/to/your/topographic/raster.tif" with the path to your raster file
raster_file <- "/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/WI_Madison_503660_1991_100000_geo.tif"

# Read the raster file
topo_raster <- raster(raster_file)

# Convert raster to data frame
raster_df <- as.data.frame(raster::rasterToPoints(topo_raster))

# Create a map with ggplot2 and zoom in on a specific region
ggplot(raster_df) +
  geom_raster(aes(x = x, y = y, fill = WI_Madison_503660_1991_100000_geo_1)) +  # Replace with your actual layer name
  scale_fill_gradient(low = "white", high = "brown") +
  coord_fixed(ratio = 1) +  # Adjust ratio as needed
  theme_minimal()

```

```{r}
library(ggmap)

# Replace "your_api_key" with your actual API key
register_google(key = "your_api_key")

# Get the map info
map <- get_googlemap("Montpellier, France", zoom = 8, maptype = "terrain")

# Plot it
ggmap(map) +
  theme_minimal() +
  ggtitle("terrain") +
  theme(
    plot.title = element_text(colour = "orange"),
    panel.border = element_rect(colour = "grey", fill = NA, size = 2)
  )
```

```{r}
# Read the raster file
topo_raster <- raster("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/WI_Madison_503660_1991_100000_geo.tif")

# Convert raster to data frame
raster_df <- as.data.frame(raster::rasterToPoints(topo_raster))

# Print column names
print(names(raster_df))

# View the first few rows of the data frame
head(raster_df)
```

```{r}
library(sf)

# Read shapefile
shape_data <- st_read("/Users/hannahcurtis/Downloads/Stormwater_Impervious_Areas/Stormwater_Impervious_Areas.shp")


plot(shape_data, main = "Map")
```

```{r}
library(jpeg)
library(ggplot2)

map <- readJPEG("/Users/hannahcurtis/Downloads/Madison-Road-Map.jpg")

# Plot the RGB image
plot(map)
# plot(1:1159, 1:1159, type = "n", xlab = "", ylab = "", xlim=c(300,1159))
# rasterImage(map, 1, 1, 1500, 1159)
```

Actual Maps

Ammonia
```{r}
# load leaflet library 
library(leaflet) 
library(webshot)
library(htmlwidgets)
  
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(92.609625, 66.692625, 45.22825, 101.079, 16.478125, 28.572125, 14.525625, 21.787, 46.137125, 83.25975, 89.519875, 152.29425, 63.303, 92.69075, 147.3645, 91.70475, 67.893375, 15.57925, 45.50925, 39.942625)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg Ammonia (ug/L)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "ammonia_map.png", cliprect = "viewport")
```

Chloride
```{r}

# load leaflet library 
library(leaflet) 
library(webshot)
library(htmlwidgets)
  
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(207.77835, 85.32650, 144.70427, 49.33224, 34.19063, 50.42339, 14.59083, 24.17945, 70.20994, 67.92615, 79.85977, 38.20219, 78.98981, 68.25674, 14.40198, 12.25736, 39.68091, 17.87927, 40.39244, 12.32787)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg Chloride (mg/L)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "chloride_map.png", cliprect = "viewport")
```

Dissolved Oxygen
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(1.47000, 4.44250, 3.49250, 7.43250, 3.54500, 4.96375, 4.00875, 7.17125, 4.61500, 8.83250, 4.49125, 6.40000, 9.92000, 5.72375, 5.77125, 6.90000, 13.87000, 11.53000, 8.43000, 11.56000)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg DO (mg/L)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "DO_map.png", cliprect = "viewport")
```

Nitrate
```{r}
# load leaflet library 
library(leaflet) 
library(webshot)
library(htmlwidgets)
  
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(21.95525, 155.7655, 47.12475, 98.664625, 16.21325, 52.441125, 27.654375, 14.27075, 29.032875, 9.91725, 71.842125, 42.465375, 40.108125, 55.46225, 38.38525, 72.68525, 21.48325, 1.8325, 9.0675, 11.010625)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg Nitrate (ug/L)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "nitrate_map.png", cliprect = "viewport")
```

Secchi Depth
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(42.6875, 59.7500, 27.5250, 24.0000, 35.6500, 46.9250, 43.3750, 53.6250, 43.3125, 56.4375, 37.5000, 36.1750, 21.6875, 34.9500, 30.3375, 34.1750, 9.5625, 21.3750, 47.1000, 22.9250)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg Secchi Depth (cm)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "Secchi_map.png", cliprect = "viewport")
```

Specific Conductance
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(474.100, 656.120, 751.860, 326.420, 247.660, 140.440, 145.560, 76.750, 383.380, 347.040, 405.660, 85.360, 526.540, 133.140, 117.000, 130.550, 146.150, 165.560, 266.480, 90.546)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg SPC",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "SPC_map.png", cliprect = "viewport")
```

Sulfate
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(4.080800, 10.465925, 2.731438, 4.011838, 7.813544, 2.647844, 1.379738, 1.808775, 4.236813, 1.266750, 4.467937, 1.988575, 6.241062, 6.932175, 1.864613, 10.547019, 1.954725, 1.790325, 6.397775, 1.782350)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg Sulfate (mg/L)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "sulfate_map.png", cliprect = "viewport")
```

Temperature
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(19.91250, 21.21429, 21.27500, 21.46250, 21.65714, 21.30000, 21.60000, 22.95000, 22.18750, 24.28750, 23.82500, 25.12500, 25.12500, 25.06250, 26.68750, 26.85000, 26.77500, 26.35000, 26.21250, 25.90000)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg Temperature (C)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "temp_map.png", cliprect = "viewport")
```

Total Nitrogen
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(1303.6831, 544.6941, 1077.6535, 632.3016, 1527.6194, 513.3200, 620.2096, 693.9916, 539.2664, 678.0339, 711.1176, 952.7874, 1436.5632, 1167.5756, 1652.8053, 1599.1759, 2155.1586, 694.2777, 1119.5599, 1478.5155)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg TN (ug/L)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "TN_map.png", cliprect = "viewport")
```

Total Phosphorous
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(131.65375, 30.96312, 138.21525, 60.18650, 232.06238, 117.10263, 81.39037, 82.98538, 92.30213, 73.52738, 131.90062, 164.91887, 185.41163, 145.95250, 398.37000, 253.59750, 136.67625, 89.60675, 145.50475, 202.85850)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg TP (ug/L)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "TP_map.png", cliprect = "viewport")
```

Total Suspended Solids
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(64.784375, 7.768750, 26.721875, 22.331250, 19.811012, 9.966667, 45.587500, 24.105000, 21.282459, 9.703125, 40.656250, 39.987500, 30.895994, 10.393750, 62.793750, 17.193750, 28.005242, 26.199510, 27.753912, 27.729281)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg TSS (mg/L)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "TSS_map.png", cliprect = "viewport")
```

Richness
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(29, 50, 24, 23, 28, 38, 23, 29, 31, 27, 34, 27, 29, 26, 38, 22, 19, 31, 45, 27)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Species Richness",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "richness_map.png", cliprect = "viewport")
```

Bounce
```{r}
my_data <- data.frame(
  lat = c(43.0811, 43.0785, 43.0635, 43.0599, 43.0687, 43.0775, 43.0382, 43.0374, 43.0380, 43.0445, 43.0418, 43.0520, 43.0476, 43.0389, 43.0295, 43.0266, 43.0750, 43.0927, 43.0966, 43.1071),
  lon = c(-89.4270, -89.4292, -89.4728, -89.4995, -89.4884, -89.5157, -89.5224, -89.5273, -89.5046, -89.4996, -89.4984, -89.4351, -89.4378, -89.4246, -89.3707, -89.2848, -89.2797, -89.2663, -89.2514, -89.2979),
  value = c(1.3159187, 0.8809523, 1.9672685, 2.0760119, 2.6351491, 3.1325106, 1.9654701, 1.3247419, 2.2928970, 0.6734912, 2.2083635, 3.4292906, 2.5903646, 1.8474522, 1.7557422, 2.7115997, 1.2826354, 1.3584409, 0.7349667, 1.9438863)
)

# Create a continuous palette function
pal <- colorNumeric(
  palette = "viridis",
  domain = my_data$value)

# Popup text (you can customize this accordingly)
popup_text <- paste("Marker", 1:length(my_data$lat))

# Create a leaflet map
my_map <- leaflet() %>%
  addTiles()

# Add circle markers to the map
my_map <- addCircleMarkers(
  my_map,
  lng = my_data$lon,
  lat = my_data$lat,
  radius = 5,  # Set the radius of the dots (adjust as needed)
  fillOpacity = 0.7,  # Set the fill opacity
  color = pal(my_data$value),  # Set the border color
  fillColor = pal(my_data$value),  # Set the fill color
  popup = popup_text
) %>%
  addLegend(
    pal = pal,
    values = my_data$value,
    title = "Avg Bounce (ft)",
    opacity = 0.7
) %>%
  setView(lng = -89.390973, lat = 43.067398, zoom = 11)  # Set your desired coordinates and zoom level

# Display the map
my_map

# Save a portion of the map as an image
htmlwidgets::saveWidget(my_map, file = "my_map.html", selfcontained = FALSE)
webshot::webshot("my_map.html", file = "bounce_map.png", cliprect = "viewport")
```

