---
title: "Response Variables"
author: "Hannah Curtis"
date: "2024-01-11"
output: html_document
---
This file creates boxplots for all of the response variables with multiple values per pond, including the water quality parameters of secchi depth, chloride, dissolved oxygen, specific conductance, sulfate, temperature (from YSI), total nitrogen, total phosphorous, total suspended solids, nitrate, and ammonia. Can come back and add aesthetic parameters (range of trash, odor, recreation) and attenuation values for each storm. Could also create a boxplot of bounce for each storm.

Updated: 3/5/24

Read in files
```{r}
secchi <- read.csv('/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Secchi_Depth.csv')
chloride <- read.csv('/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Chloride.csv')
DO <- read.csv('/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/DissolvedOxygen.csv')
SPC <- read.csv('/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/SPC.csv')
sulfate <- read.csv('/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Sulfate.csv')
temp <- read.csv('/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Temperature.csv')
TN <- read.csv('/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/TotalNitrogen.csv')
TP <- read.csv('/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/TotalPhosphorous.csv')
TSS <- read.csv('/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/TSS.csv')
nitrate <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/Nitrate Data.csv")

#set colors for each box
boxplot_colors <- c("dodgerblue4", "red", "gray", "green", "gold", "magenta", "orange", "purple", "brown", "skyblue", "coral1", "lavender", "forestgreen", "yellow", "maroon", "pink", "royalblue", "lightsalmon", "tan", "darkgray")
```

Secchi Disk Boxplot
```{r}
# Get pond names from csv file
pond_name <- secchi$Pond.Name
# Get secchi depths
secchi_depth <- secchi$Secchi.Disk.Depth..cm.
# Move labels of plot to fit pond names
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))

# Plot secchi depths in boxplot
boxplot(secchi_depth ~ pond_name, data = secchi, las=2, main="Water Clarity", xlab="", ylab="Secchi Depth (cm)", col=boxplot_colors, cex.axis=1, cex.lab = 1, cex.main = 1)
mtext("Pond", side = 1, line =8, adj = 0.5)

```

Chloride Boxplot
```{r}
pond_name <- chloride$Pond.Name
chloride_conc <- chloride$Chloride..mg.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(chloride_conc ~ pond_name, data = chloride, las=2, main="Chloride", xlab="", ylab="Chloride Concentration (mg/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)
```

DO Boxplot
```{r}
pond_name <- DO$Pond.Name
DO_conc <- DO$YSI.DO..mg.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(DO_conc ~ pond_name, data = DO, las=2, main="Dissolved Oxygen", xlab="", ylab="DO Concentration (mg/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)
```

SPC Boxplot
```{r}
pond_name <- SPC$Pond.Name
SPC_conc <- SPC$SPC
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(SPC_conc ~ pond_name, data = SPC, las=2, main="Specific Conductance", xlab="", ylab="SPC (S/cm)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)
```

Sulfate Boxplot
```{r}
pond_name <- sulfate$Pond.Name
sulfate_conc <- sulfate$Sulfate..mg.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(sulfate_conc ~ pond_name, data = sulfate, las=2, main="Sulfate", xlab="", ylab="Sulfate Concentration (mg/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)
```

Temperature Boxplot
```{r}
pond_name <- temp$Pond.Name
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(temperature ~ pond_name, data = temp, las=2, main="Temperature", xlab="", ylab="Temperature (degrees C)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)
```

TN Boxplot
```{r}
pond_name <- TN$Pond.Name
TN_conc <- TN$TN..ug.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(TN_conc ~ pond_name, data = TN, las=2, main="Total Nitrogen", xlab="", ylab="TN Concentration (mg/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)
```

TP Boxplot
```{r}
pond_name <- TP$Pond.Name
TP_conc <- TP$TP..ug.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(TP_conc ~ pond_name, data = TP, las=2, main="Total Phosphorous", xlab="", ylab="TP Concentration (mg/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)
```

TSS Boxplot
```{r}
pond_name <- TSS$Pond.Name
TSS_conc <- TSS$TSS..mg.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(TSS_conc ~ pond_name, data = TSS, las=2, main="Total Suspended Solids", xlab="", ylab="TSS Concentration (mg/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)
```

Nitrate/Ammonia Boxplot
```{r}
# nitrate
pond_name <- nitrate$Pond.Name
nitrate_conc <- nitrate$Nitrate..ug.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(nitrate_conc ~ pond_name, data = nitrate, las=2, main="Nitrate", xlab="", ylab="Nitrate Concentration (ug/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)

# nitrate where values below LOD are set to half LOD
pond_name <- nitrate$Pond.Name
nitrate_lod_conc <- nitrate$Nitrate.LOD..ug.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(nitrate_lod_conc ~ pond_name, data = nitrate, las=2, main="Nitrate LOD", xlab="", ylab="Nitrate LOD Concentration (ug/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)

# ammonia
pond_name <- nitrate$Pond.Name
ammonia_conc <- nitrate$Ammonia..ug.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(ammonia_conc ~ pond_name, data = nitrate, las=2, main="Ammonia", xlab="", ylab="Ammonia Concentration (ug/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)

# ammonia where values below LOD are set to half LOD
pond_name <- nitrate$Pond.Name
ammonia_lod_conc <- nitrate$Ammonia.LOD..ug.L.
par(plt = c(0.1, 0.9, 0.1, 0.9), mar = c(10, 5, 2, 10))
boxplot(ammonia_lod_conc ~ pond_name, data = nitrate, las=2, main="Ammonia LOD", xlab="", ylab="Ammonia LOD Concentration (ug/L)", col=boxplot_colors)
mtext("Pond", side = 1, line =8, adj = 0.5)


```

