---
title: "Technical_Note_Results"
output: html_document
date: "2024-09-13"
---

```{r}
source("reverse_puls.R")

library(ggplot2)
library(BSDA)
library(plyr)
library(RColorBrewer)

# read water level files
# garner
garner <- read.csv("Inflow_Outflow/Garner_Water_Level_all.csv")
depth_gar <- garner$Depth.ft
smooth_depth_gar <- smooth_elevation(depth_gar)
datetime_gar <- as.POSIXct(garner$DateTime, format = "%m/%d/%y %H:%M")

# doba5
doba5 <- read.csv("Inflow_Outflow/DobA5_Water_Level_all.csv")
depth_da5 <- doba5$Depth.ft
smooth_depth_da5 <- smooth_elevation(depth_da5)
datetime_da5 <- as.POSIXct(doba5$DateTime, format = "%m/%d/%y %H:%M")

# midtown
midtown <- read.csv("Inflow_Outflow/Midtown_Water_Level_all.csv")
depth_mid <- midtown$Depth.ft
smooth_depth_mid <- smooth_elevation(depth_mid)
datetime_mid <- as.POSIXct(midtown$DateTime, format = "%m/%d/%y %H:%M")

# baxter
baxter <- read.csv("Inflow_Outflow/Baxter_Water_Level_all.csv")
depth_bax <- baxter$Depth.ft
smooth_depth_bax <- smooth_elevation(depth_bax)
datetime_bax <- as.POSIXct(baxter$DateTime, format = "%m/%d/%y %H:%M")

# SWMM Inflow df
swmm_inflow_df <- read.csv("SWMM__Inflow.csv")
swmm_inflow <- swmm_inflow_df$Inflow.cfs
swmm_time <- as.POSIXct(swmm_inflow_df$Hours, format = "%H:%M")

# SWMM Weir H=5, L=10
swmm_h5l10_df <- read.csv("SWMM_H5_L10.csv")
swmm_h5l10_stage <- swmm_h5l10_df$Depth.ft
swmm_h5l10_outflow <- swmm_h5l10_df$Outflow.cfs

# SWMM Weir H=5, L=5
swmm_h5l5_df <- read.csv("SWMM_H5_L5.csv")
swmm_h5l5_stage <- swmm_h5l5_df$Depth.ft
swmm_h5l5_outflow <- swmm_h5l5_df$Outflow.cfs

# SWMM Weir H=5, L=1
swmm_h5l1_df <- read.csv("SWMM_H5__L1.csv")
swmm_h5l1_stage <- swmm_h5l1_df$Depth.ft
swmm_h5l1_outflow <- swmm_h5l1_df$Outflow.cfs

# SWMM Weir H=2, L=1
swmm_h2l1_df <- read.csv("SWMM_H2_L1.csv")
swmm_h2l1_stage <- swmm_h2l1_df$Depth.cfs
swmm_h2l1_outflow <- swmm_h2l1_df$Outflow.cfs

#Atten Table Base
atten_base_df <- read.csv("Atten_Results_Base.csv")
atten_base_large_df <- read.csv("Atten_Results_Large_Storm_Base.csv")
atten_base_small_df <- read.csv("Atten_Results_Small_Storm_Base.csv")

#Atten Table Smoothed
atten_smooth_df <- read.csv("Atten_Results_Smoothed.csv")
atten_smooth_large_df <- read.csv("Atten_Results_Large_Storm_Smoothed.csv")
atten_smooth_small_df <- read.csv("Atten_Results_Small_Storm_Smoothed.csv")

```

```{r}
plot(swmm_h5l1_outflow[1:50], swmm_h5l1_stage[1:50], type = "l")
```


Colors
```{r}

# Extract colors from a specific palette
# For example, using the "Set1" palette with 3 colors
colors <- brewer.pal(4, "Greens")

colors_red <- brewer.pal(5, "Reds")

colors_blue <- brewer.pal(5, "Blues")

#colors_green <- brewer.pal(5, "Greens")
```

Get smoothed results H5L10
```{r}
# 3-point average
smoothed_depth_swmm_h5l10 <- smooth_elevation(swmm_h5l10_stage)
smoothed_results_swmm_h5l10 <- get_inflow_outflow_swmm(smoothed_depth_swmm_h5l10, 0, 0, 184, 80,  0, 3.33, 3.3, 60)
# Transform to 2-min
depth_swmm_h5l10_2min <- aggregate_data(swmm_h5l10_df, "Hours", "Depth.ft", 2)
time_swmm_h5l10_2min <- as.POSIXct(depth_swmm_h5l10_2min$Hours, format = "%H:%M")
twomin_results_swmm_h5l10 <- get_inflow_outflow_swmm(depth_swmm_h5l10_2min$Depth.ft, 0, 0, 184, 80,  0, 3.33, 3.3, 120)
# Transform to 3-min
depth_swmm_h5l10_3min <- aggregate_data(swmm_h5l10_df, "Hours", "Depth.ft", 3)
time_swmm_h5l10_3min <- as.POSIXct(depth_swmm_h5l10_3min$Hours, format = "%H:%M")
threemin_results_swmm_h5l10 <- get_inflow_outflow_swmm(depth_swmm_h5l10_3min$Depth.ft, 0, 0, 184, 80,  0, 3.33, 3.3, 180)
# Transform to 5-min
depth_swmm_h5l10_5min <- aggregate_data(swmm_h5l10_df, "Hours", "Depth.ft", 5)
time_swmm_h5l10_5min <- as.POSIXct(depth_swmm_h5l10_5min$Hours, format = "%H:%M")
fivemin_results_swmm_h5l10 <- get_inflow_outflow_swmm(depth_swmm_h5l10_5min$Depth.ft, 0, 0, 184, 80,  0, 3.33, 3.3, 300)
# Transform to 15-min
depth_swmm_h5l10_15min <- aggregate_to_15min(depth_swmm_h5l10_5min, "Hours", "Depth.ft")
fifteenmin_results_swmm_h5l10 <- get_inflow_outflow_swmm(depth_swmm_h5l10_15min$Depth.ft, 0, 0, 184, 80,  0, 3.33, 3.3, 900)
time_swmm_h5l10_15min <- as.POSIXct(depth_swmm_h5l10_15min$Hours, format = "%H:%M")

```

Get smoothed results H5L5
```{r}
# 3-point average
smoothed_depth_swmm_h5l5 <- smooth_elevation(swmm_h5l5_stage)
smoothed_results_swmm_h5l5 <- get_inflow_outflow_swmm(smoothed_depth_swmm_h5l5, 0, 0, 184, 98, 0, 3.33, 3.3, 60)
# Transform to 2-min
depth_swmm_h5l5_2min <- aggregate_data(swmm_h5l5_df, "Hours", "Depth.ft", 2)
time_swmm_h5l5_2min <- as.POSIXct(depth_swmm_h5l5_2min$Hours, format = "%H:%M")
twomin_results_swmm_h5l5 <- get_inflow_outflow_swmm(depth_swmm_h5l5_2min$Depth.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 120)
# Transform to 3-min
depth_swmm_h5l5_3min <- aggregate_data(swmm_h5l5_df, "Hours", "Depth.ft", 3)
time_swmm_h5l5_3min <- as.POSIXct(depth_swmm_h5l5_3min$Hours, format = "%H:%M")
threemin_results_swmm_h5l5 <- get_inflow_outflow_swmm(depth_swmm_h5l5_3min$Depth.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 180)
# Transform to 5-min
depth_swmm_h5l5_5min <- aggregate_data(swmm_h5l5_df, "Hours", "Depth.ft", 5)
time_swmm_h5l5_5min <- as.POSIXct(depth_swmm_h5l5_5min$Hours, format = "%H:%M")
fivemin_results_swmm_h5l5 <- get_inflow_outflow_swmm(depth_swmm_h5l5_5min$Depth.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 300)
# Transform to 15-min
depth_swmm_h5l5_15min <- aggregate_to_15min(depth_swmm_h5l5_5min, "Hours", "Depth.ft")
fifteenmin_results_swmm_h5l5 <- get_inflow_outflow_swmm(depth_swmm_h5l5_15min$Depth.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 900)
time_swmm_h5l5_15min <- as.POSIXct(depth_swmm_h5l5_15min$Hours, format = "%H:%M")

```

Get smoothed results H5L1
```{r}
# 3-point average
smoothed_depth_swmm_h5l1 <- smooth_elevation(swmm_h5l1_stage)
smoothed_results_swmm_h5l1 <- get_inflow_outflow_swmm(smoothed_depth_swmm_h5l1, 0, 0, 184, 200,  0, 3.33, 3.3, 60)
# Transform to 2-min
depth_swmm_h5l1_2min <- aggregate_data(swmm_h5l1_df, "Hours", "Depth.ft", 2)
time_swmm_h5l1_2min <- as.POSIXct(depth_swmm_h5l1_2min$Hours, format = "%H:%M")
twomin_results_swmm_h5l1 <- get_inflow_outflow_swmm(depth_swmm_h5l1_2min$Depth.ft, 0, 0, 184, 200,  0, 3.33, 3.3, 120)
# Transform to 3-min
depth_swmm_h5l1_3min <- aggregate_data(swmm_h5l1_df, "Hours", "Depth.ft", 3)
time_swmm_h5l1_3min <- as.POSIXct(depth_swmm_h5l1_3min$Hours, format = "%H:%M")
threemin_results_swmm_h5l1 <- get_inflow_outflow_swmm(depth_swmm_h5l1_3min$Depth.ft, 0, 0, 184, 200,  0, 3.33, 3.3, 180)
# Transform to 5-min
depth_swmm_h5l1_5min <- aggregate_data(swmm_h5l1_df, "Hours", "Depth.ft", 5)
time_swmm_h5l1_5min <- as.POSIXct(depth_swmm_h5l1_5min$Hours, format = "%H:%M")
fivemin_results_swmm_h5l1 <- get_inflow_outflow_swmm(depth_swmm_h5l1_5min$Depth.ft, 0, 0, 184, 200,  0, 3.33, 3.3, 300)
# Transform to 15-min
depth_swmm_h5l1_15min <- aggregate_to_15min(depth_swmm_h5l1_5min, "Hours", "Depth.ft")
fifteenmin_results_swmm_h5l1 <- get_inflow_outflow_swmm(depth_swmm_h5l1_15min$Depth.ft, 0, 0, 184, 200,  0, 3.33, 3.3, 900)
time_swmm_h5l1_15min <- as.POSIXct(depth_swmm_h5l1_15min$Hours, format = "%H:%M")

```

Get smoothed results
```{r}
# 3-point average
smoothed_depth_swmm <- smooth_elevation(swmm_outlet_stage)
smoothed_results_swmm <- get_inflow_outflow_swmm(smoothed_depth_swmm, 0, 0, 184, 98, 0, 3.33, 3.3, 60)
# Transform to 2-min
depth_swmm_2min <- aggregate_data(swmm_data, "Hours", "Depth.Outlet.ft", 2)
time_swmm_2min <- as.POSIXct(depth_swmm_2min$Hours, format = "%H:%M")
twomin_results_swmm <- get_inflow_outflow_swmm(depth_swmm_2min$Depth.Outlet.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 120)
# Transform to 3-min
depth_swmm_3min <- aggregate_data(swmm_data, "Hours", "Depth.Outlet.ft", 3)
time_swmm_3min <- as.POSIXct(depth_swmm_3min$Hours, format = "%H:%M")
threemin_results_swmm <- get_inflow_outflow_swmm(depth_swmm_3min$Depth.Outlet.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 180)
# Transform to 5-min
depth_swmm_5min <- aggregate_data(swmm_data, "Hours", "Depth.Outlet.ft", 5)
time_swmm_5min <- as.POSIXct(depth_swmm_5min$Hours, format = "%H:%M")
fivemin_results_swmm <- get_inflow_outflow_swmm(depth_swmm_5min$Depth.Outlet.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 300)
# Transform to 15-min
depth_swmm_15min <- aggregate_to_15min(depth_swmm_5min, "Hours", "Depth.Outlet.ft")
fifteenmin_results_swmm <- get_inflow_outflow_swmm(depth_swmm_15min$Depth.Outlet.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 900)
time_swmm_15min <- as.POSIXct(depth_swmm_15min$Hours, format = "%H:%M")

```

Get smoothed results restrictive pond
```{r}
# 3-point average
smoothed_depth_swmm_res <- smooth_elevation(swmm_res_outlet_stage)
smoothed_results_swmm_res <- get_inflow_outflow_swmm(smoothed_depth_swmm_res, 0, 0, 184, 98, 0, 3.33, 3.3, 60)
# Transform to 2-min
depth_swmm_res_2min <- aggregate_data(swmm_res_data, "Hours", "Depth.Outlet.ft", 2)
time_swmm_res_2min <- as.POSIXct(depth_swmm_res_2min$Hours, format = "%H:%M")
twomin_results_swmm_res <- get_inflow_outflow_swmm(depth_swmm_res_2min$Depth.Outlet.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 120)
# Transform to 3-min
depth_swmm_res_3min <- aggregate_data(swmm_res_data, "Hours", "Depth.Outlet.ft", 3)
time_swmm_res_3min <- as.POSIXct(depth_swmm_res_3min$Hours, format = "%H:%M")
threemin_results_swmm_res <- get_inflow_outflow_swmm(depth_swmm_res_3min$Depth.Outlet.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 180)
# Transform to 5-min
depth_swmm_res_5min <- aggregate_data(swmm_res_data, "Hours", "Depth.Outlet.ft", 5)
time_swmm_res_5min <- as.POSIXct(depth_swmm_res_5min$Hours, format = "%H:%M")
fivemin_results_swmm_res <- get_inflow_outflow_swmm(depth_swmm_res_5min$Depth.Outlet.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 300)
# Transform to 15-min
depth_swmm_res_15min <- aggregate_to_15min(depth_swmm_res_5min, "Hours", "Depth.Outlet.ft")
fifteenmin_results_swmm_res <- get_inflow_outflow_swmm(depth_swmm_res_15min$Depth.Outlet.ft, 0, 0, 184, 98, 0, 3.33, 3.3, 900)
time_swmm_res_15min <- as.POSIXct(depth_swmm_res_15min$Hours, format = "%H:%M")

```

Smoothing Results Differences H5L10
```{r}
# Calculate percent and magnitude difference from the base results

# 3-point average
swmm_h5l10_smoothed_inflow_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, smoothed_results_swmm_h5l10$Inflow.cfs)
swmm_h5l10_smoothed_outflow_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, smoothed_results_swmm_h5l10$Outflow.cfs)
swmm_h5l10_smoothed_inflow_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, smoothed_results_swmm_h5l10$Inflow.cfs)
swmm_h5l10_smoothed_outflow_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, smoothed_results_swmm_h5l10$Outflow.cfs)

# 2-min average
swmm_h5l10_twomin_diff_data <- read.csv("SWMM_h5l10_2min_Inflow_Outflow.csv")
swmm_h5l10_twomin_inflow_diff <- swmm_h5l10_twomin_diff_data$Inflow.Diff
swmm_h5l10_twomin_outflow_diff <- swmm_h5l10_twomin_diff_data$Outflow.Diff
swmm_h5l10_twomin_inflow_percent_diff <- swmm_h5l10_twomin_diff_data$Inflow...Diff
swmm_h5l10_twomin_outflow_percent_diff <- swmm_h5l10_twomin_diff_data$Outflow...Diff

# 3-min average
swmm_h5l10_threemin_diff_data <- read.csv("SWMM_h5l10_3min_Inflow_Outflow.csv")
swmm_h5l10_threemin_inflow_diff <- swmm_h5l10_threemin_diff_data$Inflow.Diff
swmm_h5l10_threemin_outflow_diff <- swmm_h5l10_threemin_diff_data$Outflow.Diff
swmm_h5l10_threemin_inflow_percent_diff <- swmm_h5l10_threemin_diff_data$Inflow...Diff
swmm_h5l10_threemin_outflow_percent_diff <- swmm_h5l10_threemin_diff_data$Outflow...Diff

# 5-min average
swmm_h5l10_fivemin_diff_data <- read.csv("SWMM_h5l10_5min_Inflow_Outflow.csv")
swmm_h5l10_fivemin_inflow_diff <- swmm_h5l10_fivemin_diff_data$Inflow.Diff
swmm_h5l10_fivemin_outflow_diff <- swmm_h5l10_fivemin_diff_data$Outflow.Diff
swmm_h5l10_fivemin_inflow_percent_diff <- swmm_h5l10_fivemin_diff_data$Inflow...Diff
swmm_h5l10_fivemin_outflow_percent_diff <- swmm_h5l10_fivemin_diff_data$Outflow...Diff

```

Smoothing Results Differences H5L5
```{r}
# Calculate percent and magnitude difference from the base results

# 3-point average
swmm_h5l5_smoothed_inflow_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, smoothed_results_swmm_h5l5$Inflow.cfs)
swmm_h5l5_smoothed_outflow_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, smoothed_results_swmm_h5l5$Outflow.cfs)
swmm_h5l5_smoothed_inflow_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, smoothed_results_swmm_h5l5$Inflow.cfs)
swmm_h5l5_smoothed_outflow_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, smoothed_results_swmm_h5l5$Outflow.cfs)

# 2-min average
swmm_h5l5_twomin_diff_data <- read.csv("SWMM_h5l5_2min_Inflow_Outflow.csv")
swmm_h5l5_twomin_inflow_diff <- swmm_h5l5_twomin_diff_data$Inflow.Diff
swmm_h5l5_twomin_outflow_diff <- swmm_h5l5_twomin_diff_data$Outflow.Diff
swmm_h5l5_twomin_inflow_percent_diff <- swmm_h5l5_twomin_diff_data$Inflow...Diff
swmm_h5l5_twomin_outflow_percent_diff <- swmm_h5l5_twomin_diff_data$Outflow...Diff

# 3-min average
swmm_h5l5_threemin_diff_data <- read.csv("SWMM_h5l5_3min_Inflow_Outflow.csv")
swmm_h5l5_threemin_inflow_diff <- swmm_h5l5_threemin_diff_data$Inflow.Diff
swmm_h5l5_threemin_outflow_diff <- swmm_h5l5_threemin_diff_data$Outflow.Diff
swmm_h5l5_threemin_inflow_percent_diff <- swmm_h5l5_threemin_diff_data$Inflow...Diff
swmm_h5l5_threemin_outflow_percent_diff <- swmm_h5l5_threemin_diff_data$Outflow...Diff

# 5-min average
swmm_h5l5_fivemin_diff_data <- read.csv("SWMM_h5l5_5min_Inflow_Outflow.csv")
swmm_h5l5_fivemin_inflow_diff <- swmm_h5l5_fivemin_diff_data$Inflow.Diff
swmm_h5l5_fivemin_outflow_diff <- swmm_h5l5_fivemin_diff_data$Outflow.Diff
swmm_h5l5_fivemin_inflow_percent_diff <- swmm_h5l5_fivemin_diff_data$Inflow...Diff
swmm_h5l5_fivemin_outflow_percent_diff <- swmm_h5l5_fivemin_diff_data$Outflow...Diff
```

Smoothing Results Differences H5L1
```{r}
# Calculate percent and magnitude difference from the base results

# 3-point average
swmm_h5l1_smoothed_inflow_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, smoothed_results_swmm_h5l1$Inflow.cfs)
swmm_h5l1_smoothed_outflow_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, smoothed_results_swmm_h5l1$Outflow.cfs)
swmm_h5l1_smoothed_inflow_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, smoothed_results_swmm_h5l1$Inflow.cfs)
swmm_h5l1_smoothed_outflow_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, smoothed_results_swmm_h5l1$Outflow.cfs)

# 2-min average
swmm_h5l1_twomin_diff_data <- read.csv("SWMM_h5l1_2min_Inflow_Outflow.csv")
swmm_h5l1_twomin_inflow_diff <- swmm_h5l1_twomin_diff_data$Inflow.Diff
swmm_h5l1_twomin_outflow_diff <- swmm_h5l1_twomin_diff_data$Outflow.Diff
swmm_h5l1_twomin_inflow_percent_diff <- swmm_h5l1_twomin_diff_data$Inflow...Diff
swmm_h5l1_twomin_outflow_percent_diff <- swmm_h5l1_twomin_diff_data$Outflow...Diff

# 3-min average
swmm_h5l1_threemin_diff_data <- read.csv("SWMM_h5l1_3min_Inflow_Outflow.csv")
swmm_h5l1_threemin_inflow_diff <- swmm_h5l1_threemin_diff_data$Inflow.Diff
swmm_h5l1_threemin_outflow_diff <- swmm_h5l1_threemin_diff_data$Outflow.Diff
swmm_h5l1_threemin_inflow_percent_diff <- swmm_h5l1_threemin_diff_data$Inflow...Diff
swmm_h5l1_threemin_outflow_percent_diff <- swmm_h5l1_threemin_diff_data$Outflow...Diff

# 5-min average
swmm_h5l1_fivemin_diff_data <- read.csv("SWMM_h5l1_5min_Inflow_Outflow.csv")
swmm_h5l1_fivemin_inflow_diff <- swmm_h5l1_fivemin_diff_data$Inflow.Diff
swmm_h5l1_fivemin_outflow_diff <- swmm_h5l1_fivemin_diff_data$Outflow.Diff
swmm_h5l1_fivemin_inflow_percent_diff <- swmm_h5l1_fivemin_diff_data$Inflow...Diff
swmm_h5l1_fivemin_outflow_percent_diff <- swmm_h5l1_fivemin_diff_data$Outflow...Diff
```

Smoothing Results Differences
```{r}
# Calculate percent and magnitude difference from the base results

# 3-point average
swmm_smoothed_inflow_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, smoothed_results_swmm$Inflow.cfs)
swmm_smoothed_outflow_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, smoothed_results_swmm$Outflow.cfs)
swmm_smoothed_inflow_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, smoothed_results_swmm$Inflow.cfs)
swmm_smoothed_outflow_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, smoothed_results_swmm$Outflow.cfs)

# 2-min average
swmm_twomin_diff_data <- read.csv("SWMM_2min_Inflow_Outflow.csv")
swmm_twomin_inflow_diff <- swmm_twomin_diff_data$Inflow.Diff
swmm_twomin_outflow_diff <- swmm_twomin_diff_data$Outflow.Diff
swmm_twomin_inflow_percent_diff <- swmm_twomin_diff_data$Inflow...Diff
swmm_twomin_outflow_percent_diff <- swmm_twomin_diff_data$Outflow...Diff

# 3-min average
swmm_threemin_diff_data <- read.csv("SWMM_3min_Inflow_Outflow.csv")
swmm_threemin_inflow_diff <- swmm_threemin_diff_data$Inflow.Diff
swmm_threemin_outflow_diff <- swmm_threemin_diff_data$Outflow.Diff
swmm_threemin_inflow_percent_diff <- swmm_threemin_diff_data$Inflow...Diff
swmm_threemin_outflow_percent_diff <- swmm_threemin_diff_data$Outflow...Diff

# 5-min average
swmm_fivemin_diff_data <- read.csv("SWMM_5min_Inflow_Outflow.csv")
swmm_fivemin_inflow_diff <- swmm_fivemin_diff_data$Inflow.Diff
swmm_fivemin_outflow_diff <- swmm_fivemin_diff_data$Outflow.Diff
swmm_fivemin_inflow_percent_diff <- swmm_fivemin_diff_data$Inflow...Diff
swmm_fivemin_outflow_percent_diff <- swmm_fivemin_diff_data$Outflow...Diff

```

Smoothing results differences restrictive pond
```{r}
# Calculate percent and magnitude difference from the base results

# 3-point average
swmm_res_smoothed_inflow_diff <- calc_magnitude_difference(swmm_res_results_base$Inflow.cfs, smoothed_results_swmm_res$Inflow.cfs)
swmm_res_smoothed_outflow_diff <- calc_magnitude_difference(swmm_res_results_base$Outflow.cfs, smoothed_results_swmm_res$Outflow.cfs)
swmm_res_smoothed_inflow_percent_diff <- calc_percent_difference(swmm_res_results_base$Inflow.cfs, smoothed_results_swmm_res$Inflow.cfs)
swmm_res_smoothed_outflow_percent_diff <- calc_percent_difference(swmm_res_results_base$Outflow.cfs, smoothed_results_swmm_res$Outflow.cfs)

# 2-min average
swmm_res_twomin_diff_data <- read.csv("swmm_res_2min_Inflow_Outflow.csv")
swmm_res_twomin_inflow_diff <- swmm_res_twomin_diff_data$Inflow.Diff
swmm_res_twomin_outflow_diff <- swmm_res_twomin_diff_data$Outflow.Diff
swmm_res_twomin_inflow_percent_diff <- swmm_res_twomin_diff_data$Inflow...Diff
swmm_res_twomin_outflow_percent_diff <- swmm_res_twomin_diff_data$Outflow...Diff

# 3-min average
swmm_res_threemin_diff_data <- read.csv("swmm_res_3min_Inflow_Outflow.csv")
swmm_res_threemin_inflow_diff <- swmm_res_threemin_diff_data$Inflow.Diff
swmm_res_threemin_outflow_diff <- swmm_res_threemin_diff_data$Outflow.Diff
swmm_res_threemin_inflow_percent_diff <- swmm_res_threemin_diff_data$Inflow...Diff
swmm_res_threemin_outflow_percent_diff <- swmm_res_threemin_diff_data$Outflow...Diff

# 5-min average
swmm_res_fivemin_diff_data <- read.csv("swmm_res_5min_Inflow_Outflow.csv")
swmm_res_fivemin_inflow_diff <- swmm_res_fivemin_diff_data$Inflow.Diff
swmm_res_fivemin_outflow_diff <- swmm_res_fivemin_diff_data$Outflow.Diff
swmm_res_fivemin_inflow_percent_diff <- swmm_res_fivemin_diff_data$Inflow...Diff
swmm_res_fivemin_outflow_percent_diff <- swmm_res_fivemin_diff_data$Outflow...Diff
```

Plot smoothed results H5L10
```{r}
plot(swmm_time[1:325], swmm_results_h5l10_base$Inflow.cfs[1:325], type = "l", xlab = "Time", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow with Smoothing", lwd = 1, ylim=c(-1, max(swmm_results_h5l10_plus5cm$Inflow.cfs)), col = colors[1])
     lines(swmm_time[1:325], swmm_h5l10_outflow[1:325], col = colors[1], lwd = 1, lty = 3)
     lines(swmm_time[1:325], smoothed_results_swmm_h5l10$Inflow.cfs[1:325], col = colors[2], lwd = 1)
     lines(swmm_time[1:325], smoothed_results_swmm_h5l10$Outflow.cfs[1:325], col = colors[2], lwd = 1, lty = 3)
     lines(time_swmm_5min[1:65], fivemin_results_swmm_h5l10$Inflow.cfs[1:65], col = colors[4], lwd = 1)
     lines(time_swmm_5min[1:65], fivemin_results_swmm_h5l10$Outflow.cfs[1:65], col = colors[4], lwd = 1, lty = 3)
     lines(time_swmm_2min[1:162], twomin_results_swmm_h5l10$Inflow.cfs[1:162], col = colors[3], lwd = 1)
     lines(time_swmm_2min[1:162], twomin_results_swmm_h5l10$Outflow.cfs[1:162], col = colors[3], lwd = 1, lty = 3)
     grid()
       legend("topright", legend = c("Inflow Raw", "Inflow Smoothed", "Inflow 2 Min", "Inflow 5 min", "Outflow Raw", "Outflow Smoothed", "Outflow 2 Min", "Outflow 5 min"), col = c(colors[1], colors[2], colors[3], colors[4], colors[1], colors[2], colors[3], colors[4]), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2)
```

Plot smoothed results H5L5
```{r}
par(pin = c(5, 2.5))  # 5 inches wide, 2 inches tall
# Adjust the axis title position with the mgp parameter
par(mgp = c(2, 0.5, 0))  # Move axis titles closer to the axis


plot(swmm_time[1:325], swmm_results_h5l5_base$Inflow.cfs[1:325], type = "l", xlab = "Time (hours)", ylab = "Flow (cfs)", main = "", lwd = 1, ylim=c(-1, 65), col = "black", cex.lab = 1.1)
     lines(swmm_time[1:325], swmm_h5l5_outflow[1:325], col = "black", lwd = 1, lty = 3)
     lines(swmm_time[1:325], smoothed_results_swmm_h5l5$Inflow.cfs[1:325], col = colors[4], lwd = 1)
     lines(swmm_time[1:325], smoothed_results_swmm_h5l5$Outflow.cfs[1:325], col = colors[4], lwd = 1, lty = 3)
     lines(time_swmm_5min[1:65], fivemin_results_swmm_h5l5$Inflow.cfs[1:65], col = colors[2], lwd = 1)
     lines(time_swmm_5min[1:65], fivemin_results_swmm_h5l5$Outflow.cfs[1:65], col = colors[2], lwd = 1, lty = 3)
     lines(time_swmm_2min[1:162], twomin_results_swmm_h5l5$Inflow.cfs[1:162], col = colors[3], lwd = 1)
     lines(time_swmm_2min[1:162], twomin_results_swmm_h5l5$Outflow.cfs[1:162], col = colors[3], lwd = 1, lty = 3)
     grid()
       legend("topright", legend = c("Inflow Raw", "Inflow Smoothed", "Inflow 2 Min", "Inflow 5 min", "Outflow Raw", "Outflow Smoothed", "Outflow 2 Min", "Outflow 5 min"), col = c("black", colors[4], colors[3], colors[2], "black", colors[4], colors[3], colors[2]), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2)
```

Plot smoothed results H5L1
```{r}
par(pin = c(5, 2.5))  # 5 inches wide, 2 inches tall
par(mgp = c(2, 0.5, 0))  # Move axis titles closer to the axis

plot(swmm_time[1:325], swmm_results_h5l1_base$Inflow.cfs[1:325], type = "l", xlab = "Time (hours)", ylab = "Flow (cfs)", main = "", lwd = 1, ylim=c(-1, 65), col = "black", cex.lab = 1.1, cex.axis = 1)
     lines(swmm_time[1:325], swmm_h5l1_outflow[1:325], col = "black", lwd = 1, lty = 3)
     lines(swmm_time[1:325], smoothed_results_swmm_h5l1$Inflow.cfs[1:325], col = colors[4], lwd = 1)
     lines(swmm_time[1:325], smoothed_results_swmm_h5l1$Outflow.cfs[1:325], col = colors[4], lwd = 1, lty = 3)
     lines(time_swmm_5min[1:65], fivemin_results_swmm_h5l1$Inflow.cfs[1:65], col = colors[2], lwd = 1)
     lines(time_swmm_5min[1:65], fivemin_results_swmm_h5l1$Outflow.cfs[1:65], col = colors[2], lwd = 1, lty = 3)
     lines(time_swmm_2min[1:162], twomin_results_swmm_h5l1$Inflow.cfs[1:162], col = colors[3], lwd = 1)
     lines(time_swmm_2min[1:162], twomin_results_swmm_h5l1$Outflow.cfs[1:162], col = colors[3], lwd = 1, lty = 3)
     grid()
       legend("topright", legend = c("Inflow Raw", "Inflow Smoothed", "Inflow 2 Min", "Inflow 5 min", "Outflow Raw", "Outflow Smoothed", "Outflow 2 Min", "Outflow 5 min"), col = c("black", colors[4], colors[3], colors[2], "black", colors[4], colors[3], colors[2]), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2, cex = 1)
```

Plot smoothed results
```{r}

plot(swmm_time[1:325], swmm_results_base$Inflow.cfs[1:325], type = "l", xlab = "Time", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow with Smoothing", lwd = 1, ylim=c(-1, max(swmm_results_plus5cm$Inflow.cfs)), col = colors[1])
     lines(swmm_time[1:325], swmm_outflow[1:325], col = colors[1], lwd = 1, lty = 3)
     lines(swmm_time[1:325], smoothed_results_swmm$Inflow.cfs[1:325], col = colors[2], lwd = 1)
     lines(swmm_time[1:325], smoothed_results_swmm$Outflow.cfs[1:325], col = colors[2], lwd = 1, lty = 3)
     lines(time_swmm_5min[1:65], fivemin_results_swmm$Inflow.cfs[1:65], col = colors[4], lwd = 1)
     lines(time_swmm_5min[1:65], fivemin_results_swmm$Outflow.cfs[1:65], col = colors[4], lwd = 1, lty = 3)
     lines(time_swmm_2min[1:162], twomin_results_swmm$Inflow.cfs[1:162], col = colors[3], lwd = 1)
     lines(time_swmm_2min[1:162], twomin_results_swmm$Outflow.cfs[1:162], col = colors[3], lwd = 1, lty = 3)
     grid()
       legend("topright", legend = c("Inflow Raw", "Inflow Smoothed", "Inflow 2 Min", "Inflow 5 min", "Outflow Raw", "Outflow Smoothed", "Outflow 2 Min", "Outflow 5 min"), col = c(colors[1], colors[2], colors[3], colors[4], colors[1], colors[2], colors[3], colors[4]), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2)

```

Plot smoothed results differences H5L10
```{r}
# Plot showing smoothing differences
plot(swmm_time[1:325], swmm_h5l10_smoothed_inflow_diff[1:325], type = "l", col = colors[2], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "", ylim = c(-20,10), lty = 3)
lines(swmm_time[1:325], swmm_h5l10_smoothed_outflow_diff[1:325], col = colors[2])
lines(time_swmm_5min[1:65], swmm_h5l10_fivemin_inflow_diff[1:65], col = colors[4])
lines(time_swmm_5min[1:65], swmm_h5l10_fivemin_outflow_diff[1:65], col = colors[4], lty = 3)
lines(time_swmm_2min[1:162], swmm_h5l10_twomin_inflow_diff[1:162], col = colors[3])
lines(time_swmm_2min[1:162], swmm_h5l10_twomin_outflow_diff[1:162], col = colors[3], lty = 3)
grid()
#legend("topright", legend = c("Inflow Smoothed Difference", "Inflow 2 Min Difference", "Inflow 5 min Difference", "Outflow Smoothed Difference", "Outflow 2 Min Difference", "Outflow 5 min Difference"), col = c(colors[2], colors[3], colors[4], colors[2], colors[3], colors[4]), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2, cex = 0.8)
```

Plot smoothed results differences H5L5
```{r}
par(pin = c(5, 1.5))  # 5 inches wide, 2 inches tall
par(mgp = c(2, 0.5, 0))  # Move axis titles closer to the axis

# Plot showing smoothing differences
plot(swmm_time[1:325], swmm_h5l5_smoothed_inflow_diff[1:325], type = "l", col = colors[4], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "", ylim = c(-20,20), cex.lab = 1.1)
lines(swmm_time[1:325], swmm_h5l5_smoothed_outflow_diff[1:325], col = colors[4], lty=3)
lines(time_swmm_5min[1:65], swmm_h5l5_fivemin_inflow_diff[1:65], col = colors[2])
lines(time_swmm_5min[1:65], swmm_h5l5_fivemin_outflow_diff[1:65], col = colors[2], lty = 3)
lines(time_swmm_2min[1:162], swmm_h5l5_twomin_inflow_diff[1:162], col = colors[3])
lines(time_swmm_2min[1:162], swmm_h5l5_twomin_outflow_diff[1:162], col = colors[3], lty = 3)
grid()
#legend("topright", legend = c("Inflow Smoothed Difference", "Inflow 2 Min Difference", "Inflow 5 min Difference", "Outflow Smoothed Difference", "Outflow 2 Min Difference", "Outflow 5 min Difference"), col = c(colors[2], colors[3], colors[4], colors[2], colors[3], colors[4]), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2, cex = 0.8)
```

Plot smoothed results differences H5L1
```{r}
par(pin = c(5, 1.5))  # 5 inches wide, 2 inches tall
par(mgp = c(2, 0.5, 0))  # Move axis titles closer to the axis

# Plot showing smoothing differences
plot(swmm_time[1:325], swmm_h5l1_smoothed_inflow_diff[1:325], type = "l", col = colors[4], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "", ylim = c(-20,20), cex.lab = 1.1)
lines(swmm_time[1:325], swmm_h5l1_smoothed_outflow_diff[1:325], col = colors[4], lty = 3)
lines(time_swmm_5min[1:65], swmm_h5l1_fivemin_inflow_diff[1:65], col = colors[2])
lines(time_swmm_5min[1:65], swmm_h5l1_fivemin_outflow_diff[1:65], col = colors[2], lty = 3)
lines(time_swmm_2min[1:162], swmm_h5l1_twomin_inflow_diff[1:162], col = colors[3])
lines(time_swmm_2min[1:162], swmm_h5l1_twomin_outflow_diff[1:162], col = colors[3], lty = 3)
grid()
#legend("topright", legend = c("Inflow Smoothed Difference", "Inflow 2 Min Difference", "Inflow 5 min Difference", "Outflow Smoothed Difference", "Outflow 2 Min Difference", "Outflow 5 min Difference"), col = c(colors[2], colors[3], colors[4], colors[2], colors[3], colors[4]), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2, cex = 0.8)
```

Plot smoothed results differences 
```{r}
# Plot showing smoothing differences
plot(swmm_time[1:325], swmm_smoothed_inflow_diff[1:325], type = "l", col = "forestgreen", xlab = "Time (hours)", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow Smoothing Differences", ylim = c(-10,20), lty = 3)
lines(swmm_time[1:325], swmm_smoothed_outflow_diff[1:325], col = "forestgreen")
lines(time_swmm_5min[1:65], swmm_fivemin_inflow_diff[1:65], col = "palegreen")
lines(time_swmm_5min[1:65], swmm_fivemin_outflow_diff[1:65], col = "palegreen", lty = 3)
lines(time_swmm_2min[1:162], swmm_twomin_inflow_diff[1:162], col = "palegreen3")
lines(time_swmm_2min[1:162], swmm_twomin_outflow_diff[1:162], col = "palegreen3", lty = 3)
grid()
legend("topright", legend = c("Inflow Raw", "Inflow Smoothed", "Inflow 2 Min", "Inflow 5 min", "Outflow Raw", "Outflow Smoothed", "Outflow 2 Min", "Outflow 5 min"), col = c("black", "forestgreen", "palegreen3", "palegreen", "black", "forestgreen", "palegreen3", "palegreen"), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2, cex = 0.8)
```

Plot smoothed results restrictive
```{r}

plot(swmm_res_time[1:325], swmm_res_results_base$Inflow.cfs[1:325], type = "l", xlab = "Time", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow with Smoothing", lwd = 1, ylim=c(-1, max(swmm_res_results_plus5cm$Inflow.cfs)), col = colors[1])
     lines(swmm_res_time[1:325], swmm_res_outflow[1:325], col = colors[1], lwd = 1, lty = 3)
     lines(swmm_res_time[1:325], smoothed_results_swmm_res$Inflow.cfs[1:325], col = colors[2], lwd = 1)
     lines(swmm_res_time[1:325], smoothed_results_swmm_res$Outflow.cfs[1:325], col = colors[2], lwd = 1, lty = 3)
     lines(time_swmm_res_5min[1:65], fivemin_results_swmm_res$Inflow.cfs[1:65], col = colors[4], lwd = 1)
     lines(time_swmm_res_5min[1:65], fivemin_results_swmm_res$Outflow.cfs[1:65], col = colors[4], lwd = 1, lty = 3)
     lines(time_swmm_res_2min[1:162], twomin_results_swmm_res$Inflow.cfs[1:162], col = colors[3], lwd = 1)
     lines(time_swmm_res_2min[1:162], twomin_results_swmm_res$Outflow.cfs[1:162], col = colors[3], lwd = 1, lty = 3)
     grid()
       legend("topright", legend = c("Inflow Raw", "Inflow Smoothed", "Inflow 2 Min", "Inflow 5 min", "Outflow Raw", "Outflow Smoothed", "Outflow 2 Min", "Outflow 5 min"), col = c(colors[1], colors[2], colors[3], colors[4], colors[1], colors[2], colors[3], colors[4]), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2)

```

Plot smoothed results differences restrictive
```{r}

# Plot showing smoothing differences
plot(swmm_time[1:325], swmm_smoothed_inflow_diff[1:325], type = "l", col = colors[2], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow Smoothing Differences", ylim = c(-10,20), lty = 3)
lines(swmm_time[1:325], swmm_smoothed_outflow_diff[1:325], col = colors[2])
lines(time_swmm_5min[1:65], swmm_fivemin_inflow_diff[1:65], col = colors[4])
lines(time_swmm_5min[1:65], swmm_fivemin_outflow_diff[1:65], col = colors[4], lty = 3)
lines(time_swmm_2min[1:162], swmm_twomin_inflow_diff[1:162], col = colors[3])
lines(time_swmm_2min[1:162], swmm_twomin_outflow_diff[1:162], col = colors[3], lty = 3)
grid()
legend("topright", legend = c("Inflow Smoothed Difference", "Inflow 2 Min Difference", "Inflow 5 min Difference", "Outflow Smoothed Difference", "Outflow 2 Min Difference", "Outflow 5 min Difference"), col = c(colors[2], colors[3], colors[4], colors[2], colors[3], colors[4]), lty = c(1, 1, 1, 1, 3, 3, 3, 3), lwd = 2, cex = 0.8)

```

SWMM Results H=5, L=10
```{r}
# get inflow for base case
swmm_results_h5l10_base <- get_inflow_outflow_swmm(swmm_h5l10_stage, 0, 0, 184, 80,  0, 3.33, 3.3, 60)
# adding typical noise and no bias
swmm_results_h5l10_typical_noise <- get_inflow_outflow_swmm(swmm_h5l10_stage, 0, 0.01, 184, 80,  0, 3.33, 3.3, 60)
# adding maximum noise and no bias
swmm_results_h5l10_max_noise <- get_inflow_outflow_swmm(swmm_h5l10_stage, 0, 0.02, 184, 80,  0, 3.33, 3.3, 60)
# adding no noise and +1cm bias
swmm_results_h5l10_plus1cm <- get_inflow_outflow_swmm(swmm_h5l10_stage, 1/(2.54*12), 0, 184, 80,  0, 3.33, 3.3, 60)
# adding no noise and -1cm bias
swmm_results_h5l10_minus1cm <- get_inflow_outflow_swmm(swmm_h5l10_stage, -1/(2.54*12), 0, 184, 80,  0, 3.33, 3.3, 60)
# adding no noise and +5cm bias
swmm_results_h5l10_plus5cm <- get_inflow_outflow_swmm(swmm_h5l10_stage, 5/(2.54*12), 0, 184, 80,  0, 3.33, 3.3, 60)
# adding no noise and -5cm bias
swmm_results_h5l10_minus5cm <- get_inflow_outflow_swmm(swmm_h5l10_stage, -5/(2.54*12), 0, 184, 80,  0, 3.33, 3.3, 60)
# typical noise and +1cm bias
swmm_results_h5l10_typical_noise_plus1cm <- get_inflow_outflow_swmm(swmm_h5l10_stage, 1/(2.54*12), 0.01, 184, 80,  0, 3.33, 3.3, 60)
# typical noise and -1cm bias
swmm_results_h5l10_typical_noise_minus1cm <- get_inflow_outflow_swmm(swmm_h5l10_stage, -1/(2.54*12), 0.01, 184, 80,  0, 3.33, 3.3, 60)
# typical noise and +5cm bias
swmm_results_h5l10_typical_noise_plus5cm <- get_inflow_outflow_swmm(swmm_h5l10_stage, 5/(2.54*12), 0.01, 184, 80,  0, 3.33, 3.3, 60)
# typical noise and -5cm bias
swmm_results_h5l10_typical_noise_minus5cm <- get_inflow_outflow_swmm(swmm_h5l10_stage, -5/(2.54*12), 0.01, 184, 80,  0, 3.33, 3.3, 60)
```

SWMM Results H=5, L=5
```{r}
# get inflow for base case
swmm_results_h5l5_base <- get_inflow_outflow_swmm(swmm_h5l5_stage, 0, 0, 184, 98,  0, 3.33, 3.3, 60)
# adding typical noise and no bias
swmm_results_h5l5_typical_noise <- get_inflow_outflow_swmm(swmm_h5l5_stage, 0, 0.01, 184, 98,  0, 3.33, 3.3, 60)
# adding maximum noise and no bias
swmm_results_h5l5_max_noise <- get_inflow_outflow_swmm(swmm_h5l5_stage, 0, 0.02, 184, 98,  0, 3.33, 3.3, 60)
# adding no noise and +1cm bias
swmm_results_h5l5_plus1cm <- get_inflow_outflow_swmm(swmm_h5l5_stage, 1/(2.54*12), 0, 184, 98,  0, 3.33, 3.3, 60)
# adding no noise and -1cm bias
swmm_results_h5l5_minus1cm <- get_inflow_outflow_swmm(swmm_h5l5_stage, -1/(2.54*12), 0, 184, 98,  0, 3.33, 3.3, 60)
# adding no noise and +5cm bias
swmm_results_h5l5_plus5cm <- get_inflow_outflow_swmm(swmm_h5l5_stage, 5/(2.54*12), 0, 184, 98,  0, 3.33, 3.3, 60)
# adding no noise and -5cm bias
swmm_results_h5l5_minus5cm <- get_inflow_outflow_swmm(swmm_h5l5_stage, -5/(2.54*12), 0, 184, 98,  0, 3.33, 3.3, 60)
# typical noise and +1cm bias
swmm_results_h5l5_typical_noise_plus1cm <- get_inflow_outflow_swmm(swmm_h5l5_stage, 1/(2.54*12), 0.01, 184, 98,  0, 3.33, 3.3, 60)
# typical noise and -1cm bias
swmm_results_h5l5_typical_noise_minus1cm <- get_inflow_outflow_swmm(swmm_h5l5_stage, -1/(2.54*12), 0.01, 184, 98,  0, 3.33, 3.3, 60)
# typical noise and +5cm bias
swmm_results_h5l5_typical_noise_plus5cm <- get_inflow_outflow_swmm(swmm_h5l5_stage, 5/(2.54*12), 0.01, 184, 98,  0, 3.33, 3.3, 60)
# typical noise and -5cm bias
swmm_results_h5l5_typical_noise_minus5cm <- get_inflow_outflow_swmm(swmm_h5l5_stage, -5/(2.54*12), 0.01, 184, 98,  0, 3.33, 3.3, 60)
```

SWMM Results H=5, L=1
```{r}
# get inflow for base case
swmm_results_h5l1_base <- get_inflow_outflow_swmm(swmm_h5l1_stage, 0, 0, 184, 200,  0, 3.33, 3.3, 60)
# adding typical noise and no bias
swmm_results_h5l1_typical_noise <- get_inflow_outflow_swmm(swmm_h5l1_stage, 0, 0.01/2, 184, 200,  0, 3.33, 3.3, 60)
# adding maximum noise and no bias
swmm_results_h5l1_max_noise <- get_inflow_outflow_swmm(swmm_h5l1_stage, 0, 0.02/2, 184, 200,  0, 3.33, 3.3, 60)
# adding no noise and +1cm bias
swmm_results_h5l1_plus1cm <- get_inflow_outflow_swmm(swmm_h5l1_stage, 1/(2.54*12), 0, 184, 200,  0, 3.33, 3.3, 60)
# adding no noise and -1cm bias
swmm_results_h5l1_minus1cm <- get_inflow_outflow_swmm(swmm_h5l1_stage, -1/(2.54*12), 0, 184, 200,  0, 3.33, 3.3, 60)
# adding no noise and +5cm bias
swmm_results_h5l1_plus5cm <- get_inflow_outflow_swmm(swmm_h5l1_stage, 5/(2.54*12), 0, 184, 200,  0, 3.33, 3.3, 60)
# adding no noise and -5cm bias
swmm_results_h5l1_minus5cm <- get_inflow_outflow_swmm(swmm_h5l1_stage, -5/(2.54*12), 0, 184, 200,  0, 3.33, 3.3, 60)
# typical noise and +1cm bias
swmm_results_h5l1_typical_noise_plus1cm <- get_inflow_outflow_swmm(swmm_h5l1_stage, 1/(2.54*12), 0.01/2, 184, 200,  0, 3.33, 3.3, 60)
# typical noise and -1cm bias
swmm_results_h5l1_typical_noise_minus1cm <- get_inflow_outflow_swmm(swmm_h5l1_stage, -1/(2.54*12), 0.01/2, 184, 200,  0, 3.33, 3.3, 60)
# typical noise and +5cm bias
swmm_results_h5l1_typical_noise_plus5cm <- get_inflow_outflow_swmm(swmm_h5l1_stage, 5/(2.54*12), 0.01/2, 184, 200,  0, 3.33, 3.3, 60)
# typical noise and -5cm bias
swmm_results_h5l1_typical_noise_minus5cm <- get_inflow_outflow_swmm(swmm_h5l1_stage, -5/(2.54*12), 0.01/2, 184, 200,  0, 3.33, 3.3, 60)
```

SWMM Results H=2, L=1
```{r}
# get inflow for base case
swmm_results_h2l1_base <- get_inflow_outflow_swmm(swmm_h2l1_stage, 0, 0, 184, 300,  0, 3.33, 3.3, 60)
# adding typical noise and no bias
swmm_results_h2l1_typical_noise <- get_inflow_outflow_swmm(swmm_h2l1_stage, 0, 0.01, 184, 300,  0, 3.33, 3.3, 60)
# adding maximum noise and no bias
swmm_results_h2l1_max_noise <- get_inflow_outflow_swmm(swmm_h2l1_stage, 0, 0.02, 184, 300,  0, 3.33, 3.3, 60)
# adding no noise and +1cm bias
swmm_results_h2l1_plus1cm <- get_inflow_outflow_swmm(swmm_h2l1_stage, 1/(2.54*12), 0, 184, 300,  0, 3.33, 3.3, 60)
# adding no noise and -1cm bias
swmm_results_h2l1_minus1cm <- get_inflow_outflow_swmm(swmm_h2l1_stage, -1/(2.54*12), 0, 184, 300,  0, 3.33, 3.3, 60)
# adding no noise and +5cm bias
swmm_results_h2l1_plus5cm <- get_inflow_outflow_swmm(swmm_h2l1_stage, 5/(2.54*12), 0, 184, 300,  0, 3.33, 3.3, 60)
# adding no noise and -5cm bias
swmm_results_h2l1_minus5cm <- get_inflow_outflow_swmm(swmm_h2l1_stage, -5/(2.54*12), 0, 184, 300,  0, 3.33, 3.3, 60)
# typical noise and +1cm bias
swmm_results_h2l1_typical_noise_plus1cm <- get_inflow_outflow_swmm(swmm_h2l1_stage, 1/(2.54*12), 0.01, 184, 300,  0, 3.33, 3.3, 60)
# typical noise and -1cm bias
swmm_results_h2l1_typical_noise_minus1cm <- get_inflow_outflow_swmm(swmm_h2l1_stage, -1/(2.54*12), 0.01, 184, 300,  0, 3.33, 3.3, 60)
# typical noise and +5cm bias
swmm_results_h2l1_typical_noise_plus5cm <- get_inflow_outflow_swmm(swmm_h2l1_stage, 5/(2.54*12), 0.01, 184, 300,  0, 3.33, 3.3, 60)
# typical noise and -5cm bias
swmm_results_h2l1_typical_noise_minus5cm <- get_inflow_outflow_swmm(swmm_h2l1_stage, -5/(2.54*12), 0.01, 184, 300,  0, 3.33, 3.3, 60)
```

Compare EPA SWMM to calculated inflows
```{r}
plot(swmm_inflow[1:300], type = "l", col = "black")
lines(swmm_results_h5l1_base$Inflow.cfs[1:300], col = "red")
```

SWMM Results
```{r}
# get inflow for base case
swmm_results_base <- get_inflow_outflow_swmm(swmm_outlet_stage, 0, 0, 184, 98, 0, 3.33, 3.3, 60)
# adding typical noise and no bias
swmm_results_typical_noise <- get_inflow_outflow_swmm(swmm_outlet_stage, 0, 0.01, 184, 98, 0, 3.33, 3.3, 60)
# adding maximum noise and no bias
swmm_results_max_noise <- get_inflow_outflow_swmm(swmm_outlet_stage, 0, 0.02, 184, 98, 0, 3.33, 3.3, 60)
# adding no noise and +1cm bias
swmm_results_plus1cm <- get_inflow_outflow_swmm(swmm_outlet_stage, 1/(2.54*12), 0, 184, 98, 0, 3.33, 3.3, 60)
# adding no noise and -1cm bias
swmm_results_minus1cm <- get_inflow_outflow_swmm(swmm_outlet_stage, -1/(2.54*12), 0, 184, 98, 0, 3.33, 3.3, 60)
# adding no noise and +5cm bias
swmm_results_plus5cm <- get_inflow_outflow_swmm(swmm_outlet_stage, 5/(2.54*12), 0, 184, 98, 0, 3.33, 3.3, 60)
# adding no noise and -5cm bias
swmm_results_minus5cm <- get_inflow_outflow_swmm(swmm_outlet_stage, -5/(2.54*12), 0, 184, 98, 0, 3.33, 3.3, 60)
# typical noise and +1cm bias
swmm_results_typical_noise_plus1cm <- get_inflow_outflow_swmm(swmm_outlet_stage, 1/(2.54*12), 0.01, 184, 98, 0, 3.33, 3.3, 60)
# typical noise and -1cm bias
swmm_results_typical_noise_minus1cm <- get_inflow_outflow_swmm(swmm_outlet_stage, -1/(2.54*12), 0.01, 184, 98, 0, 3.33, 3.3, 60)
# typical noise and +5cm bias
swmm_results_typical_noise_plus5cm <- get_inflow_outflow_swmm(swmm_outlet_stage, 5/(2.54*12), 0.01, 184, 98, 0, 3.33, 3.3, 60)
# typical noise and -5cm bias
swmm_results_typical_noise_minus5cm <- get_inflow_outflow_swmm(swmm_outlet_stage, -5/(2.54*12), 0.01, 184, 98, 0, 3.33, 3.3, 60)
```

SWMM Results Restrictive Pond
```{r}
# get inflow for base case
swmm_res_results_base <- get_inflow_outflow_swmm(swmm_res_outlet_stage, 0, 0, 184, 98, 0, 3.33, 3.3, 60)
# adding typical noise and no bias
swmm_res_results_typical_noise <- get_inflow_outflow_swmm(swmm_res_outlet_stage, 0, 0.01, 184, 98, 0, 3.33, 3.3, 60)
# adding maximum noise and no bias
swmm_res_results_max_noise <- get_inflow_outflow_swmm(swmm_res_outlet_stage, 0, 0.02, 184, 98, 0, 3.33, 3.3, 60)
# adding no noise and +1cm bias
swmm_res_results_plus1cm <- get_inflow_outflow_swmm(swmm_res_outlet_stage, 1/(2.54*12), 0, 184, 98, 0, 3.33, 3.3, 60)
# adding no noise and -1cm bias
swmm_res_results_minus1cm <- get_inflow_outflow_swmm(swmm_res_outlet_stage, -1/(2.54*12), 0, 184, 98, 0, 3.33, 3.3, 60)
# adding no noise and +5cm bias
swmm_res_results_plus5cm <- get_inflow_outflow_swmm(swmm_res_outlet_stage, 5/(2.54*12), 0, 184, 98, 0, 3.33, 3.3, 60)
# adding no noise and -5cm bias
swmm_res_results_minus5cm <- get_inflow_outflow_swmm(swmm_res_outlet_stage, -5/(2.54*12), 0, 184, 98, 0, 3.33, 3.3, 60)
# typical noise and +1cm bias
swmm_res_results_typical_noise_plus1cm <- get_inflow_outflow_swmm(swmm_res_outlet_stage, 1/(2.54*12), 0.01, 184, 98, 0, 3.33, 3.3, 60)
# typical noise and -1cm bias
swmm_res_results_typical_noise_minus1cm <- get_inflow_outflow_swmm(swmm_res_outlet_stage, -1/(2.54*12), 0.01, 184, 98, 0, 3.33, 3.3, 60)
# typical noise and +5cm bias
swmm_res_results_typical_noise_plus5cm <- get_inflow_outflow_swmm(swmm_res_outlet_stage, 5/(2.54*12), 0.01, 184, 98, 0, 3.33, 3.3, 60)
# typical noise and -5cm bias
swmm_res_results_typical_noise_minus5cm <- get_inflow_outflow_swmm(swmm_res_outlet_stage, -5/(2.54*12), 0.01, 184, 98, 0, 3.33, 3.3, 60)
```

SWMM Results Differences
```{r}
# Calculate percent and magnitude difference from the base results

# Typical noise
swmm_inflow_typical_noise_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise$Inflow.cfs)
swmm_outflow_typical_noise_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise$Outflow.cfs)
swmm_inflow_typical_noise_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise$Inflow.cfs)
swmm_outflow_typical_noise_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise$Outflow.cfs)

# Maximum noise
swmm_inflow_max_noise_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_max_noise$Inflow.cfs)
swmm_outflow_max_noise_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_max_noise$Outflow.cfs)
swmm_inflow_max_noise_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_max_noise$Inflow.cfs)
swmm_outflow_max_noise_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_max_noise$Outflow.cfs)

# +1cm bias
swmm_inflow_plus1cm_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_plus1cm$Inflow.cfs)
swmm_outflow_plus1cm_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_plus1cm$Outflow.cfs)
swmm_inflow_plus1cm_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_plus1cm$Inflow.cfs)
swmm_outflow_plus1cm_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_plus1cm$Outflow.cfs)

# -1cm bias
swmm_inflow_minus1cm_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_minus1cm$Inflow.cfs)
swmm_outflow_minus1cm_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_minus1cm$Outflow.cfs)
swmm_inflow_minus1cm_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_minus1cm$Inflow.cfs)
swmm_outflow_minus1cm_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_minus1cm$Outflow.cfs)

# +5cm bias
swmm_inflow_plus5cm_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_plus5cm$Inflow.cfs)
swmm_outflow_plus5cm_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_plus5cm$Outflow.cfs)
swmm_inflow_plus5cm_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_plus5cm$Inflow.cfs)
swmm_outflow_plus5cm_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_plus5cm$Outflow.cfs)

# -5cm bias
swmm_inflow_minus5cm_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_minus5cm$Inflow.cfs)
swmm_outflow_minus5cm_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_minus5cm$Outflow.cfs)
swmm_inflow_minus5cm_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_minus5cm$Inflow.cfs)
swmm_outflow_minus5cm_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_minus5cm$Outflow.cfs)

# +1cm bias and typical noise
swmm_inflow_typical_noise_plus1cm_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise_plus1cm$Inflow.cfs)
swmm_outflow_typical_noise_plus1cm_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise_plus1cm$Outflow.cfs)
swmm_inflow_typical_noise_plus1cm_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise_plus1cm$Inflow.cfs)
swmm_outflow_typical_noise_plus1cm_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise_plus1cm$Outflow.cfs)

# -1cm bias and typical noise
swmm_inflow_typical_noise_minus1cm_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise_minus1cm$Inflow.cfs)
swmm_outflow_typical_noise_minus1cm_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise_minus1cm$Outflow.cfs)
swmm_inflow_typical_noise_minus1cm_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise_minus1cm$Inflow.cfs)
swmm_outflow_typical_noise_minus1cm_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise_minus1cm$Outflow.cfs)

# +5cm bias and typical noise
swmm_inflow_typical_noise_plus5cm_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise_plus5cm$Inflow.cfs)
swmm_outflow_typical_noise_plus5cm_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise_plus5cm$Outflow.cfs)
swmm_inflow_typical_noise_plus5cm_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise_plus5cm$Inflow.cfs)
swmm_outflow_typical_noise_plus5cm_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise_plus5cm$Outflow.cfs)

# -5cm bias and typical noise
swmm_inflow_typical_noise_minus5cm_diff <- calc_magnitude_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise_minus5cm$Inflow.cfs)
swmm_outflow_typical_noise_minus5cm_diff <- calc_magnitude_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise_minus5cm$Outflow.cfs)
swmm_inflow_typical_noise_minus5cm_percent_diff <- calc_percent_difference(swmm_results_base$Inflow.cfs, swmm_results_typical_noise_minus5cm$Inflow.cfs)
swmm_outflow_typical_noise_minus5cm_percent_diff <- calc_percent_difference(swmm_results_base$Outflow.cfs, swmm_results_typical_noise_minus5cm$Outflow.cfs)

```

SWMM Results Differences H=5, L=10
```{r}
# Calculate percent and magnitude difference from the base results

# Typical noise
swmm_h5l10_inflow_typical_noise_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise$Outflow.cfs)
swmm_h5l10_inflow_typical_noise_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise$Outflow.cfs)

# Maximum noise
swmm_h5l10_inflow_max_noise_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_max_noise$Inflow.cfs)
swmm_h5l10_outflow_max_noise_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_max_noise$Outflow.cfs)
swmm_h5l10_inflow_max_noise_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_max_noise$Inflow.cfs)
swmm_h5l10_outflow_max_noise_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_max_noise$Outflow.cfs)

# +1cm bias
swmm_h5l10_inflow_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_plus1cm$Inflow.cfs)
swmm_h5l10_outflow_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_plus1cm$Outflow.cfs)
swmm_h5l10_inflow_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_plus1cm$Inflow.cfs)
swmm_h5l10_outflow_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_plus1cm$Outflow.cfs)

# -1cm bias
swmm_h5l10_inflow_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_minus1cm$Inflow.cfs)
swmm_h5l10_outflow_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_minus1cm$Outflow.cfs)
swmm_h5l10_inflow_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_minus1cm$Inflow.cfs)
swmm_h5l10_outflow_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_minus1cm$Outflow.cfs)

# +5cm bias
swmm_h5l10_inflow_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_plus5cm$Inflow.cfs)
swmm_h5l10_outflow_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_plus5cm$Outflow.cfs)
swmm_h5l10_inflow_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_plus5cm$Inflow.cfs)
swmm_h5l10_outflow_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_plus5cm$Outflow.cfs)

# -5cm bias
swmm_h5l10_inflow_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_minus5cm$Inflow.cfs)
swmm_h5l10_outflow_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_minus5cm$Outflow.cfs)
swmm_h5l10_inflow_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_minus5cm$Inflow.cfs)
swmm_h5l10_outflow_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_minus5cm$Outflow.cfs)

# +1cm bias and typical noise
swmm_h5l10_inflow_typical_noise_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise_plus1cm$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise_plus1cm$Outflow.cfs)
swmm_h5l10_inflow_typical_noise_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise_plus1cm$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise_plus1cm$Outflow.cfs)

# -1cm bias and typical noise
swmm_h5l10_inflow_typical_noise_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise_minus1cm$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise_minus1cm$Outflow.cfs)
swmm_h5l10_inflow_typical_noise_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise_minus1cm$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise_minus1cm$Outflow.cfs)

# +5cm bias and typical noise
swmm_h5l10_inflow_typical_noise_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise_plus5cm$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise_plus5cm$Outflow.cfs)
swmm_h5l10_inflow_typical_noise_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise_plus5cm$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise_plus5cm$Outflow.cfs)

# -5cm bias and typical noise
swmm_h5l10_inflow_typical_noise_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise_minus5cm$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise_minus5cm$Outflow.cfs)
swmm_h5l10_inflow_typical_noise_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Inflow.cfs, swmm_results_h5l10_typical_noise_minus5cm$Inflow.cfs)
swmm_h5l10_outflow_typical_noise_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l10_base$Outflow.cfs, swmm_results_h5l10_typical_noise_minus5cm$Outflow.cfs)

```

SWMM Results Differences H=5, L=5
```{r}
# Calculate percent and magnitude difference from the base results

# Typical noise
swmm_h5l5_inflow_typical_noise_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise$Outflow.cfs)
swmm_h5l5_inflow_typical_noise_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise$Outflow.cfs)

# Maximum noise
swmm_h5l5_inflow_max_noise_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_max_noise$Inflow.cfs)
swmm_h5l5_outflow_max_noise_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_max_noise$Outflow.cfs)
swmm_h5l5_inflow_max_noise_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_max_noise$Inflow.cfs)
swmm_h5l5_outflow_max_noise_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_max_noise$Outflow.cfs)

# +1cm bias
swmm_h5l5_inflow_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_plus1cm$Inflow.cfs)
swmm_h5l5_outflow_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_plus1cm$Outflow.cfs)
swmm_h5l5_inflow_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_plus1cm$Inflow.cfs)
swmm_h5l5_outflow_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_plus1cm$Outflow.cfs)

# -1cm bias
swmm_h5l5_inflow_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_minus1cm$Inflow.cfs)
swmm_h5l5_outflow_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_minus1cm$Outflow.cfs)
swmm_h5l5_inflow_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_minus1cm$Inflow.cfs)
swmm_h5l5_outflow_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_minus1cm$Outflow.cfs)

# +5cm bias
swmm_h5l5_inflow_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_plus5cm$Inflow.cfs)
swmm_h5l5_outflow_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_plus5cm$Outflow.cfs)
swmm_h5l5_inflow_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_plus5cm$Inflow.cfs)
swmm_h5l5_outflow_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_plus5cm$Outflow.cfs)

# -5cm bias
swmm_h5l5_inflow_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_minus5cm$Inflow.cfs)
swmm_h5l5_outflow_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_minus5cm$Outflow.cfs)
swmm_h5l5_inflow_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_minus5cm$Inflow.cfs)
swmm_h5l5_outflow_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_minus5cm$Outflow.cfs)

# +1cm bias and typical noise
swmm_h5l5_inflow_typical_noise_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise_plus1cm$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise_plus1cm$Outflow.cfs)
swmm_h5l5_inflow_typical_noise_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise_plus1cm$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise_plus1cm$Outflow.cfs)

# -1cm bias and typical noise
swmm_h5l5_inflow_typical_noise_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise_minus1cm$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise_minus1cm$Outflow.cfs)
swmm_h5l5_inflow_typical_noise_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise_minus1cm$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise_minus1cm$Outflow.cfs)

# +5cm bias and typical noise
swmm_h5l5_inflow_typical_noise_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise_plus5cm$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise_plus5cm$Outflow.cfs)
swmm_h5l5_inflow_typical_noise_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise_plus5cm$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise_plus5cm$Outflow.cfs)

# -5cm bias and typical noise
swmm_h5l5_inflow_typical_noise_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise_minus5cm$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise_minus5cm$Outflow.cfs)
swmm_h5l5_inflow_typical_noise_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Inflow.cfs, swmm_results_h5l5_typical_noise_minus5cm$Inflow.cfs)
swmm_h5l5_outflow_typical_noise_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l5_base$Outflow.cfs, swmm_results_h5l5_typical_noise_minus5cm$Outflow.cfs)

```

SWMM Results Differences H=5, L=1
```{r}
# Calculate percent and magnitude difference from the base results

# Typical noise
swmm_h5l1_inflow_typical_noise_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise$Outflow.cfs)
swmm_h5l1_inflow_typical_noise_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise$Outflow.cfs)

# Maximum noise
swmm_h5l1_inflow_max_noise_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_max_noise$Inflow.cfs)
swmm_h5l1_outflow_max_noise_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_max_noise$Outflow.cfs)
swmm_h5l1_inflow_max_noise_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_max_noise$Inflow.cfs)
swmm_h5l1_outflow_max_noise_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_max_noise$Outflow.cfs)

# +1cm bias
swmm_h5l1_inflow_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_plus1cm$Inflow.cfs)
swmm_h5l1_outflow_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_plus1cm$Outflow.cfs)
swmm_h5l1_inflow_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_plus1cm$Inflow.cfs)
swmm_h5l1_outflow_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_plus1cm$Outflow.cfs)

# -1cm bias
swmm_h5l1_inflow_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_minus1cm$Inflow.cfs)
swmm_h5l1_outflow_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_minus1cm$Outflow.cfs)
swmm_h5l1_inflow_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_minus1cm$Inflow.cfs)
swmm_h5l1_outflow_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_minus1cm$Outflow.cfs)

# +5cm bias
swmm_h5l1_inflow_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_plus5cm$Inflow.cfs)
swmm_h5l1_outflow_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_plus5cm$Outflow.cfs)
swmm_h5l1_inflow_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_plus5cm$Inflow.cfs)
swmm_h5l1_outflow_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_plus5cm$Outflow.cfs)

# -5cm bias
swmm_h5l1_inflow_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_minus5cm$Inflow.cfs)
swmm_h5l1_outflow_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_minus5cm$Outflow.cfs)
swmm_h5l1_inflow_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_minus5cm$Inflow.cfs)
swmm_h5l1_outflow_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_minus5cm$Outflow.cfs)

# +1cm bias and typical noise
swmm_h5l1_inflow_typical_noise_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise_plus1cm$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_plus1cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise_plus1cm$Outflow.cfs)
swmm_h5l1_inflow_typical_noise_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise_plus1cm$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_plus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise_plus1cm$Outflow.cfs)

# -1cm bias and typical noise
swmm_h5l1_inflow_typical_noise_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise_minus1cm$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_minus1cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise_minus1cm$Outflow.cfs)
swmm_h5l1_inflow_typical_noise_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise_minus1cm$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_minus1cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise_minus1cm$Outflow.cfs)

# +5cm bias and typical noise
swmm_h5l1_inflow_typical_noise_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise_plus5cm$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_plus5cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise_plus5cm$Outflow.cfs)
swmm_h5l1_inflow_typical_noise_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise_plus5cm$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_plus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise_plus5cm$Outflow.cfs)

# -5cm bias and typical noise
swmm_h5l1_inflow_typical_noise_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise_minus5cm$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_minus5cm_diff <- calc_magnitude_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise_minus5cm$Outflow.cfs)
swmm_h5l1_inflow_typical_noise_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Inflow.cfs, swmm_results_h5l1_typical_noise_minus5cm$Inflow.cfs)
swmm_h5l1_outflow_typical_noise_minus5cm_percent_diff <- calc_percent_difference(swmm_results_h5l1_base$Outflow.cfs, swmm_results_h5l1_typical_noise_minus5cm$Outflow.cfs)

```

Plot SWMM Results H5L10
```{r}
# Plot showing noise
plot(swmm_time[1:300], swmm_h5l10_outflow[1:300], type = "l", col = colors_red[1], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow with Noise", ylim = c(-10, 70), lty = 3)
lines(swmm_time[1:300], swmm_results_h5l10_max_noise$Inflow.cfs[1:300], col = colors_blue[5])
lines(swmm_time[1:300], swmm_results_h5l10_max_noise$Outflow.cfs[1:300], col = colors_red[5], lty = 3)
lines(swmm_time[1:300], swmm_results_h5l10_typical_noise$Inflow.cfs[1:300], col = colors_blue[3])
lines(swmm_time[1:300], swmm_results_h5l10_typical_noise$Outflow.cfs[1:300], col = colors_red[3], lty = 3)
lines(swmm_time[1:300], swmm_results_h5l10_base$Inflow.cfs[1:300], col = colors_blue[1])
grid()
legend("topright", legend = c("Inflow Raw", "Inflow Typical Noise", "Inflow Max Noise", "Outflow Raw", "Outflow Typical Noise", "Outflow Max Noise"), col = c(colors_blue[1], colors_blue[3], colors_blue[5], colors_red[1], colors_red[3], colors_red[5]), lty = c(1, 1, 1, 3, 3, 3), lwd = 2, cex = 0.7)

# Plot showing bias
plot(swmm_time[5:300], swmm_h5l10_outflow[5:300], type = "l", col = colors_red[1], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow with Bias", ylim = c(-10, 70), lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_plus1cm$Inflow.cfs[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_results_h5l10_plus1cm$Outflow.cfs[5:300], col = colors_red[2], lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_minus1cm$Inflow.cfs[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_results_h5l10_minus1cm$Outflow.cfs[5:300], col = colors_red[3], lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_plus5cm$Inflow.cfs[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_results_h5l10_plus5cm$Outflow.cfs[5:300], col = colors_red[4], lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_minus5cm$Inflow.cfs[5:300], col = colors_blue[5])
lines(swmm_time[5:300], swmm_results_h5l10_minus5cm$Outflow.cfs[5:300], col = colors_red[5], lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_base$Inflow.cfs[5:300], col = colors_blue[1])
grid()
legend("topright", legend = c("Inflow Raw", "Inflow +1cm Bias", "Inflow -1cm Bias", "Inflow +5cm Bias", "Inflow -5cm Bias", "Outflow Raw", "Outflow +1cm Bias", "Outflow -1cm Bias", "Outflow +5cm Bias", "Outflow -5cm Bias"), col = c(colors_blue[1], colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[1], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.7)

# Plot showing noise and bias
plot(swmm_time[5:300], swmm_h5l10_outflow[5:300], type = "l", col = colors_red[1], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow with Noise and Bias", ylim = c(-10, 70), lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_typical_noise_plus1cm$Inflow.cfs[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_results_h5l10_typical_noise_plus1cm$Outflow.cfs[5:300], col = colors_red[2], lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_typical_noise_minus1cm$Inflow.cfs[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_results_h5l10_typical_noise_minus1cm$Outflow.cfs[5:300], col = colors_red[3], lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_typical_noise_plus5cm$Inflow.cfs[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_results_h5l10_typical_noise_plus5cm$Outflow.cfs[5:300], col = colors_red[4], lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_typical_noise_minus5cm$Inflow.cfs[5:300], col = colors_blue[5])
lines(swmm_time[5:300], swmm_results_h5l10_typical_noise_minus5cm$Outflow.cfs[5:300], col = colors_red[5], lty = 3)
lines(swmm_time[5:300], swmm_results_h5l10_base$Inflow.cfs[5:300], col = colors_blue[1])
grid()
legend("topright", legend = c("Inflow Raw", "Inflow Typical Noise +1cm Bias", "Inflow Typical Noise -1cm Bias", "Inflow Typical Noise +5cm Bias", "Inflow Typical Noise -5cm Bias", "Outflow Raw", "Outflow Typical Noise +1cm Bias", "Outflow Typical Noise -1cm Bias", "Outflow Typical Noise +5cm Bias", "Outflow Typical Noise -5cm Bias"), col = c(colors_blue[1], colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[1], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.7)
```

Plot SWMM Results H5L5
```{r}
par(pin = c(5, 2.5))  # 5 inches wide, 2 inches tall
par(mgp = c(2, 0.5, 0))  # Move axis titles closer to the axis

# Plot showing noise
plot(swmm_time[1:300], swmm_h5l5_outflow[1:300], type = "l", col = colors_red[5], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "", ylim = c(-10, 70), cex.lab = 1.1)
lines(swmm_time[1:300], swmm_results_h5l5_max_noise$Inflow.cfs[1:300], col = colors_blue[1])
lines(swmm_time[1:300], swmm_results_h5l5_max_noise$Outflow.cfs[1:300], col = colors_red[1])
lines(swmm_time[1:300], swmm_results_h5l5_typical_noise$Inflow.cfs[1:300], col = colors_blue[3])
lines(swmm_time[1:300], swmm_results_h5l5_typical_noise$Outflow.cfs[1:300], col = colors_red[3])
lines(swmm_time[1:300], swmm_results_h5l5_base$Inflow.cfs[1:300], col = colors_blue[5])
lines(swmm_time[1:300], swmm_h5l5_outflow[1:300], col = "black")
lines(swmm_time[1:300], swmm_inflow[1:300], col = "black")
grid()
legend("topright", legend = c("Inflow No Noise No Bias", "Inflow Typical Noise", "Inflow Max Noise", "Outflow No Noise No Bias", "Outflow Typical Noise", "Outflow Max Noise"), col = c(colors_blue[5], colors_blue[3], colors_blue[1], colors_red[5], colors_red[3], colors_red[1]), lty = c(1, 1, 1, 1,1,1), lwd = 2, cex = 0.8)

# Plot showing bias
plot(swmm_time[5:300], swmm_h5l5_outflow[5:300], type = "l", col = colors_red[5], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "", ylim = c(-10, 70), cex.lab = 1.1)
lines(swmm_time[5:300], swmm_results_h5l5_plus1cm$Inflow.cfs[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_results_h5l5_plus1cm$Outflow.cfs[5:300], col = colors_red[4])
lines(swmm_time[5:300], swmm_results_h5l5_minus1cm$Inflow.cfs[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_results_h5l5_minus1cm$Outflow.cfs[5:300], col = colors_red[3])
lines(swmm_time[5:300], swmm_results_h5l5_plus5cm$Inflow.cfs[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_results_h5l5_plus5cm$Outflow.cfs[5:300], col = colors_red[2])
lines(swmm_time[5:300], swmm_results_h5l5_minus5cm$Inflow.cfs[5:300], col = colors_blue[1])
lines(swmm_time[5:300], swmm_results_h5l5_minus5cm$Outflow.cfs[5:300], col = colors_red[1])
lines(swmm_time[5:300], swmm_results_h5l5_base$Inflow.cfs[5:300], col = colors_blue[5])
lines(swmm_time[1:300], swmm_h5l5_outflow[1:300], col = "black")
lines(swmm_time[1:300], swmm_inflow[1:300], col = "black")
grid()
legend("topright", legend = c("Inflow No Noise No Bias", "Inflow +1cm Bias", "Inflow -1cm Bias", "Inflow +5cm Bias", "Inflow -5cm Bias", "Outflow No Noise No Bias", "Outflow +1cm Bias", "Outflow -1cm Bias", "Outflow +5cm Bias", "Outflow -5cm Bias"), col = c(colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], colors_blue[1], colors_red[5], colors_red[4], colors_red[3], colors_red[2], colors_red[1]), lty = c(1, 1, 1, 1, 1, 1,1,1,1,1), lwd = 2, cex = 0.8)

# Plot showing noise and bias
plot(swmm_time[5:300], swmm_h5l5_outflow[5:300], type = "l", col = colors_red[5], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "", ylim = c(-10, 70), cex.lab = 1.1)
lines(swmm_time[5:300], swmm_results_h5l5_typical_noise_plus1cm$Inflow.cfs[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_results_h5l5_typical_noise_plus1cm$Outflow.cfs[5:300], col = colors_red[4])
lines(swmm_time[5:300], swmm_results_h5l5_typical_noise_minus1cm$Inflow.cfs[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_results_h5l5_typical_noise_minus1cm$Outflow.cfs[5:300], col = colors_red[3])
lines(swmm_time[5:300], swmm_results_h5l5_typical_noise_plus5cm$Inflow.cfs[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_results_h5l5_typical_noise_plus5cm$Outflow.cfs[5:300], col = colors_red[2])
lines(swmm_time[5:300], swmm_results_h5l5_typical_noise_minus5cm$Inflow.cfs[5:300], col = colors_blue[1])
lines(swmm_time[5:300], swmm_results_h5l5_typical_noise_minus5cm$Outflow.cfs[5:300], col = colors_red[1])
lines(swmm_time[5:300], swmm_results_h5l5_base$Inflow.cfs[5:300], col = colors_blue[5])
lines(swmm_time[1:300], swmm_h5l5_outflow[1:300], col = "black")
lines(swmm_time[1:300], swmm_inflow[1:300], col = "black")
grid()
legend("topright", legend = c("Inflow No Noise No Bias", "Inflow Typical Noise +1cm Bias", "Inflow Typical Noise -1cm Bias", "Inflow Typical Noise +5cm Bias", "Inflow Typical Noise -5cm Bias", "Outflow No Noise No Bias", "Outflow Typical Noise +1cm Bias", "Outflow Typical Noise -1cm Bias", "Outflow Typical Noise +5cm Bias", "Outflow Typical Noise -5cm Bias"), col = c(colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], colors_blue[1], colors_red[5], colors_red[4], colors_red[3], colors_red[2], colors_red[1]), lty = c(1, 1, 1, 1, 1, 1,1,1,1,1), lwd = 2, cex = 0.8)
```

Plot SWMM Results H5L1
```{r}
par(pin = c(5, 2.5))  # 5 inches wide, 2 inches tall
par(mgp = c(2, 0.5, 0))  # Move axis titles closer to the axis

# Plot showing noise
plot(swmm_time[1:300], swmm_h5l1_outflow[1:300], type = "l", col = colors_red[5], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "", ylim = c(-10, 70), cex.lab = 1.1)
lines(swmm_time[1:300], swmm_results_h5l1_max_noise$Inflow.cfs[1:300], col = colors_blue[1])
lines(swmm_time[1:300], swmm_results_h5l1_max_noise$Outflow.cfs[1:300], col = colors_red[1])
lines(swmm_time[1:300], swmm_results_h5l1_typical_noise$Inflow.cfs[1:300], col = colors_blue[3])
lines(swmm_time[1:300], swmm_results_h5l1_typical_noise$Outflow.cfs[1:300], col = colors_red[3])
lines(swmm_time[1:300], swmm_results_h5l1_base$Inflow.cfs[1:300], col = colors_blue[5])
grid()
legend("topright", legend = c("Inflow Raw", "Inflow Typical Noise", "Inflow Max Noise", "Outflow Raw", "Outflow Typical Noise", "Outflow Max Noise"), col = c(colors_blue[5], colors_blue[3], colors_blue[1], colors_red[5], colors_red[3], colors_red[1]), lty = c(1, 1, 1, 1,1,1), lwd = 2, cex = 0.8)

# Plot showing bias
plot(swmm_time[5:300], swmm_h5l1_outflow[5:300], type = "l", col = colors_red[5], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "", ylim = c(-10, 70), cex.lab = 1.1)
lines(swmm_time[5:300], swmm_results_h5l1_plus1cm$Inflow.cfs[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_results_h5l1_plus1cm$Outflow.cfs[5:300], col = colors_red[4])
lines(swmm_time[5:300], swmm_results_h5l1_minus1cm$Inflow.cfs[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_results_h5l1_minus1cm$Outflow.cfs[5:300], col = colors_red[3])
lines(swmm_time[5:300], swmm_results_h5l1_plus5cm$Inflow.cfs[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_results_h5l1_plus5cm$Outflow.cfs[5:300], col = colors_red[2])
lines(swmm_time[5:300], swmm_results_h5l1_minus5cm$Inflow.cfs[5:300], col = colors_blue[1])
lines(swmm_time[5:300], swmm_results_h5l1_minus5cm$Outflow.cfs[5:300], col = colors_red[1])
lines(swmm_time[5:300], swmm_results_h5l1_base$Inflow.cfs[5:300], col = colors_blue[5])
grid()
legend("topright", legend = c("Inflow Raw", "Inflow +1cm Bias", "Inflow -1cm Bias", "Inflow +5cm Bias", "Inflow -5cm Bias", "Outflow Raw", "Outflow +1cm Bias", "Outflow -1cm Bias", "Outflow +5cm Bias", "Outflow -5cm Bias"), col = c(colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], colors_blue[1], colors_red[5], colors_red[4], colors_red[3], colors_red[2], colors_red[1]), lty = c(1, 1, 1, 1, 1, 1,1,1,1,1), lwd = 2, cex = 0.8)

# Plot showing noise and bias
plot(swmm_time[5:300], swmm_h5l1_outflow[5:300], type = "l", col = colors_red[5], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "", ylim = c(-10, 70), cex.lab = 1.1)
lines(swmm_time[5:300], swmm_results_h5l1_typical_noise_plus1cm$Inflow.cfs[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_results_h5l1_typical_noise_plus1cm$Outflow.cfs[5:300], col = colors_red[4])
lines(swmm_time[5:300], swmm_results_h5l1_typical_noise_minus1cm$Inflow.cfs[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_results_h5l1_typical_noise_minus1cm$Outflow.cfs[5:300], col = colors_red[3])
lines(swmm_time[5:300], swmm_results_h5l1_typical_noise_plus5cm$Inflow.cfs[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_results_h5l1_typical_noise_plus5cm$Outflow.cfs[5:300], col = colors_red[2])
lines(swmm_time[5:300], swmm_results_h5l1_typical_noise_minus5cm$Inflow.cfs[5:300], col = colors_blue[1])
lines(swmm_time[5:300], swmm_results_h5l1_typical_noise_minus5cm$Outflow.cfs[5:300], col = colors_red[1])
lines(swmm_time[5:300], swmm_results_h5l1_base$Inflow.cfs[5:300], col = colors_blue[5])
grid()
legend("topright", legend = c("Inflow Raw", "Inflow Typical Noise +1cm Bias", "Inflow Typical Noise -1cm Bias", "Inflow Typical Noise +5cm Bias", "Inflow Typical Noise -5cm Bias", "Outflow Raw", "Outflow Typical Noise +1cm Bias", "Outflow Typical Noise -1cm Bias", "Outflow Typical Noise +5cm Bias", "Outflow Typical Noise -5cm Bias"), col = c(colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], colors_blue[1], colors_red[5], colors_red[4], colors_red[3], colors_red[2], colors_red[1]), lty = c(1, 1, 1, 1, 1, 1,1,1,1,1), lwd = 2, cex = 0.8)
```

Plot SWMM Results
```{r}
# Plot showing noise
plot(swmm_time[1:300], swmm_outflow[1:300], type = "l", col = colors_red[1], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow with Noise", ylim = c(min(swmm_results_max_noise$Inflow.cfs), 60), lty = 3)
lines(swmm_time[1:300], swmm_results_max_noise$Inflow.cfs[1:300], col = colors_blue[5])
lines(swmm_time[1:300], swmm_results_max_noise$Outflow.cfs[1:300], col = colors_red[5], lty = 3)
lines(swmm_time[1:300], swmm_results_typical_noise$Inflow.cfs[1:300], col = colors_blue[3])
lines(swmm_time[1:300], swmm_results_typical_noise$Outflow.cfs[1:300], col = colors_red[3], lty = 3)
lines(swmm_time[1:300], swmm_results_base$Inflow.cfs[1:300], col = colors_blue[1])
grid()
legend("topright", legend = c("Inflow Raw", "Inflow Typical Noise", "Inflow Max Noise", "Outflow Raw", "Outflow Typical Noise", "Outflow Max Noise"), col = c(colors_blue[1], colors_blue[3], colors_blue[5], colors_red[1], colors_red[3], colors_red[5]), lty = c(1, 1, 1, 3, 3, 3), lwd = 2, cex = 0.7)

# Plot showing bias
plot(swmm_time[5:300], swmm_outflow[5:300], type = "l", col = colors_red[1], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow with Bias", ylim = c(min(swmm_results_max_noise$Inflow.cfs), 60), lty = 3)
lines(swmm_time[5:300], swmm_results_plus1cm$Inflow.cfs[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_results_plus1cm$Outflow.cfs[5:300], col = colors_red[2], lty = 3)
lines(swmm_time[5:300], swmm_results_minus1cm$Inflow.cfs[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_results_minus1cm$Outflow.cfs[5:300], col = colors_red[3], lty = 3)
lines(swmm_time[5:300], swmm_results_plus5cm$Inflow.cfs[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_results_plus5cm$Outflow.cfs[5:300], col = colors_red[4], lty = 3)
lines(swmm_time[5:300], swmm_results_minus5cm$Inflow.cfs[5:300], col = colors_blue[5])
lines(swmm_time[5:300], swmm_results_minus5cm$Outflow.cfs[5:300], col = colors_red[5], lty = 3)
lines(swmm_time[5:300], swmm_results_base$Inflow.cfs[5:300], col = colors_blue[1])
grid()
legend("topright", legend = c("Inflow Raw", "Inflow +1cm Bias", "Inflow -1cm Bias", "Inflow +5cm Bias", "Inflow -5cm Bias", "Outflow Raw", "Outflow +1cm Bias", "Outflow -1cm Bias", "Outflow +5cm Bias", "Outflow -5cm Bias"), col = c(colors_blue[1], colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[1], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.7)

# Plot showing noise and bias
plot(swmm_time[5:300], swmm_outflow[5:300], type = "l", col = colors_red[1], xlab = "Time (hours)", ylab = "Flow (cfs)", main = "SWMM Inflow/Outflow with Noise and Bias", ylim = c(min(swmm_results_max_noise$Inflow.cfs), 60), lty = 3)
lines(swmm_time[5:300], swmm_results_typical_noise_plus1cm$Inflow.cfs[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_results_typical_noise_plus1cm$Outflow.cfs[5:300], col = colors_red[2], lty = 3)
lines(swmm_time[5:300], swmm_results_typical_noise_minus1cm$Inflow.cfs[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_results_typical_noise_minus1cm$Outflow.cfs[5:300], col = colors_red[3], lty = 3)
lines(swmm_time[5:300], swmm_results_typical_noise_plus5cm$Inflow.cfs[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_results_typical_noise_plus5cm$Outflow.cfs[5:300], col = colors_red[4], lty = 3)
lines(swmm_time[5:300], swmm_results_typical_noise_minus5cm$Inflow.cfs[5:300], col = colors_blue[5])
lines(swmm_time[5:300], swmm_results_typical_noise_minus5cm$Outflow.cfs[5:300], col = colors_red[5], lty = 3)
lines(swmm_time[5:300], swmm_results_base$Inflow.cfs[5:300], col = colors_blue[1])
grid()
legend("topright", legend = c("Inflow Raw", "Inflow Typical Noise +1cm Bias", "Inflow Typical Noise -1cm Bias", "Inflow Typical Noise +5cm Bias", "Inflow Typical Noise -5cm Bias", "Outflow Raw", "Outflow Typical Noise +1cm Bias", "Outflow Typical Noise -1cm Bias", "Outflow Typical Noise +5cm Bias", "Outflow Typical Noise -5cm Bias"), col = c(colors_blue[1], colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[1], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.7)

```

Plot SWMM Results Differences H5L10
```{r}
# Plot showing noise differences
plot(swmm_time[1:300], swmm_h5l10_inflow_typical_noise_diff[1:300], type = "l", col = colors_blue[3], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "SWMM Inflow/Outflow Noise Differences", ylim = c(-20,40))
lines(swmm_time[1:300], swmm_h5l10_outflow_typical_noise_diff[1:300], col = colors_red[3], lty = 3)
lines(swmm_time[1:300], swmm_h5l10_inflow_max_noise_diff[1:300], col = colors_blue[5])
lines(swmm_time[1:300], swmm_h5l10_outflow_max_noise_diff[1:300], col = colors_red[5], lty = 3)
grid()
legend("topright", legend = c("Inflow Typical Noise Difference", "Inflow Max Noise Difference", "Outflow Typical Noise Difference", "Outflow Max Noise Difference"), col = c(colors_blue[3], colors_blue[5], colors_red[3], colors_red[5]), lty = c(1, 1, 1, 3, 3, 3), lwd = 2, cex = 0.7)


# Plot showing bias differences
plot(swmm_time[5:300], swmm_h5l10_inflow_plus1cm_diff[5:300], type = "l", col = colors_blue[2], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "SWMM Inflow/Outflow Bias Differences", ylim = c(-20,40))
lines(swmm_time[5:300], swmm_h5l10_outflow_plus1cm_diff[5:300], col = colors_red[2], lty = 3)
lines(swmm_time[5:300], swmm_h5l10_inflow_minus1cm_diff[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_h5l10_outflow_minus1cm_diff[5:300], col = colors_red[3], lty = 3)
lines(swmm_time[5:300], swmm_h5l10_inflow_plus5cm_diff[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_h5l10_outflow_plus5cm_diff[5:300], col = colors_red[4], lty = 3)
lines(swmm_time[5:300], swmm_h5l10_inflow_minus5cm_diff[5:300], col = colors_blue[5])
lines(swmm_time[5:300], swmm_h5l10_outflow_minus5cm_diff[5:300], col = colors_red[5], lty = 3)
grid()
legend("topright", legend = c("Inflow +1cm Bias Difference", "Inflow -1cm Bias Difference", "Inflow +5cm Bias Difference", "Inflow -5cm Bias Difference", "Outflow +1cm Bias Difference", "Outflow -1cm Bias Difference", "Outflow +5cm Bias Difference", "Outflow -5cm Bias Difference"), col = c(colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.7)


# Plots showing noise and bias differences
plot(swmm_time[5:300], swmm_h5l10_inflow_typical_noise_plus1cm_diff[5:300], type = "l", col = colors_blue[2], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "SWMM Inflow/Outflow Noise and Bias Differences", ylim = c(-20,40))
lines(swmm_time[5:300], swmm_h5l10_outflow_typical_noise_plus1cm_diff[5:300], col = colors_red[2], lty = 3)
lines(swmm_time[5:300], swmm_h5l10_inflow_typical_noise_minus1cm_diff[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_h5l10_outflow_typical_noise_minus1cm_diff[5:300], col = colors_red[3], lty = 3)
lines(swmm_time[5:300], swmm_h5l10_inflow_typical_noise_plus5cm_diff[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_h5l10_outflow_typical_noise_plus5cm_diff[5:300], col = colors_red[4], lty = 3)
lines(swmm_time[5:300], swmm_h5l10_inflow_typical_noise_minus5cm_diff[5:300], col = colors_blue[5])
lines(swmm_time[5:300], swmm_h5l10_outflow_typical_noise_minus5cm_diff[5:300], col = colors_red[5], lty = 3)
grid()
legend("topright", legend = c("Inflow Typical Noise +1cm Bias Difference", "Inflow Typical Noise -1cm Bias Difference", "Inflow Typical Noise +5cm Bias Difference", "Inflow Typical Noise -5cm Bias Difference", "Outflow Typical Noise +1cm Bias Difference", "Outflow Typical Noise -1cm Bias Difference", "Outflow Typical Noise +5cm Bias Difference", "Outflow Typical Noise -5cm Bias Difference"), col = c(colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.6)

```

Plot SWMM Results Differences H5L5
```{r}
par(pin = c(5, 1.5))  # 5 inches wide, 2 inches tall
par(mgp = c(2, 0.5, 0))  # Move axis titles closer to the axis

# Plot showing noise differences
plot(swmm_time[1:300], swmm_h5l5_inflow_typical_noise_diff[1:300], type = "l", col = colors_blue[3], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "", ylim = c(-20,20))
lines(swmm_time[1:300], swmm_h5l5_outflow_typical_noise_diff[1:300], col = colors_red[3])
lines(swmm_time[1:300], swmm_h5l5_inflow_max_noise_diff[1:300], col = colors_blue[1])
lines(swmm_time[1:300], swmm_h5l5_outflow_max_noise_diff[1:300], col = colors_red[1])
grid()
#legend("topright", legend = c("Inflow Typical Noise Difference", "Inflow Max Noise Difference", "Outflow Typical Noise Difference", "Outflow Max Noise Difference"), col = c(colors_blue[3], colors_blue[5], colors_red[3], colors_red[5]), lty = c(1, 1, 1, 1,1,1), lwd = 2, cex = 0.7)


# Plot showing bias differences
plot(swmm_time[5:300], swmm_h5l5_inflow_plus1cm_diff[5:300], type = "l", col = colors_blue[4], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "", ylim = c(-20,20))
lines(swmm_time[5:300], swmm_h5l5_outflow_plus1cm_diff[5:300], col = colors_red[4])
lines(swmm_time[5:300], swmm_h5l5_inflow_minus1cm_diff[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_h5l5_outflow_minus1cm_diff[5:300], col = colors_red[3])
lines(swmm_time[5:300], swmm_h5l5_inflow_plus5cm_diff[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_h5l5_outflow_plus5cm_diff[5:300], col = colors_red[2])
lines(swmm_time[5:300], swmm_h5l5_inflow_minus5cm_diff[5:300], col = colors_blue[1])
lines(swmm_time[5:300], swmm_h5l5_outflow_minus5cm_diff[5:300], col = colors_red[1])
grid()
#legend("topright", legend = c("Inflow +1cm Bias Difference", "Inflow -1cm Bias Difference", "Inflow +5cm Bias Difference", "Inflow -5cm Bias Difference", "Outflow +1cm Bias Difference", "Outflow -1cm Bias Difference", "Outflow +5cm Bias Difference", "Outflow -5cm Bias Difference"), col = c(colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.7)


# Plots showing noise and bias differences
plot(swmm_time[5:300], swmm_h5l5_inflow_typical_noise_plus1cm_diff[5:300], type = "l", col = colors_blue[4], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "", ylim = c(-20,20))
lines(swmm_time[5:300], swmm_h5l5_outflow_typical_noise_plus1cm_diff[5:300], col = colors_red[4])
lines(swmm_time[5:300], swmm_h5l5_inflow_typical_noise_minus1cm_diff[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_h5l5_outflow_typical_noise_minus1cm_diff[5:300], col = colors_red[3])
lines(swmm_time[5:300], swmm_h5l5_inflow_typical_noise_plus5cm_diff[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_h5l5_outflow_typical_noise_plus5cm_diff[5:300], col = colors_red[2])
lines(swmm_time[5:300], swmm_h5l5_inflow_typical_noise_minus5cm_diff[5:300], col = colors_blue[1])
lines(swmm_time[5:300], swmm_h5l5_outflow_typical_noise_minus5cm_diff[5:300], col = colors_red[1])
grid()
#legend("topright", legend = c("Inflow Typical Noise +1cm Bias Difference", "Inflow Typical Noise -1cm Bias Difference", "Inflow Typical Noise +5cm Bias Difference", "Inflow Typical Noise -5cm Bias Difference", "Outflow Typical Noise +1cm Bias Difference", "Outflow Typical Noise -1cm Bias Difference", "Outflow Typical Noise +5cm Bias Difference", "Outflow Typical Noise -5cm Bias Difference"), col = c(colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.6)
```

Plot SWMM Results Differences H5L1
```{r}
par(pin = c(5, 1.5))  # 5 inches wide, 2 inches tall
par(mgp = c(2, 0.5, 0))  # Move axis titles closer to the axis

# Plot showing noise differences
plot(swmm_time[1:300], swmm_h5l1_inflow_typical_noise_diff[1:300], type = "l", col = colors_blue[3], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "", ylim = c(-20,20))
lines(swmm_time[1:300], swmm_h5l1_outflow_typical_noise_diff[1:300], col = colors_red[3])
lines(swmm_time[1:300], swmm_h5l1_inflow_max_noise_diff[1:300], col = colors_blue[1])
lines(swmm_time[1:300], swmm_h5l1_outflow_max_noise_diff[1:300], col = colors_red[1])
grid()
#legend("topright", legend = c("Inflow Typical Noise Difference", "Inflow Max Noise Difference", "Outflow Typical Noise Difference", "Outflow Max Noise Difference"), col = c(colors_blue[3], colors_blue[5], colors_red[3], colors_red[5]), lty = c(1, 1, 1, 3, 3, 3), lwd = 2, cex = 0.7)


# Plot showing bias differences
plot(swmm_time[5:300], swmm_h5l1_inflow_plus1cm_diff[5:300], type = "l", col = colors_blue[4], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "", ylim = c(-20,20))
lines(swmm_time[5:300], swmm_h5l1_outflow_plus1cm_diff[5:300], col = colors_red[4])
lines(swmm_time[5:300], swmm_h5l1_inflow_minus1cm_diff[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_h5l1_outflow_minus1cm_diff[5:300], col = colors_red[3])
lines(swmm_time[5:300], swmm_h5l1_inflow_plus5cm_diff[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_h5l1_outflow_plus5cm_diff[5:300], col = colors_red[2])
lines(swmm_time[5:300], swmm_h5l1_inflow_minus5cm_diff[5:300], col = colors_blue[1])
lines(swmm_time[5:300], swmm_h5l1_outflow_minus5cm_diff[5:300], col = colors_red[1])
grid()
#legend("topright", legend = c("Inflow +1cm Bias Difference", "Inflow -1cm Bias Difference", "Inflow +5cm Bias Difference", "Inflow -5cm Bias Difference", "Outflow +1cm Bias Difference", "Outflow -1cm Bias Difference", "Outflow +5cm Bias Difference", "Outflow -5cm Bias Difference"), col = c(colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.7)


# Plots showing noise and bias differences
plot(swmm_time[5:300], swmm_h5l1_inflow_typical_noise_plus1cm_diff[5:300], type = "l", col = colors_blue[4], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "", ylim = c(-20,20))
lines(swmm_time[5:300], swmm_h5l1_outflow_typical_noise_plus1cm_diff[5:300], col = colors_red[4])
lines(swmm_time[5:300], swmm_h5l1_inflow_typical_noise_minus1cm_diff[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_h5l1_outflow_typical_noise_minus1cm_diff[5:300], col = colors_red[3])
lines(swmm_time[5:300], swmm_h5l1_inflow_typical_noise_plus5cm_diff[5:300], col = colors_blue[2])
lines(swmm_time[5:300], swmm_h5l1_outflow_typical_noise_plus5cm_diff[5:300], col = colors_red[2])
lines(swmm_time[5:300], swmm_h5l1_inflow_typical_noise_minus5cm_diff[5:300], col = colors_blue[1])
lines(swmm_time[5:300], swmm_h5l1_outflow_typical_noise_minus5cm_diff[5:300], col = colors_red[1])
grid()
#legend("topright", legend = c("Inflow Typical Noise +1cm Bias Difference", "Inflow Typical Noise -1cm Bias Difference", "Inflow Typical Noise +5cm Bias Difference", "Inflow Typical Noise -5cm Bias Difference", "Outflow Typical Noise +1cm Bias Difference", "Outflow Typical Noise -1cm Bias Difference", "Outflow Typical Noise +5cm Bias Difference", "Outflow Typical Noise -5cm Bias Difference"), col = c(colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.6)
```

Plot SWMM Results Differences
```{r}
# Plot showing noise differences
plot(swmm_time[1:300], swmm_inflow_typical_noise_diff[1:300], type = "l", col = colors_blue[3], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "SWMM Inflow/Outflow Noise Differences", ylim = c(-20,40))
lines(swmm_time[1:300], swmm_outflow_typical_noise_diff[1:300], col = colors_red[3], lty = 3)
lines(swmm_time[1:300], swmm_inflow_max_noise_diff[1:300], col = colors_blue[5])
lines(swmm_time[1:300], swmm_outflow_max_noise_diff[1:300], col = colors_red[5], lty = 3)
grid()
legend("topright", legend = c("Inflow Typical Noise Difference", "Inflow Max Noise Difference", "Outflow Typical Noise Difference", "Outflow Max Noise Difference"), col = c(colors_blue[3], colors_blue[5], colors_red[3], colors_red[5]), lty = c(1, 1, 1, 3, 3, 3), lwd = 2, cex = 0.7)


# Plot showing bias differences
plot(swmm_time[5:300], swmm_inflow_plus1cm_diff[5:300], type = "l", col = colors_blue[2], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "SWMM Inflow/Outflow Bias Differences", ylim = c(-20,40))
lines(swmm_time[5:300], swmm_outflow_plus1cm_diff[5:300], col = colors_red[2], lty = 3)
lines(swmm_time[5:300], swmm_inflow_minus1cm_diff[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_outflow_minus1cm_diff[5:300], col = colors_red[3], lty = 3)
lines(swmm_time[5:300], swmm_inflow_plus5cm_diff[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_outflow_plus5cm_diff[5:300], col = colors_red[4], lty = 3)
lines(swmm_time[5:300], swmm_inflow_minus5cm_diff[5:300], col = colors_blue[5])
lines(swmm_time[5:300], swmm_outflow_minus5cm_diff[5:300], col = colors_red[5], lty = 3)
grid()
legend("topright", legend = c("Inflow +1cm Bias Difference", "Inflow -1cm Bias Difference", "Inflow +5cm Bias Difference", "Inflow -5cm Bias Difference", "Outflow +1cm Bias Difference", "Outflow -1cm Bias Difference", "Outflow +5cm Bias Difference", "Outflow -5cm Bias Difference"), col = c(colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.7)


# Plots showing noise and bias differences
plot(swmm_time[5:300], swmm_inflow_typical_noise_plus1cm_diff[5:300], type = "l", col = colors_blue[2], xlab = "Time (hours)", ylab = "Flow Difference (cfs)", main = "SWMM Inflow/Outflow Noise and Bias Differences", ylim = c(-20,40))
lines(swmm_time[5:300], swmm_outflow_typical_noise_plus1cm_diff[5:300], col = colors_red[2], lty = 3)
lines(swmm_time[5:300], swmm_inflow_typical_noise_minus1cm_diff[5:300], col = colors_blue[3])
lines(swmm_time[5:300], swmm_outflow_typical_noise_minus1cm_diff[5:300], col = colors_red[3], lty = 3)
lines(swmm_time[5:300], swmm_inflow_typical_noise_plus5cm_diff[5:300], col = colors_blue[4])
lines(swmm_time[5:300], swmm_outflow_typical_noise_plus5cm_diff[5:300], col = colors_red[4], lty = 3)
lines(swmm_time[5:300], swmm_inflow_typical_noise_minus5cm_diff[5:300], col = colors_blue[5])
lines(swmm_time[5:300], swmm_outflow_typical_noise_minus5cm_diff[5:300], col = colors_red[5], lty = 3)
grid()
legend("topright", legend = c("Inflow Typical Noise +1cm Bias Difference", "Inflow Typical Noise -1cm Bias Difference", "Inflow Typical Noise +5cm Bias Difference", "Inflow Typical Noise -5cm Bias Difference", "Outflow Typical Noise +1cm Bias Difference", "Outflow Typical Noise -1cm Bias Difference", "Outflow Typical Noise +5cm Bias Difference", "Outflow Typical Noise -5cm Bias Difference"), col = c(colors_blue[2], colors_blue[3], colors_blue[4], colors_blue[5], colors_red[2], colors_red[3], colors_red[4], colors_red[5]), lty = c(1, 1, 1, 1, 1, 3, 3, 3, 3, 3), lwd = 2, cex = 0.6)

```

Plot SWMM Results Percent Differences
```{r}
# Plot showing noise percent differences
plot(swmm_time[15:300], swmm_inflow_typical_noise_percent_diff[15:300], type = "l", col = "red4", xlab = "Time (hours)", ylab = "Flow Difference (%)", main = "SWMM Inflow/Outflow Noise Percent Differences", ylim = c(min(swmm_inflow_max_noise_percent_diff[15:300]), max(swmm_inflow_max_noise_percent_diff[15:300])))
lines(swmm_time[15:300], swmm_outflow_typical_noise_percent_diff[15:300], col = "red4", lty = 3)
lines(swmm_time[15:300], swmm_inflow_max_noise_percent_diff[15:300], col = "lightpink")
lines(swmm_time[15:300], swmm_outflow_max_noise_percent_diff[15:300], col = "lightpink", lty = 3)
grid()

# Plot showing bias percent differences
plot(swmm_time[15:300], swmm_inflow_plus1cm_percent_diff[15:300], type = "l", col = "plum1", xlab = "Time (hours)", ylab = "Flow Difference (%)", main = "SWMM Inflow/Outflow Bias Percent Differences", ylim = c(-100,100))
lines(swmm_time[15:300], swmm_outflow_plus1cm_percent_diff[15:300], col = "plum1", lty = 3)
lines(swmm_time[15:300], swmm_inflow_minus1cm_percent_diff[15:300], col = "plum4")
lines(swmm_time[15:300], swmm_outflow_minus1cm_percent_diff[15:300], col = "plum4", lty = 3)
lines(swmm_time[15:300], swmm_inflow_plus5cm_percent_diff[15:300], col = "slateblue2")
lines(swmm_time[15:300], swmm_outflow_plus5cm_percent_diff[15:300], col = "slateblue2", lty = 3)
lines(swmm_time[15:300], swmm_inflow_minus5cm_percent_diff[15:300], col = "slateblue4")
lines(swmm_time[15:300], swmm_outflow_minus5cm_percent_diff[15:300], col = "slateblue4", lty = 3)
grid()

# Plots showing noise and bias percent differences
plot(swmm_time[15:300], swmm_inflow_typical_noise_plus1cm_percent_diff[15:300], type = "l", col = "yellow1", xlab = "Time (hours)", ylab = "Flow Difference (%)", main = "SWMM Inflow/Outflow Noise and Bias Percent Differences", ylim = c(-100,100))
lines(swmm_time[15:300], swmm_outflow_typical_noise_plus1cm_percent_diff[15:300], col = "yellow1", lty = 3)
lines(swmm_time[15:300], swmm_inflow_typical_noise_minus1cm_percent_diff[15:300], col = "gold1")
lines(swmm_time[15:300], swmm_outflow_typical_noise_minus1cm_percent_diff[15:300], col = "gold1", lty = 3)
lines(swmm_time[15:300], swmm_inflow_typical_noise_plus5cm_percent_diff[15:300], col = "tomato1")
lines(swmm_time[15:300], swmm_outflow_typical_noise_plus5cm_percent_diff[15:300], col = "tomato1", lty = 3)
lines(swmm_time[15:300], swmm_inflow_typical_noise_minus5cm_percent_diff[15:300], col = "brown")
lines(swmm_time[15:300], swmm_outflow_typical_noise_minus5cm_percent_diff[15:300], col = "brown", lty = 3)
grid()

```

Garner
```{r}
source("reverse_puls.R")

# make example reproducible
#set.seed(0)

# matrix of bias values
bias_values <- seq(-10, 10, by = 0.2)/(2.54*12)

# Use lapply to run the function for each multiplier value
garner_results_list <- lapply(bias_values, function(x) get_inflow_outflow_res(depth_gar[27256:27656], x, 0.01, 320, 145, 14/12, (2.75/25.4)/12, 0.595, (20*pi/180), 300))

# Combine the results into a data frame
garner_results_df <- do.call(cbind, garner_results_list)

# Convert to a data frame if needed
garner_results_df <- as.data.frame(garner_results_df)

# save results df as csv
write.csv(garner_results_df, file = "Test_Garner_Inflow_Outflow.csv")

# identify inflow columns
inflow_cols <- grepl("Inflow.cfs", colnames(garner_results_df))

# identify outflow columns
outflow_cols <- grepl("Outflow.cfs", colnames(garner_results_df))

# create data frame with only inflow columns
gar_inflow_df <- garner_results_df[, inflow_cols]

# create data frame with only outflow columns
gar_outflow_df <- garner_results_df[, outflow_cols]

write.csv(gar_inflow_df, file = "Garner_Inflow_Test.csv")
write.csv(gar_outflow_df, file = "Garner_Outflow_Test.csv")

# smoothed inflow/outflow with no bias
smoothed_results_gar <- get_inflow_outflow_res(smooth_depth_gar[27256:27656], 0, 0, 320, 145, 14/12, (2.75/25.4)/12, 0.595, (20*pi/180), 300)

```

DobA5
```{r}
# make example reproducible
set.seed(0)

# matrix of bias values
bias_values <- seq(-10, 10, by = 0.2)/(2.54*12)

# Use lapply to run the function for each multiplier value
doba5_results_list <- lapply(bias_values, function(x) get_inflow_outflow_res(depth_da5[8686:9086], x, 0.01, 313, 146, 15.5/12, (2.2/25.4)/12, 0.585, (30*pi)/180, 300))

# Combine the results into a data frame
doba5_results_df <- do.call(cbind, doba5_results_list)

# Convert to a data frame if needed
doba5_results_df <- as.data.frame(doba5_results_df)

# save results df as csv
write.csv(doba5_results_df, file = "Test_doba5_Inflow_Outflow.csv")

# identify inflow columns
inflow_cols <- grepl("Inflow.cfs", colnames(doba5_results_df))

# identify outflow columns
outflow_cols <- grepl("Outflow.cfs", colnames(doba5_results_df))

# create data frame with only inflow columns
da5_inflow_df <- doba5_results_df[, inflow_cols]

# create data frame with only outflow columns
da5_outflow_df <- doba5_results_df[, outflow_cols]

write.csv(da5_inflow_df, file = "doba5_Inflow_Test.csv")
write.csv(da5_outflow_df, file = "doba5_Outflow_Test.csv")

# smoothed inflow/outflow with no bias
smoothed_results_da5 <- get_inflow_outflow_res(smooth_depth_da5[8686:9086], 0, 0, 313, 146, 15.5/12, (2.2/25.4)/12, 0.585, (30*pi)/180, 300)

```

Midtown
```{r}
# make example reproducible
set.seed(0)

# matrix of bias values
bias_values <- seq(-5, 5, by = 0.1)/(2.54*12)

# Use lapply to run the function for each multiplier value
midtown_results_list <- lapply(bias_values, function(x) get_inflow_outflow_nonres(depth_mid[1289:1689], x, 0.01, 510, 143, 27.25/12, 10, 300))

# Combine the results into a data frame
midtown_results_df <- do.call(cbind, midtown_results_list)

# Convert to a data frame if needed
midtown_results_df <- as.data.frame(midtown_results_df)

# save results df as csv
write.csv(midtown_results_df, file = "Test_midtown_Inflow_Outflow.csv")

# identify inflow columns
inflow_cols <- grepl("Inflow.cfs", colnames(midtown_results_df))

# identify outflow columns
outflow_cols <- grepl("Outflow.cfs", colnames(midtown_results_df))

# create data frame with only inflow columns
mid_inflow_df <- midtown_results_df[, inflow_cols]

# create data frame with only outflow columns
mid_outflow_df <- midtown_results_df[, outflow_cols]

write.csv(mid_inflow_df, file = "midtown_Inflow_Test.csv")
write.csv(mid_outflow_df, file = "midtown_Outflow_Test.csv")

# smoothed inflow/outflow with no bias
smoothed_results_mid <- get_inflow_outflow_nonres(smooth_depth_mid[1289:1689], 0, 0, 510, 143, 27.25/12, 10, 300)

```

Baxter
```{r}
# make example reproducible
set.seed(0)

# matrix of bias values
bias_values <- seq(-5, 5, by = 0.1)/(2.54*12)

# Use lapply to run the function for each multiplier value
baxter_results_list <- lapply(bias_values, function(x) get_inflow_outflow_nonres(depth_bax[27203:27603], x, 0.01, 60, 100, 12/12, 2.25, 300))

# Combine the results into a data frame
baxter_results_df <- do.call(cbind, baxter_results_list)

# Convert to a data frame if needed
baxter_results_df <- as.data.frame(baxter_results_df)

# save results df as csv
write.csv(baxter_results_df, file = "Test_baxter_Inflow_Outflow.csv")

# identify inflow columns
inflow_cols <- grepl("Inflow.cfs", colnames(baxter_results_df))

# identify outflow columns
outflow_cols <- grepl("Outflow.cfs", colnames(baxter_results_df))

# create data frame with only inflow columns
bax_inflow_df <- baxter_results_df[, inflow_cols]

# create data frame with only outflow columns
bax_outflow_df <- baxter_results_df[, outflow_cols]

write.csv(bax_inflow_df, file = "baxter_Inflow_Test.csv")
write.csv(bax_outflow_df, file = "baxter_Outflow_Test.csv")

# smoothed inflow/outflow with no bias
smoothed_results_bax <- get_inflow_outflow_nonres(smooth_depth_bax[27203:27603], 0, 0, 60, 100, 12/12, 2.25, 300)

```

95% Confidence Interval Function
```{r}
# Function to calculate 95% confidence intervals for each row in a data frame
calculate_ci_loop <- function(df) {
  # Create a matrix to store the results
  conf_intervals <- matrix(NA, nrow = nrow(df), ncol = 2)
  
  # Loop through each row of the data frame
  for (i in 1:nrow(df)) {
    row <- df[i, ]
    
    # Remove NAs from the row to avoid errors in t.test()
    row <- na.omit(as.numeric(row))
    
    # Run t-test to get the confidence interval
    if (length(row) > 1) {  # t.test needs at least 2 observations
      t_test_result <- t.test(row, conf.level = 0.95)
      conf_intervals[i, ] <- t_test_result$conf.int
    }
  }
  
  # Convert the matrix to a data frame and add column names
  conf_intervals_df <- as.data.frame(conf_intervals)
  colnames(conf_intervals_df) <- c("Lower_CI", "Upper_CI")
  
  return(conf_intervals_df)
}

```

Calculate 95% CI for pond inflow/outflow
```{r}
# Garner
garner_ci_inflow <- calculate_ci_loop(gar_inflow_df)
garner_ci_outflow <- calculate_ci_loop(gar_outflow_df)
# DobA5
doba5_ci_inflow <- calculate_ci_loop(da5_inflow_df)
doba5_ci_outflow <- calculate_ci_loop(da5_outflow_df)
# Midtown
midtown_ci_inflow <- calculate_ci_loop(mid_inflow_df)
midtown_ci_outflow <- calculate_ci_loop(mid_outflow_df)
# Baxter
baxter_ci_inflow <- calculate_ci_loop(bax_inflow_df)
baxter_ci_outflow <- calculate_ci_loop(bax_outflow_df)
```

Plot results from 95% confidence interval: Garner
```{r}
# Right now using range of values instead of confidence interval
plot_df <- data.frame(x = datetime_gar[27258:27656], mean_value_inflow = smoothed_results_gar$Inflow.cfs[3:401], lower_bound_inflow = gar_inflow_df$Inflow.cfs.1[3:401], upper_bound_inflow = gar_inflow_df$Inflow.cfs.100[3:401], lower_ci_inflow = garner_ci_inflow$Lower_CI[3:401], upper_ci_inflow = garner_ci_inflow$Upper_CI[3:401], mean_value_outflow = smoothed_results_gar$Outflow.cfs[3:401], lower_bound_outflow = gar_outflow_df$Outflow.cfs.1[3:401], upper_bound_outflow = gar_outflow_df$Outflow.cfs.100[3:401], lower_ci_outflow = garner_ci_outflow$Lower_CI[3:401], upper_ci_outflow = garner_ci_outflow$Upper_CI[3:401]) 
  
# Create the plot
ggplot(plot_df, aes(x = x)) +
  geom_line(aes(y = mean_value_inflow), color = "blue", size = 0.5) +  # Line for the mean inflow
  geom_line(aes(y = mean_value_outflow), color = "red", size = 0.5) +  # Line for the mean outflow
  geom_ribbon(aes(ymin = lower_ci_inflow, ymax = upper_ci_inflow), fill = "blue", alpha = 0.2) +  # Shaded area inflow
  geom_ribbon(aes(ymin = lower_ci_outflow, ymax = upper_ci_outflow), fill = "red", alpha = 0.2) +  # Shaded area outflow
  labs(title = "",
       x = "DateTime",
       y = "Flow (cfs)") +
  theme_minimal() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 1),  # Border around plot panel
    panel.grid.major = element_line(colour = "darkgray", linetype = "dashed"),  # Dotted major grid lines
    panel.grid.minor = element_line(colour = "darkgray", linetype = "dashed"),   # Dotted minor grid lines
    axis.ticks = element_line(size = 0.5, color = "black"),  # Makes tick marks thicker and darker
    axis.ticks.length = unit(0.25, "cm"),
    axis.title.x = element_text(size = 16),  # Larger X-axis title
    axis.title.y = element_text(size = 16),  # Larger Y-axis title
    axis.text.x = element_text(size = 14),   # Larger X-axis tick labels
    axis.text.y = element_text(size = 14)    # Larger Y-axis tick labels
  )

ggsave("garner_95ci.png")
```

Plot results from 95% confidence interval: DobA5
```{r}
plot_df <- data.frame(x = datetime_da5[8688:9086], mean_value_inflow = smoothed_results_da5$Inflow.cfs[3:401], lower_bound_inflow = da5_inflow_df$Inflow.cfs.1[3:401], upper_bound_inflow = da5_inflow_df$Inflow.cfs.100[3:401], lower_ci_inflow = doba5_ci_inflow$Lower_CI[3:401], upper_ci_inflow = doba5_ci_inflow$Upper_CI[3:401], mean_value_outflow = smoothed_results_da5$Outflow.cfs[3:401], lower_bound_outflow = da5_outflow_df$Outflow.cfs.1[3:401], upper_bound_outflow = da5_outflow_df$Outflow.cfs.100[3:401], lower_ci_outflow = doba5_ci_outflow$Lower_CI[3:401], upper_ci_outflow = doba5_ci_outflow$Upper_CI[3:401]) 
  
# Create the plot
ggplot(plot_df, aes(x = x)) +
  geom_line(aes(y = mean_value_inflow), color = "blue", size = 0.5) +  # Line for the mean inflow
  geom_line(aes(y = mean_value_outflow), color = "red", size = 0.5) +  # Line for the mean outflow
  geom_ribbon(aes(ymin = lower_ci_inflow, ymax = upper_ci_inflow), fill = "blue", alpha = 0.2) +  # Shaded area inflow
  geom_ribbon(aes(ymin = lower_ci_outflow, ymax = upper_ci_outflow), fill = "red", alpha = 0.2) +  # Shaded area outflow
  labs(title = "Mean with 95% Confidence Interval",
       x = "DateTime",
       y = "Flow (cfs)") +
  theme_minimal()
```

Plot results from 95% confidence interval: Baxter
```{r}
plot_df <- data.frame(x = datetime_bax[27205:27603], mean_value_inflow = smoothed_results_bax$Inflow.cfs[3:401], lower_bound_inflow = bax_inflow_df$Inflow.cfs.1[3:401], upper_bound_inflow = bax_inflow_df$Inflow.cfs.100[3:401], lower_ci_inflow = baxter_ci_inflow$Lower_CI[3:401], upper_ci_inflow = baxter_ci_inflow$Upper_CI[3:401], mean_value_outflow = smoothed_results_bax$Outflow.cfs[3:401], lower_bound_outflow = bax_outflow_df$Outflow.cfs.1[3:401], upper_bound_outflow = bax_outflow_df$Outflow.cfs.100[3:401], lower_ci_outflow = baxter_ci_outflow$Lower_CI[3:401], upper_ci_outflow = baxter_ci_outflow$Upper_CI[3:401]) 
  
# Create the plot
ggplot(plot_df, aes(x = x)) +
  geom_line(aes(y = mean_value_inflow), color = "blue", size = 0.5) +  # Line for the mean inflow
  geom_line(aes(y = mean_value_outflow), color = "red", size = 0.5) +  # Line for the mean outflow
  geom_ribbon(aes(ymin = lower_ci_inflow, ymax = upper_ci_inflow), fill = "blue", alpha = 0.2) +  # Shaded area inflow
  geom_ribbon(aes(ymin = lower_ci_outflow, ymax = upper_ci_outflow), fill = "red", alpha = 0.2) +  # Shaded area outflow
  labs(title = "Mean with 95% Confidence Interval",
       x = "DateTime",
       y = "Flow (cfs)") +
  theme_minimal()
```

Plot results from 95% confidence interval: Midtown
```{r}
plot_df <- data.frame(x = datetime_mid[1291:1689], mean_value_inflow = smoothed_results_mid$Inflow.cfs[3:401], lower_bound_inflow = mid_inflow_df$Inflow.cfs.1[3:401], upper_bound_inflow = mid_inflow_df$Inflow.cfs.100[3:401], lower_ci_inflow = midtown_ci_inflow$Lower_CI[3:401], upper_ci_inflow = midtown_ci_inflow$Upper_CI[3:401], mean_value_outflow = smoothed_results_mid$Outflow.cfs[3:401], lower_bound_outflow = mid_outflow_df$Outflow.cfs.1[3:401], upper_bound_outflow = mid_outflow_df$Outflow.cfs.100[3:401], lower_ci_outflow = midtown_ci_outflow$Lower_CI[3:401], upper_ci_outflow = midtown_ci_outflow$Upper_CI[3:401]) 
  
# Create the plot
ggplot(plot_df, aes(x = x)) +
  geom_line(aes(y = mean_value_inflow), color = "blue", size = 0.5) +  # Line for the mean inflow
  geom_line(aes(y = mean_value_outflow), color = "red", size = 0.5) +  # Line for the mean outflow
  geom_ribbon(aes(ymin = lower_ci_inflow, ymax = upper_ci_inflow), fill = "blue", alpha = 0.2) +  # Shaded area inflow
  geom_ribbon(aes(ymin = lower_ci_outflow, ymax = upper_ci_outflow), fill = "red", alpha = 0.2) +  # Shaded area outflow
  labs(title = "",
       x = "DateTime",
       y = "Flow (cfs)") +
  theme_minimal() +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 1),  # Border around plot panel
    panel.grid.major = element_line(colour = "darkgray", linetype = "dashed"),  # Dotted major grid lines
    panel.grid.minor = element_line(colour = "darkgray", linetype = "dashed"),   # Dotted minor grid lines
    axis.ticks = element_line(size = 0.5, color = "black"),  # Makes tick marks thicker and darker
    axis.ticks.length = unit(0.25, "cm"),
    axis.title.x = element_text(size = 16),  # Larger X-axis title
    axis.title.y = element_text(size = 16),  # Larger Y-axis title
    axis.text.x = element_text(size = 14),   # Larger X-axis tick labels
    axis.text.y = element_text(size = 14)    # Larger Y-axis tick labels
  )

ggsave("midtown_95ci.png")
```

Plot Attenuation vs Error for Base Results Medium Storm
```{r}
typical_noise_base_lm <- lm(abs(atten_base_df$Typical.Noise.Error) ~ atten_base_df$Typical.Noise.Atten)
plus1cm_base_lm <- lm(abs(atten_base_df$Plus.1cm.Error) ~ atten_base_df$Plus.1cm.Atten)
minus1cm_base_lm <- lm(abs(atten_base_df$Minus.1cm.Error) ~ atten_base_df$Minus.1cm.Atten)
plus5cm_base_lm <- lm(abs(atten_base_df$Plus.5cm.Error) ~ atten_base_df$Plus.5cm.Atten)
minus5cm_base_lm <- lm(abs(atten_base_df$Minus.5cm.Error) ~ atten_base_df$Minus.5cm.Atten)

typical_noise_base_df <- data.frame(atten_base_df$Typical.Noise.Atten, atten_base_df$Typical.Noise.Error)
typical_noise_base_sorted <- typical_noise_base_df[order(typical_noise_base_df$atten_base_df.Typical.Noise.Atten),]
plus1cm_base_df <- data.frame(atten_base_df$Plus.1cm.Atten, atten_base_df$Plus.1cm.Error)
plus1cm_base_sorted <- plus1cm_base_df[order(plus1cm_base_df$atten_base_df.Plus.1cm.Atten),]
minus1cm_base_df <- data.frame(atten_base_df$Minus.1cm.Atten, atten_base_df$Minus.1cm.Error)
minus1cm_base_sorted <- minus1cm_base_df[order(minus1cm_base_df$atten_base_df.Minus.1cm.Atten),]
plus5cm_base_df <- data.frame(atten_base_df$Plus.5cm.Atten, atten_base_df$Plus.5cm.Error)
plus5cm_base_sorted <- plus5cm_base_df[order(plus5cm_base_df$atten_base_df.Plus.5cm.Atten),]
minus5cm_base_df <- data.frame(atten_base_df$Minus.5cm.Atten, atten_base_df$Minus.5cm.Error)
minus5cm_base_sorted <- minus5cm_base_df[order(minus5cm_base_df$atten_base_df.Minus.5cm.Atten),]

shape_map <- c("V-notch" = 25, #inverted triange
               "Rectangular" = 15, #rectangle
               "Trapezoidal" = 18, #diamond
               "Culvert" =16) #circle

# Adjust margins: increase the right margin (fourth value) to make space for the legend
par(mar = c(5, 4, 4, 10) + 0.1)  # c(bottom, left, top, right)

plot(atten_base_df$Typical.Noise.Atten, abs(atten_base_df$Typical.Noise.Error), pch = shape_map[atten_base_df$Outlet.Type], col=colors_red[5], bg=colors_red[5], xlab="Attenuation (% Reduction in Inflow)", ylab="Error (% Difference from Base)", ylim=c(0, max(abs(atten_base_df$Minus.5cm.Error))))
abline(typical_noise_base_lm, col=colors_red[5])
#lines(typical_noise_base_sorted$atten_base_df.Typical.Noise.Atten, abs(typical_noise_base_sorted$atten_base_df.Typical.Noise.Error), lty=3, col=colors_red[5])
points(atten_base_df$Plus.1cm.Atten, abs(atten_base_df$Plus.1cm.Error), pch = shape_map[atten_base_df$Outlet.Type], col=colors_blue[4], bg=colors_blue[4])
abline(plus1cm_base_lm, col=colors_blue[4])
#lines(plus1cm_base_sorted$atten_base_df.Plus.1cm.Atten, abs(plus1cm_base_sorted$atten_base_df.Plus.1cm.Error), lty=3, col=colors_blue[4])
points(atten_base_df$Minus.1cm.Atten, abs(atten_base_df$Minus.1cm.Error), pch = shape_map[atten_base_df$Outlet.Type], col=colors_blue[3], bg=colors_blue[3])
abline(minus1cm_base_lm, col=colors_blue[3])
#lines(minus1cm_base_sorted$atten_base_df.Minus.1cm.Atten, abs(minus1cm_base_sorted$atten_base_df.Minus.1cm.Error), lty=3, col=colors_blue[3])
points(atten_base_df$Plus.5cm.Atten, abs(atten_base_df$Plus.5cm.Error), pch = shape_map[atten_base_df$Outlet.Type], col=colors_blue[5], bg=colors_blue[5])
abline(plus5cm_base_lm, col=colors_blue[5])
#lines(plus5cm_base_sorted$atten_base_df.Plus.5cm.Atten, abs(plus5cm_base_sorted$atten_base_df.Plus.5cm.Error), lty=3, col=colors_blue[5])
points(atten_base_df$Minus.5cm.Atten, abs(atten_base_df$Minus.5cm.Error), pch = shape_map[atten_base_df$Outlet.Type], col=colors_blue[2], bg=colors_blue[2])
abline(minus5cm_base_lm, col=colors_blue[2])
#lines(minus5cm_base_sorted$atten_base_df.Minus.5cm.Atten, abs(minus5cm_base_sorted$atten_base_df.Minus.5cm.Error), lty=3, col=colors_blue[2])
grid()
legend("topright", inset = c(-0.45,0.1), legend = c("Typical Noise", "Plus 5cm", "Plus 1cm", "Minus 1cm", "Minus 5cm", "V-notch Weir", "Rectangular Weir", "Trapezoidal Weir", "Culvert"), col = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pt.bg = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pch = c(NA,NA,NA,NA,NA,25,15,18,16), lty = c(1,1,1,1,1,NA,NA,NA,NA), lwd = c(2,2,2,2,2,NA,NA,NA,NA), xpd=TRUE)
```

Plot Attenuation vs Error for Smoothed Results Medium Storm
```{r}
typical_noise_smooth_lm <- lm(abs(atten_smooth_df$Typical.Noise.Error) ~ atten_smooth_df$Typical.Noise.Atten)
plus1cm_smooth_lm <- lm(abs(atten_smooth_df$Plus.1cm.Error) ~ atten_smooth_df$Plus.1cm.Atten)
minus1cm_smooth_lm <- lm(abs(atten_smooth_df$Minus.1cm.Error) ~ atten_smooth_df$Minus.1cm.Atten)
plus5cm_smooth_lm <- lm(abs(atten_smooth_df$Plus.5cm.Error[2:19]) ~ atten_smooth_df$Plus.5cm.Atten[2:19])
minus5cm_smooth_lm <- lm(abs(atten_smooth_df$Minus.5cm.Error[2:19]) ~ atten_smooth_df$Minus.5cm.Atten[2:19])

typical_noise_smooth_df <- data.frame(atten_smooth_df$Typical.Noise.Atten, atten_smooth_df$Typical.Noise.Error)
typical_noise_smooth_sorted <- typical_noise_smooth_df[order(typical_noise_smooth_df$atten_smooth_df.Typical.Noise.Atten),]
plus1cm_smooth_df <- data.frame(atten_smooth_df$Plus.1cm.Atten, atten_smooth_df$Plus.1cm.Error)
plus1cm_smooth_sorted <- plus1cm_smooth_df[order(plus1cm_smooth_df$atten_smooth_df.Plus.1cm.Atten),]
minus1cm_smooth_df <- data.frame(atten_smooth_df$Minus.1cm.Atten, atten_smooth_df$Minus.1cm.Error)
minus1cm_smooth_sorted <- minus1cm_smooth_df[order(minus1cm_smooth_df$atten_smooth_df.Minus.1cm.Atten),]
plus5cm_smooth_df <- data.frame(atten_smooth_df$Plus.5cm.Atten[2:19], atten_smooth_df$Plus.5cm.Error[2:19])
plus5cm_smooth_sorted <- plus5cm_smooth_df[order(plus5cm_smooth_df$atten_smooth_df.Plus.5cm.Atten),]
minus5cm_smooth_df <- data.frame(atten_smooth_df$Minus.5cm.Atten[2:19], atten_smooth_df$Minus.5cm.Error[2:19])
minus5cm_smooth_sorted <- minus5cm_smooth_df[order(minus5cm_smooth_df$atten_smooth_df.Minus.5cm.Atten),]

shape_map <- c("V-notch" = 25, #inverted triange
               "Rectangular" = 15, #rectangle
               "Trapezoidal" = 18, #diamond
               "Culvert" =16) #circle

# Adjust margins: increase the right margin (fourth value) to make space for the legend
par(mar = c(5, 4, 4, 10) + 0.1)  # c(bottom, left, top, right)

plot(atten_smooth_df$Typical.Noise.Atten, abs(atten_smooth_df$Typical.Noise.Error), pch = shape_map[atten_smooth_df$Outlet.Type], col=colors_red[5], bg=colors_red[5], xlab="Attenuation (% Reduction in Inflow)", ylab="Error (% Difference from Smoothed Base)", ylim=c(0, max(abs(atten_smooth_df$Minus.5cm.Error[2:19]))))
abline(typical_noise_smooth_lm, col=colors_red[5])
#lines(typical_noise_smooth_sorted$atten_smooth_df.Typical.Noise.Atten, abs(typical_noise_smooth_sorted$atten_smooth_df.Typical.Noise.Error), lty=3, col=colors_red[5])
points(atten_smooth_df$Plus.1cm.Atten, abs(atten_smooth_df$Plus.1cm.Error), pch = shape_map[atten_smooth_df$Outlet.Type], col=colors_blue[4], bg=colors_blue[4])
abline(plus1cm_smooth_lm, col=colors_blue[4])
#lines(plus1cm_smooth_sorted$atten_smooth_df.Plus.1cm.Atten, abs(plus1cm_smooth_sorted$atten_smooth_df.Plus.1cm.Error), lty=3, col=colors_blue[4])
points(atten_smooth_df$Minus.1cm.Atten, abs(atten_smooth_df$Minus.1cm.Error), pch = shape_map[atten_smooth_df$Outlet.Type], col=colors_blue[3], bg=colors_blue[3])
abline(minus1cm_smooth_lm, col=colors_blue[3])
#lines(minus1cm_smooth_sorted$atten_smooth_df.Minus.1cm.Atten, abs(minus1cm_smooth_sorted$atten_smooth_df.Minus.1cm.Error), lty=3, col=colors_blue[3])
points(atten_smooth_df$Plus.5cm.Atten[2:19], abs(atten_smooth_df$Plus.5cm.Error[2:19]), pch = shape_map[atten_smooth_df$Outlet.Type], col=colors_blue[5], bg=colors_blue[5])
abline(plus5cm_smooth_lm, col=colors_blue[5])
#lines(plus5cm_smooth_sorted$atten_smooth_df.Plus.5cm.Atten, abs(plus5cm_smooth_sorted$atten_smooth_df.Plus.5cm.Error), lty=3, col=colors_blue[5])
points(atten_smooth_df$Minus.5cm.Atten[2:19], abs(atten_smooth_df$Minus.5cm.Error[2:19]), pch = shape_map[atten_smooth_df$Outlet.Type], col=colors_blue[2], bg=colors_blue[2])
abline(minus5cm_smooth_lm, col=colors_blue[2])
#lines(minus5cm_smooth_sorted$atten_smooth_df.Minus.5cm.Atten, abs(minus5cm_smooth_sorted$atten_smooth_df.Minus.5cm.Error), lty=3, col=colors_blue[2])
grid()
legend("topright", inset = c(-0.45,0.1), legend = c("Typical Noise", "Plus 5cm", "Plus 1cm", "Minus 1cm", "Minus 5cm", "V-notch Weir", "Rectangular Weir", "Trapezoidal Weir", "Culvert"), col = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pt.bg = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pch = c(NA,NA,NA,NA,NA,25,15,18,16), lty = c(1,1,1,1,1,NA,NA,NA,NA), lwd = c(2,2,2,2,2,NA,NA,NA,NA), xpd=TRUE)
```

Plot Attenuation vs Error for Base Results Large Storm
```{r}
typical_noise_base_large_lm <- lm(abs(atten_base_large_df$Typical.Noise.Error) ~ atten_base_large_df$Typical.Noise.Atten)
plus1cm_base_large_lm <- lm(abs(atten_base_large_df$Plus.1cm.Error) ~ atten_base_large_df$Plus.1cm.Atten)
minus1cm_base_large_lm <- lm(abs(atten_base_large_df$Minus.1cm.Error) ~ atten_base_large_df$Minus.1cm.Atten)
plus5cm_base_large_lm <- lm(abs(atten_base_large_df$Plus.5cm.Error) ~ atten_base_large_df$Plus.5cm.Atten)
minus5cm_base_large_lm <- lm(abs(atten_base_large_df$Minus.5cm.Error) ~ atten_base_large_df$Minus.5cm.Atten)

typical_noise_base_large_df <- data.frame(atten_base_large_df$Typical.Noise.Atten, atten_base_large_df$Typical.Noise.Error)
typical_noise_base_large_sorted <- typical_noise_base_large_df[order(typical_noise_base_large_df$atten_base_large_df.Typical.Noise.Atten),]
plus1cm_base_large_df <- data.frame(atten_base_large_df$Plus.1cm.Atten, atten_base_large_df$Plus.1cm.Error)
plus1cm_base_large_sorted <- plus1cm_base_large_df[order(plus1cm_base_large_df$atten_base_large_df.Plus.1cm.Atten),]
minus1cm_base_large_df <- data.frame(atten_base_large_df$Minus.1cm.Atten, atten_base_large_df$Minus.1cm.Error)
minus1cm_base_large_sorted <- minus1cm_base_large_df[order(minus1cm_base_large_df$atten_base_large_df.Minus.1cm.Atten),]
plus5cm_base_large_df <- data.frame(atten_base_large_df$Plus.5cm.Atten, atten_base_large_df$Plus.5cm.Error)
plus5cm_base_large_sorted <- plus5cm_base_large_df[order(plus5cm_base_large_df$atten_base_large_df.Plus.5cm.Atten),]
minus5cm_base_large_df <- data.frame(atten_base_large_df$Minus.5cm.Atten, atten_base_large_df$Minus.5cm.Error)
minus5cm_base_large_sorted <- minus5cm_base_large_df[order(minus5cm_base_large_df$atten_base_large_df.Minus.5cm.Atten),]

shape_map <- c("V-notch" = 25, #inverted triange
               "Rectangular" = 15, #rectangle
               "Trapezoidal" = 18, #diamond
               "Culvert" =16) #circle

# Adjust margins: increase the right margin (fourth value) to make space for the legend
par(mar = c(5, 4, 4, 10) + 0.1)  # c(bottom, left, top, right)

plot(atten_base_large_df$Typical.Noise.Atten, abs(atten_base_large_df$Typical.Noise.Error), pch = shape_map[atten_base_large_df$Outlet.Type], col=colors_red[5], bg=colors_red[5], xlab="Attenuation (% Reduction in Inflow)", ylab="Error (% Difference from Base)", ylim=c(0, max(abs(atten_base_large_df$Minus.5cm.Error))))
abline(typical_noise_base_large_lm, col=colors_red[5])
#lines(typical_noise_base_large_sorted$atten_base_large_df.Typical.Noise.Atten, abs(typical_noise_base_large_sorted$atten_base_large_df.Typical.Noise.Error), lty=3, col=colors_red[5])
points(atten_base_large_df$Plus.1cm.Atten, abs(atten_base_large_df$Plus.1cm.Error), pch = shape_map[atten_base_large_df$Outlet.Type], col=colors_blue[4], bg=colors_blue[4])
abline(plus1cm_base_large_lm, col=colors_blue[4])
#lines(plus1cm_base_large_sorted$atten_base_large_df.Plus.1cm.Atten, abs(plus1cm_base_large_sorted$atten_base_large_df.Plus.1cm.Error), lty=3, col=colors_blue[4])
points(atten_base_large_df$Minus.1cm.Atten, abs(atten_base_large_df$Minus.1cm.Error), pch = shape_map[atten_base_large_df$Outlet.Type], col=colors_blue[3], bg=colors_blue[3])
abline(minus1cm_base_large_lm, col=colors_blue[3])
#lines(minus1cm_base_large_sorted$atten_base_large_df.Minus.1cm.Atten, abs(minus1cm_base_large_sorted$atten_base_large_df.Minus.1cm.Error), lty=3, col=colors_blue[3])
points(atten_base_large_df$Plus.5cm.Atten, abs(atten_base_large_df$Plus.5cm.Error), pch = shape_map[atten_base_large_df$Outlet.Type], col=colors_blue[5], bg=colors_blue[5])
abline(plus5cm_base_large_lm, col=colors_blue[5])
#lines(plus5cm_base_large_sorted$atten_base_large_df.Plus.5cm.Atten, abs(plus5cm_base_large_sorted$atten_base_large_df.Plus.5cm.Error), lty=3, col=colors_blue[5])
points(atten_base_large_df$Minus.5cm.Atten, abs(atten_base_large_df$Minus.5cm.Error), pch = shape_map[atten_base_large_df$Outlet.Type], col=colors_blue[2], bg=colors_blue[2])
abline(minus5cm_base_large_lm, col=colors_blue[2])
#lines(minus5cm_base_large_sorted$atten_base_large_df.Minus.5cm.Atten, abs(minus5cm_base_large_sorted$atten_base_large_df.Minus.5cm.Error), lty=3, col=colors_blue[2])
grid()
legend("topright", inset = c(-0.45,0.1), legend = c("Typical Noise", "Plus 5cm", "Plus 1cm", "Minus 1cm", "Minus 5cm", "V-notch Weir", "Rectangular Weir", "Trapezoidal Weir", "Culvert"), col = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pt.bg = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pch = c(NA,NA,NA,NA,NA,25,15,18,16), lty = c(1,1,1,1,1,NA,NA,NA,NA), lwd = c(2,2,2,2,2,NA,NA,NA,NA), xpd=TRUE)
```

Plot Attenuation vs Error for Smoothed Results Large Storm
```{r}
typical_noise_smooth_large_lm <- lm(abs(atten_smooth_large_df$Typical.Noise.Error) ~ atten_smooth_large_df$Typical.Noise.Atten)
plus1cm_smooth_large_lm <- lm(abs(atten_smooth_large_df$Plus.1cm.Error) ~ atten_smooth_large_df$Plus.1cm.Atten)
minus1cm_smooth_large_lm <- lm(abs(atten_smooth_large_df$Minus.1cm.Error) ~ atten_smooth_large_df$Minus.1cm.Atten)
plus5cm_smooth_large_lm <- lm(abs(atten_smooth_large_df$Plus.5cm.Error[2:19]) ~ atten_smooth_large_df$Plus.5cm.Atten[2:19])
minus5cm_smooth_large_lm <- lm(abs(atten_smooth_large_df$Minus.5cm.Error[2:19]) ~ atten_smooth_large_df$Minus.5cm.Atten[2:19])

typical_noise_smooth_large_df <- data.frame(atten_smooth_large_df$Typical.Noise.Atten, atten_smooth_large_df$Typical.Noise.Error)
typical_noise_smooth_large_sorted <- typical_noise_smooth_large_df[order(typical_noise_smooth_large_df$atten_smooth_large_df.Typical.Noise.Atten),]
plus1cm_smooth_large_df <- data.frame(atten_smooth_large_df$Plus.1cm.Atten, atten_smooth_large_df$Plus.1cm.Error)
plus1cm_smooth_large_sorted <- plus1cm_smooth_large_df[order(plus1cm_smooth_large_df$atten_smooth_large_df.Plus.1cm.Atten),]
minus1cm_smooth_large_df <- data.frame(atten_smooth_large_df$Minus.1cm.Atten, atten_smooth_large_df$Minus.1cm.Error)
minus1cm_smooth_large_sorted <- minus1cm_smooth_large_df[order(minus1cm_smooth_large_df$atten_smooth_large_df.Minus.1cm.Atten),]
plus5cm_smooth_large_df <- data.frame(atten_smooth_large_df$Plus.5cm.Atten[2:19], atten_smooth_large_df$Plus.5cm.Error[2:19])
plus5cm_smooth_large_sorted <- plus5cm_smooth_large_df[order(plus5cm_smooth_large_df$atten_smooth_large_df.Plus.5cm.Atten),]
minus5cm_smooth_large_df <- data.frame(atten_smooth_large_df$Minus.5cm.Atten[2:19], atten_smooth_large_df$Minus.5cm.Error[2:19])
minus5cm_smooth_large_sorted <- minus5cm_smooth_large_df[order(minus5cm_smooth_large_df$atten_smooth_large_df.Minus.5cm.Atten),]

shape_map <- c("V-notch" = 25, #inverted triange
               "Rectangular" = 15, #rectangle
               "Trapezoidal" = 18, #diamond
               "Culvert" =16) #circle

# Adjust margins: increase the right margin (fourth value) to make space for the legend
par(mar = c(5, 4, 4, 10) + 0.1)  # c(bottom, left, top, right)

plot(atten_smooth_large_df$Typical.Noise.Atten, abs(atten_smooth_large_df$Typical.Noise.Error), pch = shape_map[atten_smooth_large_df$Outlet.Type], col=colors_red[5], bg=colors_red[5], xlab="Attenuation (% Reduction in Inflow)", ylab="Error (% Difference from Smoothed Base)", ylim=c(0, max(abs(atten_smooth_large_df$Minus.5cm.Error))))
abline(typical_noise_smooth_large_lm, col=colors_red[5])
#lines(typical_noise_smooth_large_sorted$atten_smooth_large_df.Typical.Noise.Atten, abs(typical_noise_smooth_large_sorted$atten_smooth_large_df.Typical.Noise.Error), lty=3, col=colors_red[5])
points(atten_smooth_large_df$Plus.1cm.Atten, abs(atten_smooth_large_df$Plus.1cm.Error), pch = shape_map[atten_smooth_large_df$Outlet.Type], col=colors_blue[4], bg=colors_blue[4])
abline(plus1cm_smooth_large_lm, col=colors_blue[4])
#lines(plus1cm_smooth_large_sorted$atten_smooth_large_df.Plus.1cm.Atten, abs(plus1cm_smooth_large_sorted$atten_smooth_large_df.Plus.1cm.Error), lty=3, col=colors_blue[4])
points(atten_smooth_large_df$Minus.1cm.Atten, abs(atten_smooth_large_df$Minus.1cm.Error), pch = shape_map[atten_smooth_large_df$Outlet.Type], col=colors_blue[3], bg=colors_blue[3])
abline(minus1cm_smooth_large_lm, col=colors_blue[3])
#lines(minus1cm_smooth_large_sorted$atten_smooth_large_df.Minus.1cm.Atten, abs(minus1cm_smooth_large_sorted$atten_smooth_large_df.Minus.1cm.Error), lty=3, col=colors_blue[3])
points(atten_smooth_large_df$Plus.5cm.Atten[2:19], abs(atten_smooth_large_df$Plus.5cm.Error[2:19]), pch = shape_map[atten_smooth_large_df$Outlet.Type], col=colors_blue[5], bg=colors_blue[5])
abline(plus5cm_smooth_large_lm, col=colors_blue[5])
#lines(plus5cm_smooth_large_sorted$atten_smooth_large_df.Plus.5cm.Atten, abs(plus5cm_smooth_large_sorted$atten_smooth_large_df.Plus.5cm.Error), lty=3, col=colors_blue[5])
points(atten_smooth_large_df$Minus.5cm.Atten[2:19], abs(atten_smooth_large_df$Minus.5cm.Error[2:19]), pch = shape_map[atten_smooth_large_df$Outlet.Type], col=colors_blue[2], bg=colors_blue[2])
abline(minus5cm_smooth_large_lm, col=colors_blue[2])
#lines(minus5cm_smooth_large_sorted$atten_smooth_large_df.Minus.5cm.Atten, abs(minus5cm_smooth_large_sorted$atten_smooth_large_df.Minus.5cm.Error), lty=3, col=colors_blue[2])
grid()
legend("topright", inset = c(-0.45,0.1), legend = c("Typical Noise", "Plus 5cm", "Plus 1cm", "Minus 1cm", "Minus 5cm", "V-notch Weir", "Rectangular Weir", "Trapezoidal Weir", "Culvert"), col = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pt.bg = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pch = c(NA,NA,NA,NA,NA,25,15,18,16), lty = c(1,1,1,1,1,NA,NA,NA,NA), lwd = c(2,2,2,2,2,NA,NA,NA,NA), xpd=TRUE)
```

Plot Attenuation vs Error for Base Results Small Storm
```{r}
typical_noise_base_small_lm <- lm(abs(atten_base_small_df$Typical.Noise.Error) ~ atten_base_small_df$Typical.Noise.Atten)
plus1cm_base_small_lm <- lm(abs(atten_base_small_df$Plus.1cm.Error) ~ atten_base_small_df$Plus.1cm.Atten)
minus1cm_base_small_lm <- lm(abs(atten_base_small_df$Minus.1cm.Error) ~ atten_base_small_df$Minus.1cm.Atten)
plus5cm_base_small_lm <- lm(abs(atten_base_small_df$Plus.5cm.Error) ~ atten_base_small_df$Plus.5cm.Atten)
minus5cm_base_small_lm <- lm(abs(atten_base_small_df$Minus.5cm.Error) ~ atten_base_small_df$Minus.5cm.Atten)

typical_noise_base_small_df <- data.frame(atten_base_small_df$Typical.Noise.Atten, atten_base_small_df$Typical.Noise.Error)
typical_noise_base_small_sorted <- typical_noise_base_small_df[order(typical_noise_base_small_df$atten_base_small_df.Typical.Noise.Atten),]
plus1cm_base_small_df <- data.frame(atten_base_small_df$Plus.1cm.Atten, atten_base_small_df$Plus.1cm.Error)
plus1cm_base_small_sorted <- plus1cm_base_small_df[order(plus1cm_base_small_df$atten_base_small_df.Plus.1cm.Atten),]
minus1cm_base_small_df <- data.frame(atten_base_small_df$Minus.1cm.Atten, atten_base_small_df$Minus.1cm.Error)
minus1cm_base_small_sorted <- minus1cm_base_small_df[order(minus1cm_base_small_df$atten_base_small_df.Minus.1cm.Atten),]
plus5cm_base_small_df <- data.frame(atten_base_small_df$Plus.5cm.Atten, atten_base_small_df$Plus.5cm.Error)
plus5cm_base_small_sorted <- plus5cm_base_small_df[order(plus5cm_base_small_df$atten_base_small_df.Plus.5cm.Atten),]
minus5cm_base_small_df <- data.frame(atten_base_small_df$Minus.5cm.Atten, atten_base_small_df$Minus.5cm.Error)
minus5cm_base_small_sorted <- minus5cm_base_small_df[order(minus5cm_base_small_df$atten_base_small_df.Minus.5cm.Atten),]

shape_map <- c("V-notch" = 25, #inverted triange
               "Rectangular" = 15, #rectangle
               "Trapezoidal" = 18, #diamond
               "Culvert" =16) #circle

# Adjust margins: increase the right margin (fourth value) to make space for the legend
par(mar = c(5, 4, 4, 10) + 0.1)  # c(bottom, left, top, right)

plot(atten_base_small_df$Typical.Noise.Atten, abs(atten_base_small_df$Typical.Noise.Error), pch = shape_map[atten_base_small_df$Outlet.Type], col=colors_red[5], bg=colors_red[5], xlab="Attenuation (% Reduction in Inflow)", ylab="Error (% Difference from Base)", ylim=c(0, max(abs(atten_base_small_df$Minus.5cm.Error))))
abline(typical_noise_base_small_lm, col=colors_red[5])
#lines(typical_noise_base_small_sorted$atten_base_small_df.Typical.Noise.Atten, abs(typical_noise_base_small_sorted$atten_base_small_df.Typical.Noise.Error), lty=3, col=colors_red[5])
points(atten_base_small_df$Plus.1cm.Atten, abs(atten_base_small_df$Plus.1cm.Error), pch = shape_map[atten_base_small_df$Outlet.Type], col=colors_blue[4], bg=colors_blue[4])
abline(plus1cm_base_small_lm, col=colors_blue[4])
#lines(plus1cm_base_small_sorted$atten_base_small_df.Plus.1cm.Atten, abs(plus1cm_base_small_sorted$atten_base_small_df.Plus.1cm.Error), lty=3, col=colors_blue[4])
points(atten_base_small_df$Minus.1cm.Atten, abs(atten_base_small_df$Minus.1cm.Error), pch = shape_map[atten_base_small_df$Outlet.Type], col=colors_blue[3], bg=colors_blue[3])
abline(minus1cm_base_small_lm, col=colors_blue[3])
#lines(minus1cm_base_small_sorted$atten_base_small_df.Minus.1cm.Atten, abs(minus1cm_base_small_sorted$atten_base_small_df.Minus.1cm.Error), lty=3, col=colors_blue[3])
points(atten_base_small_df$Plus.5cm.Atten, abs(atten_base_small_df$Plus.5cm.Error), pch = shape_map[atten_base_small_df$Outlet.Type], col=colors_blue[5], bg=colors_blue[5])
abline(plus5cm_base_small_lm, col=colors_blue[5])
#lines(plus5cm_base_small_sorted$atten_base_small_df.Plus.5cm.Atten, abs(plus5cm_base_small_sorted$atten_base_small_df.Plus.5cm.Error), lty=3, col=colors_blue[5])
points(atten_base_small_df$Minus.5cm.Atten, abs(atten_base_small_df$Minus.5cm.Error), pch = shape_map[atten_base_small_df$Outlet.Type], col=colors_blue[2], bg=colors_blue[2])
abline(minus5cm_base_small_lm, col=colors_blue[2])
#lines(minus5cm_base_small_sorted$atten_base_small_df.Minus.5cm.Atten, abs(minus5cm_base_small_sorted$atten_base_small_df.Minus.5cm.Error), lty=3, col=colors_blue[2])
grid()
legend("topright", inset = c(-0.45,0.1), legend = c("Typical Noise", "Plus 5cm", "Plus 1cm", "Minus 1cm", "Minus 5cm", "V-notch Weir", "Rectangular Weir", "Trapezoidal Weir", "Culvert"), col = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pt.bg = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pch = c(NA,NA,NA,NA,NA,25,15,18,16), lty = c(1,1,1,1,1,NA,NA,NA,NA), lwd = c(2,2,2,2,2,NA,NA,NA,NA), xpd=TRUE)
```

Plot Attenuation vs Error for Smoothed Results Small Storm
```{r}
typical_noise_smooth_small_lm <- lm(abs(atten_smooth_small_df$Typical.Noise.Error) ~ atten_smooth_small_df$Typical.Noise.Atten)
plus1cm_smooth_small_lm <- lm(abs(atten_smooth_small_df$Plus.1cm.Error) ~ atten_smooth_small_df$Plus.1cm.Atten)
minus1cm_smooth_small_lm <- lm(abs(atten_smooth_small_df$Minus.1cm.Error) ~ atten_smooth_small_df$Minus.1cm.Atten)
plus5cm_smooth_small_lm <- lm(abs(atten_smooth_small_df$Plus.5cm.Error[2:19]) ~ atten_smooth_small_df$Plus.5cm.Atten[2:19])
minus5cm_smooth_small_lm <- lm(abs(atten_smooth_small_df$Minus.5cm.Error[2:19]) ~ atten_smooth_small_df$Minus.5cm.Atten[2:19])

typical_noise_smooth_small_df <- data.frame(atten_smooth_small_df$Typical.Noise.Atten, atten_smooth_small_df$Typical.Noise.Error)
typical_noise_smooth_small_sorted <- typical_noise_smooth_small_df[order(typical_noise_smooth_small_df$atten_smooth_small_df.Typical.Noise.Atten),]
plus1cm_smooth_small_df <- data.frame(atten_smooth_small_df$Plus.1cm.Atten, atten_smooth_small_df$Plus.1cm.Error)
plus1cm_smooth_small_sorted <- plus1cm_smooth_small_df[order(plus1cm_smooth_small_df$atten_smooth_small_df.Plus.1cm.Atten),]
minus1cm_smooth_small_df <- data.frame(atten_smooth_small_df$Minus.1cm.Atten, atten_smooth_small_df$Minus.1cm.Error)
minus1cm_smooth_small_sorted <- minus1cm_smooth_small_df[order(minus1cm_smooth_small_df$atten_smooth_small_df.Minus.1cm.Atten),]
plus5cm_smooth_small_df <- data.frame(atten_smooth_small_df$Plus.5cm.Atten[2:19], atten_smooth_small_df$Plus.5cm.Error[2:19])
plus5cm_smooth_small_sorted <- plus5cm_smooth_small_df[order(plus5cm_smooth_small_df$atten_smooth_small_df.Plus.5cm.Atten),]
minus5cm_smooth_small_df <- data.frame(atten_smooth_small_df$Minus.5cm.Atten[2:19], atten_smooth_small_df$Minus.5cm.Error[2:19])
minus5cm_smooth_small_sorted <- minus5cm_smooth_small_df[order(minus5cm_smooth_small_df$atten_smooth_small_df.Minus.5cm.Atten),]

shape_map <- c("V-notch" = 25, #inverted triange
               "Rectangular" = 15, #rectangle
               "Trapezoidal" = 18, #diamond
               "Culvert" =16) #circle

# Adjust margins: increase the right margin (fourth value) to make space for the legend
par(mar = c(5, 4, 4, 10) + 0.1)  # c(bottom, left, top, right)

plot(atten_smooth_small_df$Typical.Noise.Atten, abs(atten_smooth_small_df$Typical.Noise.Error), pch = shape_map[atten_smooth_small_df$Outlet.Type], col=colors_red[5], bg=colors_red[5], xlab="Attenuation (% Reduction in Inflow)", ylab="Error (% Difference from Smoothed Base)", ylim=c(0, max(abs(atten_smooth_small_df$Minus.5cm.Error))))
abline(typical_noise_smooth_small_lm, col=colors_red[5])
#lines(typical_noise_smooth_small_sorted$atten_smooth_small_df.Typical.Noise.Atten, abs(typical_noise_smooth_small_sorted$atten_smooth_small_df.Typical.Noise.Error), lty=3, col=colors_red[5])
points(atten_smooth_small_df$Plus.1cm.Atten, abs(atten_smooth_small_df$Plus.1cm.Error), pch = shape_map[atten_smooth_small_df$Outlet.Type], col=colors_blue[4], bg=colors_blue[4])
abline(plus1cm_smooth_small_lm, col=colors_blue[4])
#lines(plus1cm_smooth_small_sorted$atten_smooth_small_df.Plus.1cm.Atten, abs(plus1cm_smooth_small_sorted$atten_smooth_small_df.Plus.1cm.Error), lty=3, col=colors_blue[4])
points(atten_smooth_small_df$Minus.1cm.Atten, abs(atten_smooth_small_df$Minus.1cm.Error), pch = shape_map[atten_smooth_small_df$Outlet.Type], col=colors_blue[3], bg=colors_blue[3])
abline(minus1cm_smooth_small_lm, col=colors_blue[3])
#lines(minus1cm_smooth_small_sorted$atten_smooth_small_df.Minus.1cm.Atten, abs(minus1cm_smooth_small_sorted$atten_smooth_small_df.Minus.1cm.Error), lty=3, col=colors_blue[3])
points(atten_smooth_small_df$Plus.5cm.Atten[2:19], abs(atten_smooth_small_df$Plus.5cm.Error[2:19]), pch = shape_map[atten_smooth_small_df$Outlet.Type], col=colors_blue[5], bg=colors_blue[5])
abline(plus5cm_smooth_small_lm, col=colors_blue[5])
#lines(plus5cm_smooth_small_sorted$atten_smooth_small_df.Plus.5cm.Atten, abs(plus5cm_smooth_small_sorted$atten_smooth_small_df.Plus.5cm.Error), lty=3, col=colors_blue[5])
points(atten_smooth_small_df$Minus.5cm.Atten[2:19], abs(atten_smooth_small_df$Minus.5cm.Error[2:19]), pch = shape_map[atten_smooth_small_df$Outlet.Type], col=colors_blue[2], bg=colors_blue[2])
abline(minus5cm_smooth_small_lm, col=colors_blue[2])
#lines(minus5cm_smooth_small_sorted$atten_smooth_small_df.Minus.5cm.Atten, abs(minus5cm_smooth_small_sorted$atten_smooth_small_df.Minus.5cm.Error), lty=3, col=colors_blue[2])
grid()
legend("topright", inset = c(-0.45,0.1), legend = c("Typical Noise", "Plus 5cm", "Plus 1cm", "Minus 1cm", "Minus 5cm", "V-notch Weir", "Rectangular Weir", "Trapezoidal Weir", "Culvert"), col = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pt.bg = c(colors_red[5], colors_blue[5], colors_blue[4], colors_blue[3], colors_blue[2], "black", "black", "black", "black"), pch = c(NA,NA,NA,NA,NA,25,15,18,16), lty = c(1,1,1,1,1,NA,NA,NA,NA), lwd = c(2,2,2,2,2,NA,NA,NA,NA), xpd=TRUE)
```
Plot Bounce vs Noise Error
```{r}
typical_noise_base_lm <- lm(abs(atten_base_df$Typical.Noise.Error) ~ atten_base_df$Bounce)
typical_noise_smooth_lm <- lm(abs(atten_smooth_df$Typical.Noise.Error) ~ atten_smooth_df$Bounce)
typical_noise_base_large_lm <- lm(abs(atten_base_large_df$Typical.Noise.Error) ~ atten_base_large_df$Bounce)
typical_noise_base_small_lm <- lm(abs(atten_base_small_df$Typical.Noise.Error) ~ atten_base_small_df$Bounce)
typical_noise_smooth_large_lm <- lm(abs(atten_smooth_large_df$Typical.Noise.Error) ~ atten_smooth_large_df$Bounce)
typical_noise_smooth_small_lm <- lm(abs(atten_smooth_small_df$Typical.Noise.Error) ~ atten_smooth_small_df$Bounce)

plot(atten_base_df$Bounce, abs(atten_base_df$Typical.Noise.Error), pch=19, ylim=c(0,100))
points(atten_smooth_df$Bounce, abs(atten_smooth_df$Typical.Noise.Error), pch=19, col="red")
points(atten_base_large_df$Bounce, abs(atten_base_large_df$Typical.Noise.Error), pch=19, col="blue")
points(atten_base_small_df$Bounce, abs(atten_base_small_df$Typical.Noise.Error), pch=19, col="green")
points(atten_smooth_large_df$Bounce, abs(atten_smooth_large_df$Typical.Noise.Error), pch=19, col="gold")
points(atten_smooth_small_df$Bounce, abs(atten_smooth_small_df$Typical.Noise.Error), pch=19, col="purple")

abline(typical_noise_base_lm, col="black")
abline(typical_noise_smooth_lm, col="red")
abline(typical_noise_base_large_lm, col="blue")
abline(typical_noise_base_small_lm, col="green")
abline(typical_noise_smooth_large_lm, col="gold")
abline(typical_noise_smooth_small_lm, col="purple")
```
Plot Bounce vs +1cm Error
```{r}
typical_plus1_base_lm <- lm(abs(atten_base_df$Plus.1cm.Error) ~ atten_base_df$Bounce)
typical_plus1_smooth_lm <- lm(abs(atten_smooth_df$Plus.1cm.Error) ~ atten_smooth_df$Bounce)
typical_plus1_base_large_lm <- lm(abs(atten_base_large_df$Plus.1cm.Error) ~ atten_base_large_df$Bounce)
typical_plus1_base_small_lm <- lm(abs(atten_base_small_df$Plus.1cm.Error) ~ atten_base_small_df$Bounce)
typical_plus1_smooth_large_lm <- lm(abs(atten_smooth_large_df$Plus.1cm.Error) ~ atten_smooth_large_df$Bounce)
typical_plus1_smooth_small_lm <- lm(abs(atten_smooth_small_df$Plus.1cm.Error) ~ atten_smooth_small_df$Bounce)

plot(atten_base_df$Bounce, abs(atten_base_df$Plus.1cm.Error), pch=19, ylim=c(0,30))
points(atten_smooth_df$Bounce, abs(atten_smooth_df$Plus.1cm.Error), pch=19, col="red")
points(atten_base_large_df$Bounce, abs(atten_base_large_df$Plus.1cm.Error), pch=19, col="blue")
points(atten_base_small_df$Bounce, abs(atten_base_small_df$Plus.1cm.Error), pch=19, col="green")
points(atten_smooth_large_df$Bounce, abs(atten_smooth_large_df$Plus.1cm.Error), pch=19, col="gold")
points(atten_smooth_small_df$Bounce, abs(atten_smooth_small_df$Plus.1cm.Error), pch=19, col="purple")

abline(typical_plus1_base_lm, col="black")
abline(typical_plus1_smooth_lm, col="red")
abline(typical_plus1_base_large_lm, col="blue")
abline(typical_plus1_base_small_lm, col="green")
abline(typical_plus1_smooth_large_lm, col="gold")
abline(typical_plus1_smooth_small_lm, col="purple")

```

Plot Bounce vs -1cm Error
```{r}
typical_minus1_base_lm <- lm(abs(atten_base_df$Minus.1cm.Error) ~ atten_base_df$Bounce)
typical_minus1_smooth_lm <- lm(abs(atten_smooth_df$Minus.1cm.Error) ~ atten_smooth_df$Bounce)
typical_minus1_base_large_lm <- lm(abs(atten_base_large_df$Minus.1cm.Error) ~ atten_base_large_df$Bounce)
typical_minus1_base_small_lm <- lm(abs(atten_base_small_df$Minus.1cm.Error) ~ atten_base_small_df$Bounce)
typical_minus1_smooth_large_lm <- lm(abs(atten_smooth_large_df$Minus.1cm.Error) ~ atten_smooth_large_df$Bounce)
typical_minus1_smooth_small_lm <- lm(abs(atten_smooth_small_df$Minus.1cm.Error) ~ atten_smooth_small_df$Bounce)

plot(atten_base_df$Bounce, abs(atten_base_df$Minus.1cm.Error), pch=19, ylim=c(0,50))
points(atten_smooth_df$Bounce, abs(atten_smooth_df$Minus.1cm.Error), pch=19, col="red")
points(atten_base_large_df$Bounce, abs(atten_base_large_df$Minus.1cm.Error), pch=19, col="blue")
points(atten_base_small_df$Bounce, abs(atten_base_small_df$Minus.1cm.Error), pch=19, col="green")
points(atten_smooth_large_df$Bounce, abs(atten_smooth_large_df$Minus.1cm.Error), pch=19, col="gold")
points(atten_smooth_small_df$Bounce, abs(atten_smooth_small_df$Minus.1cm.Error), pch=19, col="purple")

abline(typical_minus1_base_lm, col="black")
abline(typical_minus1_smooth_lm, col="red")
abline(typical_minus1_base_large_lm, col="blue")
abline(typical_minus1_base_small_lm, col="green")
abline(typical_minus1_smooth_large_lm, col="gold")
abline(typical_minus1_smooth_small_lm, col="purple")
```

Plot Bounce vs +5cm Error
```{r}
typical_plus5_base_lm <- lm(abs(atten_base_df$Plus.5cm.Error) ~ atten_base_df$Bounce)
typical_plus5_smooth_lm <- lm(abs(atten_smooth_df$Plus.5cm.Error) ~ atten_smooth_df$Bounce)
typical_plus5_base_large_lm <- lm(abs(atten_base_large_df$Plus.5cm.Error) ~ atten_base_large_df$Bounce)
typical_plus5_base_small_lm <- lm(abs(atten_base_small_df$Plus.5cm.Error) ~ atten_base_small_df$Bounce)
typical_plus5_smooth_large_lm <- lm(abs(atten_smooth_large_df$Plus.5cm.Error) ~ atten_smooth_large_df$Bounce)
typical_plus5_smooth_small_lm <- lm(abs(atten_smooth_small_df$Plus.5cm.Error) ~ atten_smooth_small_df$Bounce)

plot(atten_base_df$Bounce, abs(atten_base_df$Plus.5cm.Error), pch=19, ylim=c(0,60))
points(atten_smooth_df$Bounce, abs(atten_smooth_df$Plus.5cm.Error), pch=19, col="red")
points(atten_base_large_df$Bounce, abs(atten_base_large_df$Plus.5cm.Error), pch=19, col="blue")
points(atten_base_small_df$Bounce, abs(atten_base_small_df$Plus.5cm.Error), pch=19, col="green")
points(atten_smooth_large_df$Bounce, abs(atten_smooth_large_df$Plus.5cm.Error), pch=19, col="gold")
points(atten_smooth_small_df$Bounce, abs(atten_smooth_small_df$Plus.5cm.Error), pch=19, col="purple")

abline(typical_plus5_base_lm, col="black")
abline(typical_plus5_smooth_lm, col="red")
abline(typical_plus5_base_large_lm, col="blue")
abline(typical_plus5_base_small_lm, col="green")
abline(typical_plus5_smooth_large_lm, col="gold")
abline(typical_plus5_smooth_small_lm, col="purple")
```

Plot Bounce vs -5cm Error
```{r}
typical_minus5_base_lm <- lm(abs(atten_base_df$Minus.5cm.Error) ~ atten_base_df$Bounce)
typical_minus5_smooth_lm <- lm(abs(atten_smooth_df$Minus.5cm.Error) ~ atten_smooth_df$Bounce)
typical_minus5_base_large_lm <- lm(abs(atten_base_large_df$Minus.5cm.Error) ~ atten_base_large_df$Bounce)
typical_minus5_base_small_lm <- lm(abs(atten_base_small_df$Minus.5cm.Error) ~ atten_base_small_df$Bounce)
typical_minus5_smooth_large_lm <- lm(abs(atten_smooth_large_df$Minus.5cm.Error) ~ atten_smooth_large_df$Bounce)
typical_minus5_smooth_small_lm <- lm(abs(atten_smooth_small_df$Minus.5cm.Error) ~ atten_smooth_small_df$Bounce)

plot(atten_base_df$Bounce, abs(atten_base_df$Minus.5cm.Error), pch=19, ylim=c(0,100))
points(atten_smooth_df$Bounce, abs(atten_smooth_df$Minus.5cm.Error), pch=19, col="red")
points(atten_base_large_df$Bounce, abs(atten_base_large_df$Minus.5cm.Error), pch=19, col="blue")
points(atten_base_small_df$Bounce, abs(atten_base_small_df$Minus.5cm.Error), pch=19, col="green")
points(atten_smooth_large_df$Bounce, abs(atten_smooth_large_df$Minus.5cm.Error), pch=19, col="gold")
points(atten_smooth_small_df$Bounce, abs(atten_smooth_small_df$Minus.5cm.Error), pch=19, col="purple")

abline(typical_minus5_base_lm, col="black")
abline(typical_minus5_smooth_lm, col="red")
abline(typical_minus5_base_large_lm, col="blue")
abline(typical_minus5_base_small_lm, col="green")
abline(typical_minus5_smooth_large_lm, col="gold")
abline(typical_minus5_smooth_small_lm, col="purple")
```
