---
title: "UrbanBaseflow"
author: "Hannah Curtis"
date: "2024-01-29"
output: html_document
---

This file calculates the percentage of days that urban baseflow is occurring in each pond. The calculation uses the inflow calculations using the reverse Puls routing method and considers urban baseflow to be inflow greater than 1 cfs. 

Could change the threshold to be bigger?

Should also come back and recalculate with new inflow calculations.

Updated: 3/5/24

Read inflow files:
```{r}
# Baxter
baxter_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Baxter/Baxter_Inflow_Outflow.csv")
# Commercial Ave
commave_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/CommAve/CommAve_Inflow_Outlfow.csv")
# DobsonA4
doba4_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA4/DobA4_Inflow_Outflow.csv")
# DobsonA5
doba5_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA5/DobA5_Inflow_Outflow.csv")
# DobsonA7
doba7_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA7/DobA7_Inflow_Outflow.csv")
# DobsonA8
doba8_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA8/DobA8_Inflow_Outflow.csv")
# DobsonA22
doba22_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DobA22/DobA22_Inflow_Outflow.csv")
# Door Creek
doorcreek_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/DoorCreek/DoorCreek_Inflow_Outflow.csv")
# Elver
elver_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Elver/Elver_Inflow_Outflow.csv")
# Garner
garner_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Garner/Garner_Inflow_Outflow.csv")
# Greentree
greentree_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Greentree/Greentree_Inflow_Outflow.csv")
# Hospital
hospital_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Hospital/Hospital_Inflow_Outflow.csv")
# HP Church
hpchurch_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/HPChurch/HPChurch_Inflow_Outflow.csv")
# Lot 60
lot60_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Lot60/Lot60_Inflow_Outflow.csv")
# Mad City
madcity_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/MadCity/MadCity_Inflow_Outflow.csv")
# Manitou
manitou_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Manitou/Manitou_Inflow_Outflow.csv")
# Marion Dunn
mariondunn_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/MarionDunn/MarionDunn_Inflow_Outflow.csv")
# Midtown
midtown_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Midtown/Midtown_Inflow_Outlfow.csv")
# Owen
owen_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/Owen/Owen_Inflow_Outflow.csv")
# Two Fountains
twofountains_inf_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Water_Level/TwoFountains/TwoFountains_Inflow_Outflow.csv")
```

Urban baseflow function
```{r}

get_baseflow <- function(inflow_data) {
  # Convert the DateTime column to Date format
  inflow_data$Date <- as.Date(inflow_data$DateTime, format = "%m/%d/%y %H:%M")
  # Extract just the date portion
  inflow_data$Date <- format(inflow_data$Date, "%m/%d/%y")
  # Filter dates based on the threshold of inflow
  filtered_dates <- inflow_data$Date[inflow_data$Inflow.cfs > 1]
  # Use length to get the number of different values
  unique_dates <- length(unique(filtered_dates))
  # Get percentage of days with inflow
  percentage_inflow <- (unique_dates/(length(unique(inflow_data$Date))))*100
  # Return urban baseflow
  return(percentage_inflow)
}

```

Pond urban baseflows
```{r}
# Baxter
baxter_baseflow <- get_baseflow(baxter_inf_data)
# Commercial Ave
commave_baseflow <- get_baseflow(commave_inf_data)
# DobsonA4
doba4_baseflow <- get_baseflow(doba4_inf_data)
# DobsonA5
doba5_baseflow <- get_baseflow(doba5_inf_data)
# DobsonA7
doba7_baseflow <- get_baseflow(doba7_inf_data)
# DobsonA8
doba8_baseflow <- get_baseflow(doba8_inf_data)
# DobsonA22
doba22_baseflow <- get_baseflow(doba22_inf_data)
# Door Creek
doorcreek_baseflow <- get_baseflow(doorcreek_inf_data)
# Elver
elver_baseflow <- get_baseflow(elver_inf_data)
# Garner
garner_baseflow <- get_baseflow(garner_inf_data)
# Greentree
greentree_baseflow <- get_baseflow(greentree_inf_data)
# Hospital
hospital_baseflow <- get_baseflow(hospital_inf_data)
# HP Church
hpchurch_baseflow <- get_baseflow(hpchurch_inf_data)
# Lot 60
lot60_baseflow <- get_baseflow(lot60_inf_data)
# Mad City
madcity_baseflow <- get_baseflow(madcity_inf_data)
# Manitou
manitou_baseflow <- get_baseflow(manitou_inf_data)
# Marion Dunn
mariondunn_baseflow <- get_baseflow(mariondunn_inf_data)
# Midtown
midtown_baseflow <- get_baseflow(midtown_inf_data)
# Owen
owen_baseflow <- get_baseflow(owen_inf_data)
# Two Fountains
twofountains_baseflow <- get_baseflow(twofountains_inf_data)
```

Save as csv file
```{r}

# Pond names
pond_names <- c("Hospital", "Lot60", "Garner", "DobA7", "Owen", "HPChurch", "DobA8", "Midtown", "Elver", "TwoFountains", "Greentree", "MarionDunn", "Manitou", "MadCity", "Baxter", "DobA22", "DobA5", "DobA4", "DoorCreek", "CommAve")

# Urban baseflow values
urban_baseflow <- c(hospital_baseflow, lot60_baseflow, garner_baseflow, doba7_baseflow, owen_baseflow, hpchurch_baseflow, doba8_baseflow, midtown_baseflow, elver_baseflow, twofountains_baseflow, greentree_baseflow, mariondunn_baseflow, manitou_baseflow, madcity_baseflow, baxter_baseflow, doba22_baseflow, doba5_baseflow, doba4_baseflow, doorcreek_baseflow, commave_baseflow)

# Create urban baseflow data frame for all ponds
urban_baseflow_df <- data.frame(Pond.Name = pond_names, Urban.Baseflow = urban_baseflow)

# Write csv for urban baseflow in each pond
write.csv(urban_baseflow_df, "/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Predictor_Variables/Urban_Baseflow/Urban_Baseflow.csv", row.names=FALSE)
```

