---
title: "WQ_Plots"
author: "Hannah Curtis"
date: "2024-04-09"
output: html_document
---

This file is for creating figures to show the change in magnitude of various water quality variables by storm (1 day after storm vs 7-10 days after) for each pond. The water quality variables include chloride, sulfate, nitrate, ammonia, TN, TP, water clarity, TSS, and DO. The storm dates are 7/29/23, 8/14/23, and 9/26/23.

5/3: Added plots for odor, trash count, and SPC

Last updated: 5/3/24

Read in data file
```{r}
#wq_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/WQ_Plots.csv")
wq_data_2 <- read.csv("WQ_Plots_2.csv")
#aesthetic_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Aesthetic/Aesthetic_Plots.csv")
#SPC_data <- read.csv("/Users/hannahcurtis/Desktop/School/UWMadison/Research/Data Analysis/Response_Variables/Water_Quality/SPC_Plots.csv")
```

Write function for plotting water quality arrows by storm
```{r}
plot_with_arrows <- function(x, y1, y2, ylab) {
  # Create a new plot
  plot(x, y1, type = "n", ylim = c((min(c(y1,y2))-(0.1*min(c(y1,y2)))), (max(c(y1,y2))+(0.1*max(c(y1,y2))))), xlim = c(min(x)-2, max(x)+4), xlab = "", ylab = ylab, xaxt = "n", xaxs = "i", yaxs = "i",      cex.lab = 1.4,  # Increase size of axis labels
     cex.axis = 1.4) # Increase size of tick labels)
  
  # Define the interval for shading
x_interval <- 12

  # Add shaded rectangles for every other interval
for (i in seq(0, max(x), by = x_interval * 2)) {
  rect(xleft = i, xright = i + x_interval, ybottom = par("usr")[3], ytop = par("usr")[4],
       col = "gray90", border = NA)
}
  
  # add grid
  #grid(nx = NULL, ny = NULL, col = "grey")
  
  # add border of plot back in
  box()

  # Add points for the second set of y-values
  points(x, y2, type = "n")
  
  # Define arrow colors
  arrow_colors <- rep(c("#B3CBB9", "#84A9C0", "#6A66A3", "#542E71"), length.out = length(x))
  
  # Add arrows for each pair of points with alternating colors
  for (i in seq_along(x)) {
    col <- arrow_colors[i]
    arrows(x[i], y1[i], x[i], y2[i], length = 0.08, lwd = 2, col = col)
  }
}
```

Chloride
```{r}
png("chloride.png", width = 800, height = 600)

chloride_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$Chloride.1..mg.L., wq_data_2$Chloride.2..mg.L., "Chloride Concentration (mg/L)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 1, ny = NULL)

box()

dev.off()
```
Sulfate 
```{r}

png("sulfate.png", width = 800, height = 600)

sulfate_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$Sulfate.1..mg.L., wq_data_2$Sulfate.2..mg.L., "Sulfate Concentration (mg/L)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```

Nitrate
```{r}
png("nitrate.png", width = 800, height = 600)

nitrate_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$Nitrate.1..ug.L., wq_data_2$Nitrate.2..ug.L., "Nitrate Concentration (ug/L)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```
Ammonia
```{r}
png("ammonia.png", width = 800, height = 600)

ammonia_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$Ammonia.1..ug.L., wq_data_2$Ammonia.2..ug.L., "Ammonia Concentration (ug/L)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```
TN
```{r}
png("tn.png", width = 800, height = 600)

TN_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$TN.1..ug.L., wq_data_2$TN.2..ug.L., "Total Nitrogen Concentration (ug/L)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```
TP
```{r}
png("tp.png", width = 800, height = 600)

TP_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$TP.1..ug.L., wq_data_2$TP.2..ug.L., "Total Phosphorous Concentration (ug/L)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```
Water Clarity
```{r}
png("clarity.png", width = 800, height = 600)

clarity_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$Secchi.Disk.Depth.1..cm., wq_data_2$Secchi.Disk.Depth.2..cm., "Secchi Disk Depth (cm)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()

```
TSS
```{r}
png("tss.png", width = 800, height = 600)

TSS_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$TSS.1..mg.L., wq_data_2$TSS.2..mg.L., "TSS Concentration (mg/L)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()

```

DO
```{r}
png("do.png", width = 800, height = 600)

DO_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$YSI.DO.1..mg.L., wq_data_2$YSI.DO.2..mg.L., "DO Concentration (mg/L)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```
SPC
```{r}
png("spc.png", width = 800, height = 600)

spc_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$SPC.1, wq_data_2$SPC.2, "Specific Conductance (uS/cm)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```

Label x-axis by pond names
```{r}
pond_names <- c("Hospital", "Lot 60", "Garner", "DobA7", "Owen", "HP Church", "DobA8", "Midtown", "Elver", "Two Fountains", "Greentree", "Marion-Dunn", "Manitou", "Mad City", "Baxter", "DobA22", "DobA5", "DobA4", "Door Creek", "Comm Ave")

pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 6th point)
custom_ticks <- seq(4, max(x), by = 9)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 9)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2)

```
Trash Count
```{r}
png("trash.png", width = 800, height = 600)

trash_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$Trash.1, wq_data_2$Trash.2, "In-pond Trash Count")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```

Downstream Trash
```{r}
png("dstrash.png", width = 800, height = 600)

dstrash_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$DS.Trash.1, wq_data_2$DS.Trash.2, "Downstream Trash Count")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```

Odor
```{r}
png("odor.png", width = 800, height = 600)

odor_plot <- plot_with_arrows(wq_data_2$Num4, wq_data_2$Odor.1, wq_data_2$Odor.2, "Odor Score")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```

Attenuation
```{r}
plot_with_dots <- function(x, y1, ylab) {
  # Define arrow colors
  dot_colors <- c("#B3CBB9", "#84A9C0", "#6A66A3", "#542E71", "#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#B3CBB9", "#84A9C0", "#6A66A3", "#542E71", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71","#B3CBB9", "#84A9C0", "#6A66A3", "#542E71")
  
  # Create a new plot
  plot(x, y1, col = dot_colors, pch = 19, ylim = c((min(c(y1))-(0.1*min(c(y1)))), (max(c(y1))+(0.1*max(c(y1))))), xlim = c(min(x)-2, max(x)+4), xlab = "", ylab = ylab, xaxt = "n", xaxs = "i", yaxs = "i",      cex.lab = 1.4,  # Increase size of axis labels
     cex.axis = 1.4) # Increase size of tick labels)
  
  # Define the interval for shading
x_interval <- 12

  # Add shaded rectangles for every other interval
for (i in seq(0, max(x), by = x_interval * 2)) {
  rect(xleft = i, xright = i + x_interval, ybottom = par("usr")[3], ytop = par("usr")[4],
       col = "gray90", border = NA)
}
  
  # add grid
  #grid(nx = NULL, ny = NULL, col = "grey")
  
  points(x, y1, col = dot_colors, pch = 19)
  # add border of plot back in
  box()

}

png("atten.png", width = 800, height = 600)

atten_plot <- plot_with_dots(na.omit(wq_data_2$Num5), na.omit(wq_data_2$Atten), "Attenuation (% Reduction in Flow)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```

Richness
```{r}
plot_with_dots <- function(x, y1, ylab) {
  # Define arrow colors
  # Create a new plot
  plot(x, y1, col = "#B3CBB9", pch = 19, ylim = c((min(c(y1))-(0.1*min(c(y1)))), (max(c(y1))+(0.1*max(c(y1))))), xlim = c(min(x)-2, max(x)+4), xlab = "", ylab = ylab, xaxt = "n", xaxs = "i", yaxs = "i",      cex.lab = 1.4,  # Increase size of axis labels
     cex.axis = 1.4) # Increase size of tick labels)
  
  # Define the interval for shading
x_interval <- 12

  # Add shaded rectangles for every other interval
for (i in seq(0, max(x), by = x_interval * 2)) {
  rect(xleft = i, xright = i + x_interval, ybottom = par("usr")[3], ytop = par("usr")[4],
       col = "gray90", border = NA)
}
  
  # add grid
  #grid(nx = NULL, ny = NULL, col = "grey")
  
  points(x, y1, col = "#B3CBB9", pch = 19)
  # add border of plot back in
  box()

}

png("richness.png", width = 800, height = 600)

richness_plot <- plot_with_dots(na.omit(wq_data_2$Num6), na.omit(wq_data_2$Richness), "Total Richness")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```

Percent of Days with Outflow
```{r}
plot_with_dots <- function(x, y1, ylab) {
  # Define arrow colors
  # Create a new plot
  plot(x, y1, col = "#B3CBB9", pch = 19, ylim = c((min(c(y1))-(0.1*min(c(y1)))), (max(c(y1))+(0.1*max(c(y1))))), xlim = c(min(x)-2, max(x)+4), xlab = "", ylab = ylab, xaxt = "n", xaxs = "i", yaxs = "i",      cex.lab = 1.4,  # Increase size of axis labels
     cex.axis = 1.4) # Increase size of tick labels)
  
  # Define the interval for shading
x_interval <- 12

  # Add shaded rectangles for every other interval
for (i in seq(0, max(x), by = x_interval * 2)) {
  rect(xleft = i, xright = i + x_interval, ybottom = par("usr")[3], ytop = par("usr")[4],
       col = "gray90", border = NA)
}
  
  # add grid
  #grid(nx = NULL, ny = NULL, col = "grey")
  
  points(x, y1, col = "#B3CBB9", pch = 19)
  # add border of plot back in
  box()

}

png("percentof.png", width = 800, height = 600)

percentof_plot <- plot_with_dots(na.omit(wq_data_2$Num6), na.omit(wq_data_2$Percent.Days.Outflow), "Percentage of Days with Outflow (%)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```

Peak Outflow
```{r}
plot_with_dots <- function(x, y1, ylab) {
  # Define arrow colors
  # Create a new plot
  plot(x, y1, col = "#B3CBB9", pch = 19, ylim = c((min(c(y1))-(0.1*min(c(y1)))), (max(c(y1))+(0.1*max(c(y1))))), xlim = c(min(x)-2, max(x)+4), xlab = "", ylab = ylab, xaxt = "n", xaxs = "i", yaxs = "i",      cex.lab = 1.4,  # Increase size of axis labels
     cex.axis = 1.4) # Increase size of tick labels)
  
  # Define the interval for shading
x_interval <- 12

  # Add shaded rectangles for every other interval
for (i in seq(0, max(x), by = x_interval * 2)) {
  rect(xleft = i, xright = i + x_interval, ybottom = par("usr")[3], ytop = par("usr")[4],
       col = "gray90", border = NA)
}
  
  # add grid
  #grid(nx = NULL, ny = NULL, col = "grey")
  
  points(x, y1, col = "#B3CBB9", pch = 19)
  # add border of plot back in
  box()

}

png("peakofcms.png", width = 800, height = 600)

richness_plot <- plot_with_dots(na.omit(wq_data_2$Num6), na.omit(wq_data_2$Peak.Outflow.cms), "Peak Outflow (cms)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```

Normalized Peak Outflow
```{r}
plot_with_dots <- function(x, y1, ylab) {
  # Define arrow colors
  # Create a new plot
  plot(x, y1, col = "#B3CBB9", pch = 19, ylim = c((min(c(y1))-(0.1*min(c(y1)))), (max(c(y1))+(0.1*max(c(y1))))), xlim = c(min(x)-2, max(x)+4), xlab = "", ylab = ylab, xaxt = "n", xaxs = "i", yaxs = "i",      cex.lab = 1.4,  # Increase size of axis labels
     cex.axis = 1.4) # Increase size of tick labels)
  
  # Define the interval for shading
x_interval <- 12

  # Add shaded rectangles for every other interval
for (i in seq(0, max(x), by = x_interval * 2)) {
  rect(xleft = i, xright = i + x_interval, ybottom = par("usr")[3], ytop = par("usr")[4],
       col = "gray90", border = NA)
}
  
  # add grid
  #grid(nx = NULL, ny = NULL, col = "grey")
  
  points(x, y1, col = "#B3CBB9", pch = 19)
  # add border of plot back in
  box()

}

png("normpeakof.png", width = 800, height = 600)

richness_plot <- plot_with_dots(na.omit(wq_data_2$Num6), na.omit(wq_data_2$Peak.Outflow.Norm), "Peak Outflow/Watershed Area (cfs/ft2)")
pond_codes <- c("HP-UW", "L60-UW", "GPP", "DOBA7", "OPP-W", "HPC", "DOBA8", "MDT", "ELV", "2FP", "GCH", "WS-ARB", "UM-ARB", "MC-ARB", "BaxN", "DOBA22", "DOBA5", "DOBA4", "DCSW", "CAP")

# Define custom tick mark locations (every 4th point starting from 3)
custom_ticks <- seq(5, 236, by = 12)

# Get the corresponding pond names for the custom tick mark locations
custom_labels <- pond_codes[ceiling(custom_ticks / 12)]

# Add custom tick marks and labels to the x-axis
axis(side = 1, at = custom_ticks, labels = custom_labels, las = 2, cex.axis = 1.2)

# Add gridlines that match custom ticks
#abline(v = custom_ticks, col = "grey", lty = "dotted")

# Add gridlines on y axis
grid(nx = 0, ny = NULL)

box()

dev.off()
```
